---
title: "Ferritina"
author: "Carlos Ballón-Salcedo"
date: "`r Sys.Date()`"
format:
  html:
    theme: 
     light: lux
     dark: darkly
    toc: true # índice automático
    toc-depth: 3 # niveles de encabezado en el índice
    code-overflow: wrap
    include-after-body: zoom_in_out.js
    highlight-style: github
    number-sections: true
    code-fold: true # plegar código
    code-tools: 
      source: "https://github.com/Carlos-Ballon/ferritin-anemia_diagnosis.git"
editor: source
execute:
  message: false
  warning: false
bibliography: grateful-refs.bib
csl: vancouver.csl
lang: en # idioma del documento
---

# Load packages

```{r}
# Packages
pacman::p_load(
  tidyverse,
  rio,
  here,
  epiDisplay,
  Hmisc,
  ggalluvial,
  ggplot2,
  ggsankey,
  psych,
  factoextra,
  ggpubr,
  rms,
  broom,
  ggeffects,
  rfextras,
  grateful,
  flextable,
  janitor,
  performance,
  gtsummary,
  finalfit,
  mgcv,
  officer)
```

```{r}
#| eval: false
# Citations
grateful::cite_packages(
  output = "file",
  out.format = "docx",
  out.dir = ".",
  citation.style = "vancouver")
```

# Set gtsummary theme

```{r}
# Set gtsummary theme
gtsummary::theme_gtsummary_journal(journal = "jama")

# Set gtsummary language
gtsummary::theme_gtsummary_language(language = "es")
```

# Set gtsummary theme

```{r}
# Set gtsummary theme
gtsummary::theme_gtsummary_journal(journal = "jama")

# Set gtsummary language
gtsummary::theme_gtsummary_language(language = "es")
```

# Import data

```{r}
# Data
data <- import(here("data", "base_de_curvas.dta"))

# Scripts
rfextras::load_scripts()
```

# Process data

```{r}
# Select categorical variables (to factor)
vars <- c(
  "P001", "P002", "P004", "P005", "P006", "P007", "P008", "P009", "P010", "P011",
  "P012", "P013", "P014", "P015", "P018", "P019", "P020", "P021", "P022", "P023",
  "P024", "P025", "P028", "P029", "anemia", "ferropenia")

data <- data |>
  dplyr::select(-wealth_index_raw, -urban_rural_dim, -wealth_pc1) |>
  dplyr::filter(P015 %in% c(1, 2, 6)) |>
  mutate(
    
    anemia     = if_else(P037 < 10.5, 1L, 0L),
    ferropenia = if_else(ferr_adj < 12, 1L, 0L),
    
    across(all_of(vars), ~ replace(.x, .x >= 99, NA)),
    
    across(all_of(vars), as_factor),
    
    sexo = factor(P001) |>
      fct_recode("Masculino" = "1", "Femenino" = "2") |>
      fct_relevel("Masculino", "Femenino") |>
      ff_label("Sexo del infante"), 
    
    seguro_infante = case_match(
        as.character(P002),
        c("1", "2", "3") ~ "Públicos (SIS, EsSalud, FFAA)",
        c("4", "5") ~ "Privado",
        c("6", "7", "99") ~ "No sabe o no responde",
        .default = NA_character_
      ) |>
      fct_relevel(
        "Públicos (SIS, EsSalud, FFAA)", "Privado", "No sabe o no responde") |>
      ff_label("Seguro de salud del infante"), 
    
    DEP = factor(DEP) |>
      fct_relevel("Arequipa", "Lima", "Cusco", "Puno") |>
      ff_label("Departamento"),
    
    edad_madre = ff_label(P003, "Edad de la madre"), 
    
    patologia = case_when(
      anemia == 1 & ferropenia == 1 ~ "Anemia ferropénica",
      anemia == 1 & ferropenia == 0 ~ "Anemia no ferropénica",
      anemia == 0 & ferropenia == 1 ~ "Ferropenia temprana",
      anemia == 0 & ferropenia == 0 ~ "Normal",
      TRUE ~ "Otro"
    ) |>
      fct_relevel(
        "Normal", "Ferropenia temprana", 
        "Anemia no ferropénica", "Anemia ferropénica") |>
      ff_label("Clasificación de anemia y ferropenia"),
    
    etnia = case_match(
      P015,
      "1" ~ "Quechua/Aymara",
      "2" ~ "Quechua/Aymara",
      "6" ~ "Mestizo",
      .default = NA_character_
    ) |>
      fct_relevel("Mestizo", "Quechua/Aymara") |>
      ff_label("Etnia"),
    
    educacion = case_match(
      P007, 
      c("0", "1", "2") ~ "Primaria o ninguno", 
      "3" ~ "Secundaria", 
      c("4", "5") ~ "Superior") |>
      fct_relevel("Primaria o ninguno", "Secundaria", "Superior") |>
      ff_label("Nivel educativo de la madre"),
    
    wealth_5 = ff_label(wealth_5, "Índice de riqueza"),
    
    wealth_3 = ff_label(wealth_3, "Índice de riqueza"),
    
    altura = ff_label(P017, "Altura (m s. n. m.)"),
    
    altura_cat = case_when(
      P017 < 1500  ~ "< 1500",
      P017 >= 1500 & P017 < 3000 ~ "1500 - 2999",
      P017 >= 3000 & P017 < 3500 ~ "3000 - 3499",
      P017 >= 3500 ~ ">= 3500",
      TRUE ~ NA_character_  
    ) %>% 
      fct_relevel("< 1500", "1500 - 2999", "3000 - 3499", ">= 3500") |>
      ff_label("Altura (m s. n. m.)"),
    
    anemia_oms2024 = if_else(P016 >= 10.5, "No", "Si") |>
      fct_relevel("No", "Si") |>
      ff_label("Anemia (OMS 2024, sin ajuste por altura)"),
    
    anemia_oms2024_cor = if_else(P037 >= 10.5, "No", "Si") |>
      fct_relevel("No", "Si") |>
      ff_label("Anemia (OMS 2024, con ajuste por altura)"),
    
    ferropenia_cat = if_else(P031 >= 12, "No", "Si") |>
      fct_relevel("No", "Si") |>
      ff_label("Ferropenia (OMS 2024, sin ajuste por inflamación)"),
    
    ferropenia_cor = if_else(ferr_adj >= 12, "No", "Si") |>
      fct_relevel("No", "Si") |>
      ff_label("Ferropenia (Método BRINDA)"),
    
    sTfR_cat = ff_label(P032, "Receptor soluble de transferrina"),
    
    reserva_hierro = ff_label(P036, "Estado del hierro corporal total"),
    
    vitamina_A = if_else(
      P033 < 0.70, "Deficiencia de Vitamina A", "Suficiente") |>
      fct_relevel("Suficiente", "Deficiencia de Vitamina A") |>
      ff_label("Deficiencia de Vitamina A"),
    
    suplemento = case_match(
      P029, 
      "1" ~ "Si", "2" ~ "No", .default = NA_character_) |>
      fct_relevel("No", "Si") |>
      ff_label("Suplementación con de hierro"),
    
    AGP = ff_label(P034, "Alfa-1-glicoproteína ácida (g/L)"), 
    PCR = ff_label(P035, "Proteína C reactiva (mg/L)")
  ) |>
  
  dplyr::select(P037, ferr_adj, DEP, wealth_std:PCR)
```

# Data dictionary / structure

```{r}
#| eval: false
# Generate a data dictionary
labelled::generate_dictionary(data)

# Inspect variable labels and data.frame structure
labelled::var_label(data)  # list of variable labels (if available)
Hmisc::contents(data)      # data.frame of variable types and missing values
dplyr::glimpse(data)       # compact structure
str(data)                  # detailed structure

# Inspect labels of specific variables
attributes(data$P001)
haven::var_labels(data$P001)
```

# Exploratory Data Analysis

::: {style="text-align: justify"}
Several R packages provide functions with identical names, such as `describe()` in the `Hmisc` package and `describe()` in the `psych` package. The first function performs descriptive analysis by providing robust estimators and shape metrics, such as the interquartile range (IQR), trimmed mean, median absolute deviation (MAD), skewness, and kurtosis. In contrast, the second function provides a distribution profile using percentiles, Gini's mean difference (Gdm), and the pseudomedian (pMedian), while also facilitating data screening with diagnostics for unique and missing values. The `epiDisplay` package also provides functions inspired by **Stata**, such as `summ()`. Additional valuable resources include the `janitor` package for data cleaning, as well as initiatives like the R Epidemics Consortium (RECON), Epiverse-TRACE, and the R4EPI project, which provide specialized tools for epidemiological research and analysis.
:::

## Categorical data

```{r}
#| eval: false
# Select categorical variables (factors)
categorical_vars <- data |>
  dplyr::select(where(\(x) is.character(x) | is.factor(x)))
```

### Stucture of categorical variables

```{r}
#| eval: false
# Concise statistical description (display labels)
Hmisc::describe(categorical_vars, exclude.missing = FALSE)
```

### Missing values and complete cases

```{r}
#| eval: false
# Count of missing values by column (vector)
colSums(is.na(categorical_vars))

# List of complete values by column
lapply(categorical_vars, function(x)
  sum(complete.cases(x)))

# Columns without missing values (vector)
colnames(categorical_vars)[sapply(categorical_vars, function(x)
  all(!is.na(x)))]
```

### Duplicate elements

::: {style="text-align: justify"}
The `duplicated()` function identifies duplicate elements, `unique()` extracts unique elements, and `distinct()` from dplyr package removes duplicate rows from a data frame.
:::

### Descriptive analysis: Measures of frequency and proportions

```{r}
#| eval: false
# Absolute frequency for categorical variables
lapply(categorical_vars, function(x)
  addmargins(table(x, useNA = "ifany")))

# Relative frequency for categorical variables
lapply(categorical_vars, function(x)
  round(addmargins(prop.table(table(x)) * 100), 1))
  
# Absolute frequency for categorical variables by anemia
lapply(categorical_vars, function(x)
  addmargins(table(x, categorical_vars$anemia)))

# Flextable
categorical_vars |>
  tabyl(anemia, ferropenia) |>
  adorn_totals(where = "both") |>
  adorn_percentages(denominator = "col") |>
  adorn_pct_formatting() |>
  adorn_ns(position = "front") |>
  flextable() |>
  autofit()
```

## Numerical data

```{r}
#| eval: false
# Selection of variables
numerical_vars <- data |>
  dplyr::select(where(\(x) is.numeric(x)), anemia, ferropenia)
```

#### Descriptive statistics: Summary statistics

```{r}
#| eval: false
# Compact
numerical_vars |> epiDisplay::summ(digits = 2, na.rm = FALSE)

# Detailed
numerical_vars |> psych::describe(na.rm = FALSE, IQR = TRUE, quant = c(.25,.75))

# Percentiles
numerical_vars |> Hmisc::describe()
quantile(data$P003, probs = seq(0, 1, by = 0.1), type = 7)
quantile(data$P003, probs = c(0.10, 0.30, 0.50, 0.70, 0.90), type = 6)
```

#### Descriptive statistics: Grouped summary statistics

```{r}
#| eval: false
# Anemia
numerical_vars |>
  dplyr::group_split(anemia) |>
  lapply(function(data)
    summ(numerical_vars, digits = 2, na.rm = TRUE))

# Ferropenia
numerical_vars |>
  dplyr::group_split(ferropenia) |>
  lapply(function(data)
    summ(numerical_vars, digits = 2, na.rm = TRUE))
```

# Produce outputs

Anemia no relacionada con ferropenia

Objetivo: Evaluar las brechas entre grupos etnicos relacionadas con la anemia no ferropenica según el SES

Evaluar si la etica se asocia a la ferropenia

Evaluar si la asociación entre el índice de riqueza del hogar y la prevalencia de anemia y ferropenia infantil difiere según la pertenencia étnica (mestizos, quechuas y aymaras)

Evaluar si la etnicidad se asocia (o influye) a la prevalencia de anemia o ferropenia infantil

Evaluar si la etnicidad se asocia a la prevalencia de ferropenia infantil

Anemia, anemia ferropenica, anemia no ferropenica, ferropenia. El mensaje seria "En el gradiente, tener un mejor SES reduce los niveles de anemia, pero la brecha por etnicidad es más grande en ferropenia que en anemia no ferropenica y probablemente que en anemia".

Posible resultado: La brecha es mas grande en ferropenia que en anemia no ferropenica

El muestreo nace en el establecimento de salud, basado en el CRED

8 graficos

Tabla 1. Bivariada de grupos etnicos
Tabla 2. Anemia ferropenica, anemia no ferropenica, ferropenia (solo si ferropenia), anemia total
Tabla 3. Modelos
Figura 1. 4 cosas = SES + etnica
Figura 2. 4 cosas = Educación + etnica

```{r}
# Definir las propiedades de la sección (Horizontal)
sect_properties <- prop_section(
  page_size = page_size(orient = "portrait"),
  page_margins = page_mar(bottom = 0.5, top = 0.5, right = 0.5, left = 0.5),
  type = "continuous"
)
```

## Table S1. 

```{r}
table_S1 <- data |> 
  tbl_summary(
    include = c(
      edad_madre, educacion, sexo, seguro_infante, wealth_3, altura_cat, DEP, 
      anemia_oms2024_cor, ferropenia_cor, patologia, AGP, PCR),
    by = etnia,
    percent = "row",
    statistic = list(
      all_continuous() ~ "{median} ({p25}, {p75})", 
      all_categorical() ~ "{n} ({p}%)"),
    digits = list(all_categorical() ~ c(0, 1)),
    missing_text = "no"
  ) |>
  add_p(
    test = list(
      all_continuous() ~ "wilcox.test",
      all_categorical() ~ "chisq.test",
      seguro_infante ~ "fisher.test"
    ),
    pvalue_fun = ~ style_pvalue(.x, digits = 3)
  ) |>
  bold_p(t = 0.05) |>
  # Simple star for continuous (Mann-Whitney)
  modify_fmt_fun(
    p.value ~ function(x) paste0(style_pvalue(x, digits = 3), "*"),
    rows = var_type == "continuous"
  ) |>
  # Double star for categorical (Chi-square)
  modify_fmt_fun( 
    p.value ~ function(x) paste0(style_pvalue(x, digits = 3), "**"),
    rows = var_type %in% c("categorical", "dichotomous") & variable != "seguro_infante"
  ) |>
  # Cross for Fisher test (specifically seguro_infante)
  modify_fmt_fun(
    p.value ~ function(x) paste0(style_pvalue(x, digits = 3), "†"),
    rows = variable == "seguro_infante"
  ) |>
  modify_header(
    label = "**Características**", 
    stat_1 = "**Mestizo**  \nN = {n} ({style_percent(p, digits = 1)}%)",
    stat_2 = "**Quechua/Aymara**  \nN = {n} ({style_percent(p, digits = 1)}%)"
  ) |>
  modify_abbreviation(
    "OMS, Organización Mundial de la Salud; SIS, Seguro Integral de Salud; ") |>
  modify_footnote(
    starts_with("p.value") ~ 
    "Prueba U de Mann-Whitney (*); Prueba de Chi-cuadrado (**); Prueba exacta de Fisher (†)"
  ) |>
  as_flex_table() |>
  theme_booktabs() |>
  fontsize(size = 9, part = "all") |>
  align(j = 1, align = "left", part = "header") |>
  align(j = 2, align = "center", part = "header") |>
  align(j = 2, align = "center", part = "body") |>
  padding(
    padding.top = 0, padding.bottom = 0, padding.right = 2, part = "all") |>
  width(j = 1, width = 2) |>
  width(j = 2, width = 1.2) |>
  set_table_properties(layout = "fixed")

# View
table_S1
```

## Table 1. 

```{r}
table_1 <- data |> 
  tbl_summary(
    include = c(
      sexo, wealth_3, DEP, etnia, AGP, PCR),
    by = patologia,
    percent = "row",
    statistic = list(
      all_continuous() ~ "{median} ({p25}, {p75})", 
      all_categorical() ~ "{n} ({p}%)"),
    digits = list(
      all_categorical() ~ c(0, 1)),
    missing_text = "no"
  ) |>
  add_overall() |>
  add_p(
    test = list(
      all_continuous() ~ "kruskal.test",
      all_categorical() ~ "chisq.test"
    )
  ) |> 
  # add_q(method = "BH") |>
  bold_p(t = 0.05) |>
  # Simple star for continuous (Mann-Whitney)
  modify_fmt_fun(
    p.value ~ function(x) paste0(style_pvalue(x, digits = 3), "**"),
    rows = var_type == "continuous"
  ) |>
  # Double star for categorical (Chi-square)
  modify_fmt_fun( 
    p.value ~ function(x) paste0(style_pvalue(x, digits = 3), "*"),
    rows = var_type %in% c("categorical", "dichotomous")
  ) |>
  modify_header(
    label = "**Características**",
    stat_1 = "**Normal**  \nN = {n} ({style_percent(p, digits = 1)}%)",
    stat_2 = "**Ferropenia temprana**  \nN = {n} ({style_percent(p, digits = 0)}%)",
    stat_3 = "**Anemia no ferropénica**  \nN = {n} ({style_percent(p, digits = 1)}%)",
    stat_4 = "**Anemia ferropénica**  \nN = {n} ({style_percent(p, digits = 1)}%)") |>
  modify_footnote(
    starts_with("p.value") ~ 
    "Prueba de Kruskal-Wallis (*); Prueba de Chi-cuadrado (**)."
  )

# View
table_1
```

## Table S2. Univariate regression models

```{r}
# Anemia
table_S2a <- data |>
  gtsummary::tbl_uvregression(
    include = c(etnia, wealth_3, sexo, educacion, DEP),
    method = glm,
    method.args = list(family = binomial(link = "log")),
    y = anemia,
    hide_n = TRUE,
    exponentiate = TRUE,
    conf.int = TRUE,
    conf.level = 0.95,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_p(t = 0.05)

# Ferropenia
table_S2b <- data |>
  gtsummary::tbl_uvregression(
    include = c(etnia, wealth_3, sexo, educacion, DEP),
    method = glm,
    method.args = list(family = binomial(link = "log")),
    y = ferropenia,
    hide_n = TRUE,
    exponentiate = TRUE,
    conf.int = TRUE,
    conf.level = 0.95,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_p(t = 0.05)

# Anemia no ferropénica
table_S2c <- data |>
  mutate(
    anemia_no_ferropenica = case_when(
      anemia == 1 & ferropenia == 0 ~ "Si",
      TRUE ~ "No"
    ),
    anemia_no_ferropenica = factor(
      anemia_no_ferropenica, levels = c("No", "Si"))
  ) |> 
  gtsummary::tbl_uvregression(
    include = c(etnia, wealth_3, sexo, educacion, DEP),
    method = glm,
    method.args = list(family = binomial(link = "log")),
    y = anemia_no_ferropenica,
    hide_n = TRUE,
    exponentiate = TRUE,
    conf.int = TRUE,
    conf.level = 0.95,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_p(t = 0.05)

# Anemia ferropénica
table_S2d <- data |>
  mutate(
    anemia_ferropenica = case_when(
      anemia == 1 & ferropenia == 1 ~ "Si",
      TRUE ~ "No"
    ),
    anemia_ferropenica = factor(
      anemia_ferropenica, levels = c("No", "Si"))
  ) |> 
  gtsummary::tbl_uvregression(
    include = c(etnia, wealth_3, sexo, educacion, DEP),
    method = glm,
    method.args = list(family = binomial(link = "log")),
    y = anemia_ferropenica,
    hide_n = TRUE,
    exponentiate = TRUE,
    conf.int = TRUE,
    conf.level = 0.95,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_p(t = 0.05)

# Merge tables
table_S2 <- tbl_merge(
  tbls = list(table_S2a, table_S2b, table_S2c, table_S2d),
  tab_spanner = c(
    "**Anemia**", "**Ferropenia**", "**Anemia no ferropénica**", "**Anemia ferropénica**")) |>
  modify_header(
    label = "**Características**",
    starts_with("estimate") ~ "**RPc (IC 95%)**") |>
  remove_abbreviation() |>
  modify_abbreviation("RP: Razón de prevalencia crudo; IC 95%: Intervalo de confianza al 95%")

# View
table_S2
```

## Table 2. Multivariable analysis

::: {style="text-align: justify"}
Incluir el departamento como una variable predictora (efecto fijo) es la mejor opción porque, dado el número reducido de unidades de nivel superior ($K=4$ clústeres/departamentos), un modelo de efectos mixtos no permite estimar de forma fiable la varianza inter-departamental ($\tau^2$). Asimismo, los estimadores de varianza robusta como `vcovCL` (basados en la matriz de covarianza `sándwich` asintótica tipo `HC0` a `HC3`) dependen de propiedades que requieren de 30 a 50 clusters clústeres para evitar la subestimación del error estándar y la consecuente inflación del error tipo I (falsos positivos). Incluso métodos diseñados para muestras pequeñas como `vcovCR` (ajuste tipo `CR2`), que pueden ser válidos a partir de 10 a 15 clústeres, resultan inestables con tan solo 4 unidades debido a la insuficiencia de grados de libertad efectivos (EDF). Al añadir el departamento directamente en la fórmula como efecto fijo, el modelo controla explícitamente la heterogeneidad geográfica de base, permitiendo comparaciones ajustadas (como Lima vs. otros departamentos) e inferencias válidas sobre la prevalencia de anemia y ferropenia.
::: 

```{r}
# Anemia
table_2a <-
  glm(
    anemia ~ etnia + wealth_3 + sexo + educacion + DEP, 
    data = data, 
    family = binomial(link = "log")
  ) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    conf.level = 0.95,
    tidy_fun = broom.helpers::tidy_parameters,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    estimate_fun = ~style_number(.x, digits = 2)
  ) |>
  # add_vif() |>
  bold_labels() |>
  bold_p(t = 0.05) |>
  modify_header(label = "**Caraterísticas**")

# Ferropenia
table_2b <-
  glm(
    ferropenia ~ etnia + wealth_3 + sexo + educacion + DEP,
    data = data,
    family = binomial(link = "log")
  ) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    conf.level = 0.95,
    tidy_fun = broom.helpers::tidy_parameters,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  # add_vif() |>
  bold_labels() |>
  bold_p(t = 0.05)

# Anemia no ferropénica
table_2c <- data |>
  mutate(
    anemia_no_ferropenica = case_when(
      anemia == 1 & ferropenia == 0 ~ "Si",
      TRUE ~ "No"
    ),
    anemia_no_ferropenica = factor(anemia_no_ferropenica, levels = c("No", "Si"))
  ) |>
  glm(
    anemia_no_ferropenica ~ etnia + wealth_3 + sexo + educacion + DEP,
    family = binomial(link = "log"), 
    data = _ 
  ) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    conf.level = 0.95,
    tidy_fun = broom.helpers::tidy_parameters,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    estimate_fun = ~style_number(.x, digits = 2)
  ) |>
  # add_vif() |>
  bold_labels() |>
  bold_p(t = 0.05)

# Anemia ferropénica
table_2d <- data |>
  mutate(
    anemia_ferropenica = case_when(
      anemia == 1 & ferropenia == 1 ~ "Si",
      TRUE ~ "No"
    ),
    anemia_ferropenica = factor(anemia_ferropenica, levels = c("No", "Si"))
  ) |>
  glm(
    anemia_ferropenica ~ etnia + wealth_3 + sexo + educacion + DEP,
    family = binomial(link = "log"), 
    data = _ 
  ) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    conf.level = 0.95,
    tidy_fun = broom.helpers::tidy_parameters,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    estimate_fun = ~style_number(.x, digits = 2)
  ) |>
  # add_vif() |>
  bold_labels() |>
  bold_p(t = 0.05)

# Merge tables
table_2 <- tbl_merge(
  tbls = list(table_2a, table_2b, table_2c, table_2d),
  tab_spanner = c(
    "**Anemia**", "**Ferropenia**", "**Anemia no ferropénica**", "**Anemia ferropénica**")) |>
  modify_header(
    label = "**Características**",
    starts_with("estimate") ~ "**RPa**", 
    starts_with("conf_low") ~ "**IC95%**") |>
  remove_abbreviation() |>
  modify_abbreviation("RP: Razón de prevalencia ajustado; IC 95%: Intervalo de confianza al 95%")

# View
table_2
```

### Anemia diagnosis model

```{r}
#| eval: false
# Modelo 1: SIN departamento 
m1 <- glm(
  anemia ~ etnia + wealth_3 + sexo + educacion,
  family = binomial(link = "log"),
  data = data
)

# Modelo 2: CON departamento (Recomendado)
m2 <- glm(
  anemia ~ etnia + wealth_3 + sexo + educacion + DEP,
  family = binomial(link = "log"),
  data = data
)

# Likelihood-Ratio-Test (LRT)
test_likelihoodratio(m1, m2)

# Model Performance Indices
model_performance(m1)
model_performance(m2)

# Comparison of Model Performance Indices
compare_performance(m1, m2, rank = TRUE, verbose = FALSE)

# Visualization of indices of models’ performance
plot(compare_performance(m1, m2, rank = TRUE, verbose = FALSE))

# Multicollinearity of model terms
check_collinearity(m2)
```

### Ferropenia diagnosis model

```{r}
#| eval: false
# Modelo 1: SIN departamento
m1 <- glm(
  ferropenia ~ etnia + wealth_3 + sexo + educacion,
  family = binomial(link = "log"),
  data = data
)

# Modelo 2: CON departamento (El recomendado)
m2 <- glm(
  ferropenia ~ etnia + wealth_3 + sexo + educacion + DEP,
  family = binomial(link = "log"),
  data = data
)

# Likelihood-Ratio-Test (LRT)
test_likelihoodratio(m1, m2)

# Model Performance Indices
model_performance(m1)
model_performance(m2)

# Comparison of Model Performance Indices
compare_performance(m1, m2, rank = TRUE, verbose = FALSE)

# Visualization of indices of models’ performance
plot(compare_performance(m1, m2, rank = TRUE, verbose = FALSE))

# Multicollinearity of model terms
check_collinearity(m2)
```

### Non-iron deficiency anemia diagnosis model

```{r}
#| eval: false
# Modelo 1: SIN departamento (El recomendado)
m1 <- data |>
  mutate(
    anemia_no_ferropenica = case_when(anemia == 1 & ferropenia == 0 ~ "Si", TRUE ~ "No"),
    anemia_no_ferropenica = factor(anemia_no_ferropenica, levels = c("No", "Si"))
  ) |>
  glm(
    anemia_no_ferropenica ~ etnia + wealth_3 + sexo + educacion,
    family = binomial(link = "log"),
    data = _
  )

# Modelo 2: CON departamento
m2 <- data |>
  mutate(
    anemia_no_ferropenica = case_when(anemia == 1 & ferropenia == 0 ~ "Si", TRUE ~ "No"),
    anemia_no_ferropenica = factor(anemia_no_ferropenica, levels = c("No", "Si"))
  ) |>
  glm(
    anemia_no_ferropenica ~ etnia + wealth_3 + sexo + educacion + DEP,
    family = binomial(link = "log"),
    data = _
  )

# Likelihood-Ratio-Test (LRT)
test_likelihoodratio(m1, m2)

# Model Performance Indices
model_performance(m1)
model_performance(m2)

# Comparison of Model Performance Indices
compare_performance(m1, m2, rank = TRUE, verbose = FALSE)

# Visualization of indices of models’ performance
plot(compare_performance(m1, m2, rank = TRUE, verbose = FALSE))

# Multicollinearity of model terms
check_collinearity(m2)
```

### Iron deficiency anemia diagnosis model

```{r}
#| eval: false
# Modelo 1: SIN departamento
m1 <- data |>
  mutate(
    anemia_ferropenica = case_when(anemia == 1 & ferropenia == 1 ~ "Si", TRUE ~ "No"),
    anemia_ferropenica = factor(anemia_ferropenica, levels = c("No", "Si"))
  ) |>
  glm(
    anemia_ferropenica ~ etnia + wealth_3 + sexo + educacion,
    family = binomial(link = "log"),
    data = _
  )

# Modelo 2: CON departamento (El recomendado)
m2 <- data |>
  mutate(
    anemia_ferropenica = case_when(anemia == 1 & ferropenia == 1 ~ "Si", TRUE ~ "No"),
    anemia_ferropenica = factor(anemia_ferropenica, levels = c("No", "Si"))
  ) |>
  glm(
    anemia_ferropenica ~ etnia + wealth_3 + sexo + educacion + DEP,
    family = binomial(link = "log"),
    data = _
  )

# Likelihood-Ratio-Test (LRT)
test_likelihoodratio(m1, m2)

# Model Performance Indices
model_performance(m1)
model_performance(m2)

# Comparison of Model Performance Indices
compare_performance(m1, m2, rank = TRUE, verbose = FALSE)

# Visualization of indices of models’ performance
plot(compare_performance(m1, m2, rank = TRUE, verbose = FALSE))

# Multicollinearity of model terms
check_collinearity(m1)
```

## Table S3. Mestizo

```{r}
# Anemia
table_S3a <- data |>
  filter(etnia == "Mestizo") |> 
  glm(
    anemia ~ wealth_3 + sexo + educacion + DEP, 
    family = binomial(link = "log"),
    data = _
  ) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    conf.level = 0.95,
    tidy_fun = broom.helpers::tidy_parameters,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    estimate_fun = ~style_number(.x, digits = 2)
  ) |>
  # add_vif() |>
  bold_labels() |>
  bold_p(t = 0.05)
  # modify_spanning_header(all_stat_cols() ~ "**Mestizo**")

# Ferropenia
table_S3b <- data |>
  filter(etnia == "Mestizo") |>
  glm(
    ferropenia ~ wealth_3 + sexo + educacion, 
    family = binomial(link = "log"),
    data = _
  ) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    conf.level = 0.95,
    tidy_fun = broom.helpers::tidy_parameters,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    estimate_fun = ~style_number(.x, digits = 2)
  ) |>
  # add_vif() |>
  bold_labels() |>
  bold_p(t = 0.05)

# Anemia no ferropénica
table_S3c <- data |>
  filter(etnia == "Mestizo") |>
  mutate(
    anemia_no_ferropenica = case_when(
      anemia == 1 & ferropenia == 0 ~ "Si",
      TRUE ~ "No"
    ),
    anemia_no_ferropenica = factor(anemia_no_ferropenica, levels = c("No", "Si"))
  ) |>
  glm(
    anemia_no_ferropenica ~ wealth_3 + sexo + educacion + DEP,
    family = binomial(link = "log"), 
    data = _ 
  ) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    conf.level = 0.95,
    tidy_fun = broom.helpers::tidy_parameters,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    estimate_fun = ~style_number(.x, digits = 2)
  ) |>
  # add_vif() |>
  bold_labels() |>
  bold_p(t = 0.05)

# Anemia ferropénica
table_S3d <- data |>
  filter(etnia == "Mestizo") |>
  mutate(
    anemia_ferropenica = case_when(
      anemia == 1 & ferropenia == 1 ~ "Si",
      TRUE ~ "No"
    ),
    anemia_ferropenica = factor(anemia_ferropenica, levels = c("No", "Si"))
  ) |>
  glm(
    anemia_ferropenica ~ wealth_3 + sexo + educacion + DEP,
    family = binomial(link = "log"), 
    data = _ 
  ) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    conf.level = 0.95,
    tidy_fun = broom.helpers::tidy_parameters,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    estimate_fun = ~style_number(.x, digits = 2)
  ) |>
  # add_vif() |>
  bold_labels() |>
  bold_p(t = 0.05)

# Merge tables
table_S3 <- tbl_merge(
  tbls = list(table_S3a, table_S3b, table_S3c, table_S3d),
  tab_spanner = c(
    "**Anemia**", "**Ferropenia**", "**Anemia no ferropénica**", "**Anemia ferropénica**"))

# View
table_S3
```

### Anemia diagnosis model

```{r}
#| eval: false
# Modelo 1: SIN departamento (Recomendado)
m1 <- data |>
  filter(etnia == "Mestizo") |> 
  glm(
    anemia ~ wealth_3 + sexo + educacion, 
    family = binomial(link = "log"),
    data = _
  )

# Modelo 2: CON departamento
m2 <- data |>
  filter(etnia == "Mestizo") |> 
  glm(
    anemia ~ wealth_3 + sexo + educacion + DEP, 
    family = binomial(link = "log"),
    data = _
  )

# Likelihood-Ratio-Test (LRT)
test_likelihoodratio(m1, m2)

# Model Performance Indices
model_performance(m1)
model_performance(m2)

# Comparison of Model Performance Indices
compare_performance(m1, m2, rank = TRUE, verbose = FALSE)

# Visualization of indices of models’ performance
plot(compare_performance(m1, m2, rank = TRUE, verbose = FALSE))

# Multicollinearity of model terms
check_collinearity(m2)
```

### Ferropenia diagnosis model

```{r}
#| eval: false
# Modelo 1: SIN departamento (Recomendado)
m1 <- data |>
  filter(etnia == "Mestizo") |> 
  glm(
    ferropenia ~ wealth_3 + sexo, 
    family = binomial(link = "log"),
    data = _
  )

# Modelo 2: CON departamento
m2 <- data |>
  filter(etnia == "Mestizo") |> 
  glm(
    ferropenia ~ wealth_3 + sexo + educacion, 
    family = binomial(link = "log"),
    data = _
  )

# Likelihood-Ratio-Test (LRT)
test_likelihoodratio(m1, m2)

# Model Performance Indices
model_performance(m1)
model_performance(m2)

# Comparison of Model Performance Indices
compare_performance(m1, m2, rank = TRUE, verbose = FALSE)

# Visualization of indices of models’ performance
plot(compare_performance(m1, m2, rank = TRUE, verbose = FALSE))

# Multicollinearity of model terms
check_collinearity(m2)
```

### Non-iron deficiency anemia diagnosis model

```{r}
#| eval: false
# Modelo 1: SIN departamento (El recomendado)
m1 <- data |>
  mutate(
    anemia_no_ferropenica = case_when(anemia == 1 & ferropenia == 0 ~ "Si", TRUE ~ "No"),
    anemia_no_ferropenica = factor(anemia_no_ferropenica, levels = c("No", "Si"))
  ) |>
  filter(etnia == "Mestizo") |> 
  glm(
    anemia_no_ferropenica ~ wealth_3 + sexo + educacion,
    family = binomial(link = "log"),
    data = _
  )

# Modelo 2: CON departamento
m2 <- data |>
  mutate(
    anemia_no_ferropenica = case_when(anemia == 1 & ferropenia == 0 ~ "Si", TRUE ~ "No"),
    anemia_no_ferropenica = factor(anemia_no_ferropenica, levels = c("No", "Si"))
  ) |>
  filter(etnia == "Mestizo") |> 
  glm(
    anemia_no_ferropenica ~ wealth_3 + sexo + educacion + DEP,
    family = binomial(link = "log"),
    data = _
  )

# Likelihood-Ratio-Test (LRT)
test_likelihoodratio(m1, m2)

# Model Performance Indices
model_performance(m1)
model_performance(m2)

# Comparison of Model Performance Indices
compare_performance(m1, m2, rank = TRUE, verbose = FALSE)

# Visualization of indices of models’ performance
plot(compare_performance(m1, m2, rank = TRUE, verbose = FALSE))

# Multicollinearity of model terms
check_collinearity(m1)
```

### Iron deficiency anemia diagnosis model

```{r}
#| eval: false
# Modelo 1: SIN departamento
m1 <- data |>
  mutate(
    anemia_ferropenica = case_when(anemia == 1 & ferropenia == 1 ~ "Si", TRUE ~ "No"),
    anemia_ferropenica = factor(anemia_ferropenica, levels = c("No", "Si"))
  ) |>
  filter(etnia == "Mestizo") |> 
  glm(
    anemia_ferropenica ~ wealth_3 + sexo + educacion,
    family = binomial(link = "log"),
    data = _
  )

# Modelo 2: CON departamento (El recomendado)
m2 <- data |>
  mutate(
    anemia_ferropenica = case_when(anemia == 1 & ferropenia == 1 ~ "Si", TRUE ~ "No"),
    anemia_ferropenica = factor(anemia_ferropenica, levels = c("No", "Si"))
  ) |>
  filter(etnia == "Mestizo") |> 
  glm(
    anemia_ferropenica ~ wealth_3 + sexo + educacion + DEP,
    family = binomial(link = "log"),
    data = _
  )

# Likelihood-Ratio-Test (LRT)
test_likelihoodratio(m1, m2)

# Model Performance Indices
model_performance(m1)
model_performance(m2)

# Comparison of Model Performance Indices
compare_performance(m1, m2, rank = TRUE, verbose = FALSE)

# Visualization of indices of models’ performance
plot(compare_performance(m1, m2, rank = TRUE, verbose = FALSE))

# Multicollinearity of model terms
check_collinearity(m1)
```

## Table S4. Quechua/Aymara	

```{r}
# Anemia
table_S4a <- data |>
  filter(etnia == "Quechua/Aymara") |> 
  glm(
    anemia ~ wealth_3 + sexo + educacion + DEP, 
    family = binomial(link = "log"),
    data = _
  ) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    conf.level = 0.95,
    tidy_fun = broom.helpers::tidy_parameters,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    estimate_fun = ~style_number(.x, digits = 2)
  ) |>
  # add_vif() |>
  bold_labels() |>
  bold_p(t = 0.05)

# Ferropenia
table_S4b <- data |>
  filter(etnia == "Quechua/Aymara") |>
  glm(
    ferropenia ~ wealth_3 + sexo + educacion + DEP, 
    family = binomial(link = "log"),
    data = _
  ) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    conf.level = 0.95,
    tidy_fun = broom.helpers::tidy_parameters,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    estimate_fun = ~style_number(.x, digits = 2)
  ) |>
  # add_vif() |>
  bold_labels() |>
  bold_p(t = 0.05)

# Anemia no ferropénica
table_S4c <- data |>
  filter(etnia == "Quechua/Aymara") |>
  mutate(
    anemia_no_ferropenica = case_when(
      anemia == 1 & ferropenia == 0 ~ "Si",
      TRUE ~ "No"
    ),
    anemia_no_ferropenica = factor(anemia_no_ferropenica, levels = c("No", "Si"))
  ) |>
  glm(
    anemia_no_ferropenica ~ wealth_3 + sexo + educacion + DEP,
    family = binomial(link = "log"), 
    data = _ 
  ) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    conf.level = 0.95,
    tidy_fun = broom.helpers::tidy_parameters,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    estimate_fun = ~style_number(.x, digits = 2)
  ) |>
  # add_vif() |>
  bold_labels() |>
  bold_p(t = 0.05)

# Anemia ferropénica
table_S4d <- data |>
  filter(etnia == "Quechua/Aymara") |>
  mutate(
    anemia_ferropenica = case_when(
      anemia == 1 & ferropenia == 1 ~ "Si",
      TRUE ~ "No"
    ),
    anemia_ferropenica = factor(anemia_ferropenica, levels = c("No", "Si"))
  ) |>
  glm(
    anemia_ferropenica ~ wealth_3 + sexo + educacion + DEP,
    family = binomial(link = "log"), 
    data = _ 
  ) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    conf.level = 0.95,
    tidy_fun = broom.helpers::tidy_parameters,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    estimate_fun = ~style_number(.x, digits = 2)
  ) |>
  # add_vif() |>
  bold_labels() |>
  bold_p(t = 0.05)

# Merge tables
table_S4 <- tbl_merge(
  tbls = list(table_S4a, table_S4b, table_S4c, table_S4d),
  tab_spanner = c(
    "**Anemia**", "**Ferropenia**", "**Anemia no ferropénica**", "**Anemia ferropénica**"))

# View
table_S4
```

### Anemia diagnosis model

```{r}
#| eval: false
# Modelo 1: SIN departamento
m1 <- data |>
  filter(etnia == "Quechua/Aymara") |> 
  glm(
    anemia ~ wealth_3 + sexo + educacion, 
    family = binomial(link = "log"),
    data = _
  )

# Modelo 2: CON departamento (Recomendado)
m2 <- data |>
  filter(etnia == "Quechua/Aymara") |> 
  glm(
    anemia ~ wealth_3 + sexo + educacion + DEP, 
    family = binomial(link = "log"),
    data = _
  )

# Likelihood-Ratio-Test (LRT)
test_likelihoodratio(m1, m2)

# Model Performance Indices
model_performance(m1)
model_performance(m2)

# Comparison of Model Performance Indices
compare_performance(m1, m2, rank = TRUE, verbose = FALSE)

# Visualization of indices of models’ performance
plot(compare_performance(m1, m2, rank = TRUE, verbose = FALSE))

# Multicollinearity of model terms
check_collinearity(m1)
```

### Ferropenia diagnosis model

```{r}
#| eval: false
# Modelo 1: SIN departamento
m1 <- data |>
  filter(etnia == "Quechua/Aymara") |> 
  glm(
    ferropenia ~ wealth_3 + sexo + educacion, 
    family = binomial(link = "log"),
    data = _
  )

# Modelo 2: CON departamento (Recomendado)
m2 <- data |>
  filter(etnia == "Quechua/Aymara") |> 
  glm(
    ferropenia ~ wealth_3 + sexo + educacion + DEP, 
    family = binomial(link = "log"),
    data = _
  )

# Likelihood-Ratio-Test (LRT)
test_likelihoodratio(m1, m2)

# Model Performance Indices
model_performance(m1)
model_performance(m2)

# Comparison of Model Performance Indices
compare_performance(m1, m2, rank = TRUE, verbose = FALSE)

# Visualization of indices of models’ performance
plot(compare_performance(m1, m2, rank = TRUE, verbose = FALSE))

# Multicollinearity of model terms
check_collinearity(m2)
```

### Non-iron deficiency anemia diagnosis model

```{r}
#| eval: false
# Modelo 1: SIN departamento (El recomendado)
m1 <- data |>
  mutate(
    anemia_no_ferropenica = case_when(anemia == 1 & ferropenia == 0 ~ "Si", TRUE ~ "No"),
    anemia_no_ferropenica = factor(anemia_no_ferropenica, levels = c("No", "Si"))
  ) |>
  filter(etnia == "Quechua/Aymara") |> 
  glm(
    anemia_no_ferropenica ~ wealth_3 + sexo + educacion,
    family = binomial(link = "log"),
    data = _
  )

# Modelo 2: CON departamento
m2 <- data |>
  mutate(
    anemia_no_ferropenica = case_when(anemia == 1 & ferropenia == 0 ~ "Si", TRUE ~ "No"),
    anemia_no_ferropenica = factor(anemia_no_ferropenica, levels = c("No", "Si"))
  ) |>
  filter(etnia == "Quechua/Aymara") |> 
  glm(
    anemia_no_ferropenica ~ wealth_3 + sexo + educacion + DEP,
    family = binomial(link = "log"),
    data = _
  )

# Likelihood-Ratio-Test (LRT)
test_likelihoodratio(m1, m2)

# Model Performance Indices
model_performance(m1)
model_performance(m2)

# Comparison of Model Performance Indices
compare_performance(m1, m2, rank = TRUE, verbose = FALSE)

# Visualization of indices of models’ performance
plot(compare_performance(m1, m2, rank = TRUE, verbose = FALSE))

# Multicollinearity of model terms
check_collinearity(m1)
```

### Iron deficiency anemia diagnosis model

```{r}
#| eval: false
# Modelo 1: SIN departamento
m1 <- data |>
  mutate(
    anemia_ferropenica = case_when(anemia == 1 & ferropenia == 1 ~ "Si", TRUE ~ "No"),
    anemia_ferropenica = factor(anemia_ferropenica, levels = c("No", "Si"))
  ) |>
  filter(etnia == "Quechua/Aymara") |> 
  glm(
    anemia_ferropenica ~ wealth_3 + sexo + educacion,
    family = binomial(link = "log"),
    data = _
  )

# Modelo 2: CON departamento (El recomendado)
m2 <- data |>
  mutate(
    anemia_ferropenica = case_when(anemia == 1 & ferropenia == 1 ~ "Si", TRUE ~ "No"),
    anemia_ferropenica = factor(anemia_ferropenica, levels = c("No", "Si"))
  ) |>
  filter(etnia == "Quechua/Aymara") |> 
  glm(
    anemia_ferropenica ~ wealth_3 + sexo + educacion + DEP,
    family = binomial(link = "log"),
    data = _
  )

# Likelihood-Ratio-Test (LRT)
test_likelihoodratio(m1, m2)

# Model Performance Indices
model_performance(m1)
model_performance(m2)

# Comparison of Model Performance Indices
compare_performance(m1, m2, rank = TRUE, verbose = FALSE)

# Visualization of indices of models’ performance
plot(compare_performance(m1, m2, rank = TRUE, verbose = FALSE))

# Multicollinearity of model terms
check_collinearity(m1)
```

## Table 3.

```{r}
# Anemia
table_a <- tbl_merge(tbls = list(table_S3a, table_S4a))
# Ferropenia
table_b <- tbl_merge(tbls = list(table_S3b, table_S4b))
# Anemia no ferropénica
table_c <- tbl_merge(tbls = list(table_S3c, table_S4c))
# Anemia ferropénica
table_d <- tbl_merge(tbls = list(table_S3d, table_S4d))

# Stack tables
table_3_base <- tbl_merge(tbls = list(table_a, table_b, table_c, table_d))

# Triple header
table_3 <- table_3_base |>
  as_flex_table() |>
  delete_part(part = "header") |>
  
  # Level 1: Estimates and 95% CI
  add_header_row(
    values = c(
      "Determinantes Sociales", 
      rep(c("RPa (IC 95%)", "Valor p"), 8) 
    )
  ) |>
  
  # Level 2: Ethnicity (Mestizo y Quechua/Aymara)
  add_header_row(
    values = c(
      "", # Espacio sobre la columna de variables
      rep(c("Mestizo", "Mestizo", "Quechua/Aymara", "Quechua/Aymara"), 4)
    )
  ) |>
  
  # Level 3: Las Enfermedades
  # Cada enfermedad cubre 4 columnas (2 de mestizo + 2 de quechua)
  add_header_row(
    values = c(
      "",
      rep("Anemia", 4),
      rep("Ferropenia", 4),
      rep("Anemia no ferropénica", 4),
      rep("Anemia ferropénica", 4)
    )
  ) |>
  
  # Fusionar horizontalmente (donde hay textos repetidos como "Anemia" o "Mestizo")
  merge_h(part = "header") |>
  # Fusionar verticalmente (para que "Determinantes Sociales" ocupe las 3 filas)
  merge_v(part = "header") |>
  
  # Theme
  theme_vanilla() |>
  align(align = "center", part = "header") |>
  align(j = 1, align = "left", part = "header") |>
  fontsize(size = 8, part = "all") |>
  # Forzamos el diseño 'autofit' (esto es lo que emula la opción de Word)
  set_table_properties(layout = "autofit", width = 1)

# Definir las propiedades de la sección (Horizontal)
sect_properties <- prop_section(
  page_size = page_size(orient = "landscape"),
  page_margins = page_mar(bottom = 0.5, top = 0.5, right = 0.5, left = 0.5),
  type = "continuous"
)

# View
table_3
```

## RERI

```{r}

```

## Marginal effects

### Linear Model (Naive model)

#### Anemia

```{r}
#| fig-height: 4
#| fig-width: 8
# Model
mod_anemia <- glm(
  P037 ~ etnia + wealth_3 + sexo + educacion + DEP, 
  data = data, family = binomial(link = "log"))

# Model summary
summary(mod_anemia)
tidy(mod_anemia, exponentiate = TRUE, conf.int = TRUE)

# Predicted values
fitted_glm_1 <- predict_response(
  mod_anemia, terms = c("wealth_3", "etnia"), margin = "empirical")

fitted_glm_2 <- predict_response(
  mod_anemia, terms = c("educacion", "etnia"), margin = "empirical")

# Plot
a1_mod_anemia <- plot(fitted_glm_1)
a2_mod_anemia <- plot(fitted_glm_2)

# View
ggarrange(
  a1_mod_anemia, a2_mod_anemia, ncol = 2, nrow = 1, 
  common.legend = TRUE, legend = "bottom")
```

#### Ferropenia

```{r}
#| fig-height: 4
#| fig-width: 8
# Model
mod_ferropenia <- glm(
  ferropenia ~ etnia + wealth_3 + sexo + educacion + DEP, 
  data = data, family = binomial(link = "log"))

# Model summary
summary(mod_ferropenia)
tidy(mod_ferropenia, exponentiate = TRUE, conf.int = TRUE)

# Predicted values
fitted_glm_1 <- predict_response(
  mod_ferropenia, terms = c("wealth_3", "etnia"), margin = "empirical")

fitted_glm_2 <- predict_response(
  mod_ferropenia, terms = c("educacion", "etnia"), margin = "empirical")

# Plot
a1_mod_ferropenia <- plot(fitted_glm_1)
a2_mod_ferropenia <- plot(fitted_glm_2)

# View
ggarrange(
  a1_mod_ferropenia, a2_mod_ferropenia, ncol = 2, nrow = 1,
  common.legend = TRUE, legend = "bottom")
```

#### Non-iron deficiency anemia

```{r}
#| fig-height: 4
#| fig-width: 8
# Model
mod_anemia_no_ferropenica <- data |>
  mutate(
    anemia_no_ferropenica = case_when(anemia == 1 & ferropenia == 0 ~ "Si", TRUE ~ "No"),
    anemia_no_ferropenica = factor(anemia_no_ferropenica, levels = c("No", "Si"))
  ) |>
  glm(
    anemia_no_ferropenica ~ etnia + wealth_3 + sexo + educacion + DEP,
    family = binomial(link = "log"),
    data = _
  )

# Model summary
summary(mod_anemia_no_ferropenica)
tidy(mod_anemia_no_ferropenica, exponentiate = TRUE, conf.int = TRUE)

# Predicted values
fitted_glm_1 <- predict_response(
  mod_anemia_no_ferropenica, terms = c("wealth_3", "etnia"), margin = "empirical")

fitted_glm_2 <- predict_response(
  mod_anemia_no_ferropenica, terms = c("educacion", "etnia"), margin = "empirical")

# Plot
a1_no_ferropenica <- plot(fitted_glm_1)
a2_no_ferropenica <- plot(fitted_glm_2)

# View
ggarrange(
  a1_no_ferropenica, a2_no_ferropenica, ncol = 2, nrow = 1,
  common.legend = TRUE, legend = "bottom")
```

#### Iron deficiency anemia

```{r}
#| fig-height: 4
#| fig-width: 8
# Model
mode_anemia_ferropenica <- data |>
  mutate(
    anemia_ferropenica = case_when(anemia == 1 & ferropenia == 1 ~ "Si", TRUE ~ "No"),
    anemia_ferropenica = factor(anemia_ferropenica, levels = c("No", "Si"))
  ) |>
  glm(
    anemia_ferropenica ~ etnia + wealth_3 + sexo + educacion + DEP,
    family = binomial(link = "log"),
    data = _
  )
# Model summary
summary(mode_anemia_ferropenica)
tidy(mode_anemia_ferropenica, exponentiate = TRUE, conf.int = TRUE)

# Predicted values
fitted_glm_1 <- predict_response(
  mode_anemia_ferropenica, terms = c("wealth_3", "etnia"), margin = "empirical")

fitted_glm_2 <- predict_response(
  mode_anemia_ferropenica, terms = c("educacion", "etnia"), margin = "empirical")

# Plot
a1_anemia_ferropenica <- plot(fitted_glm_1)
a2_anemia_ferropenica <- plot(fitted_glm_2)

# View
ggarrange(
  a1_anemia_ferropenica, a2_anemia_ferropenica, ncol = 2, nrow = 1,
  common.legend = TRUE, legend = "bottom")
```

#### Figure 1

```{r}
#| fig-height: 12
#| fig-width: 10
F1 <- ggarrange(
  a1_mod_anemia, a1_mod_ferropenia, a1_no_ferropenica, a1_anemia_ferropenica,
  a2_mod_anemia, a2_mod_ferropenia, a2_no_ferropenica, a2_anemia_ferropenica,
  ncol = 2, nrow = 4, common.legend = TRUE, widths = c(1, 1))

# View
F1
```

### Restricted cubic spline (natural spline)

#### Anemia

```{r}
#| fig-height: 8
#| fig-width: 8
# Model
rcs_anemia <- glm(
  anemia ~ rcs(ferr_adj, 3) + etnia + wealth_3 + sexo + educacion + DEP, 
  data = data, family = binomial(link = "logit"))

# Model summary
summary(rcs_anemia)
tidy(rcs_anemia, exponentiate = TRUE, conf.int = TRUE)

# Predicted values
fitted_rcs_1 <- predict_response(
  rcs_anemia, terms = c("ferr_adj", "wealth_3", "etnia"), margin = "empirical")

fitted_rcs_2 <- predict_response(
  rcs_anemia, terms = c("ferr_adj", "educacion", "etnia"), margin = "empirical")

# Plot
a1_rcs_anemia <- plot(fitted_rcs_1)
a2_rcs_anemia <- plot(fitted_rcs_2)

# View
ggarrange(
  a1_rcs_anemia, a2_rcs_anemia, ncol = 1, nrow = 2, 
  common.legend = FALSE, legend = "right")
```

#### Ferropenia

```{r}
#| fig-height: 8
#| fig-width: 8
# Model
rcs_ferropenia <- glm(
  ferropenia ~ rcs(P037, 3) + etnia + wealth_3 + sexo + educacion + DEP,
  data = data, family = binomial(link = "logit"))

# Model summary
summary(rcs_ferropenia)
tidy(rcs_ferropenia, exponentiate = TRUE, conf.int = TRUE)

# Predicted values
fitted_rcs_1 <- predict_response(
  rcs_ferropenia, terms = c("P037", "wealth_3", "etnia"), margin = "empirical")

fitted_rcs_2 <- predict_response(
  rcs_ferropenia, terms = c("P037", "educacion", "etnia"), margin = "empirical")

# Plot
a1_rcs_ferropenia <- plot(fitted_rcs_1)
a2_rcs_ferropenia <- plot(fitted_rcs_2)

# View
ggarrange(
  a1_rcs_ferropenia, a2_rcs_ferropenia, ncol = 1, nrow = 2, 
  common.legend = FALSE, legend = "right")
```

#### Non-iron deficiency anemia

```{r}
#| fig-height: 8
#| fig-width: 8
# Model
rcs_anemia_no_ferropenica <- data |>
  mutate(
    anemia_no_ferropenica = case_when(anemia == 1 & ferropenia == 0 ~ "Si", TRUE ~ "No"),
    anemia_no_ferropenica = factor(anemia_no_ferropenica, levels = c("No", "Si"))
  ) |>
  glm(
    anemia_no_ferropenica ~ rcs(ferr_adj, 3) + etnia + wealth_3 + sexo + educacion + DEP,
    family = binomial(link = "logit"),
    data = _
  )

# Model summary
summary(rcs_anemia_no_ferropenica)
tidy(rcs_anemia_no_ferropenica, exponentiate = TRUE, conf.int = TRUE)

# Predicted values
fitted_rcs_1 <- predict_response(
  rcs_anemia_no_ferropenica, terms = c("ferr_adj", "wealth_3", "etnia"), margin = "empirical")

fitted_rcs_2 <- predict_response(
  rcs_anemia_no_ferropenica, terms = c("ferr_adj", "educacion", "etnia"), margin = "empirical")

# Plot
a1_rcs_no_ferropenica <- plot(fitted_rcs_1)
a2_rcs_no_ferropenica <- plot(fitted_rcs_2)

# View
ggarrange(
  a1_rcs_no_ferropenica, a2_rcs_no_ferropenica, ncol = 1, nrow = 2, 
  common.legend = FALSE, legend = "right")
```

#### Iron deficiency anemia

```{r}
#| fig-height: 8
#| fig-width: 8
# Model
rcs_anemia_ferropenica <- data |>
  mutate(
    anemia_ferropenica = case_when(anemia == 1 & ferropenia == 1 ~ "Si", TRUE ~ "No"),
    anemia_ferropenica = factor(anemia_ferropenica, levels = c("No", "Si"))
  ) |>
  glm(
    anemia_ferropenica ~ rcs(P037, 3) + etnia + wealth_3 + sexo + educacion + DEP,
    family = binomial(link = "logit"),
    data = _
  )
# Model summary
summary(rcs_anemia_ferropenica)
tidy(rcs_anemia_ferropenica, exponentiate = TRUE, conf.int = TRUE)

# Predicted values
fitted_rcs_1 <- predict_response(
  rcs_anemia_ferropenica, terms = c("P037", "wealth_3", "etnia"), margin = "empirical")

fitted_rcs_2 <- predict_response(
  rcs_anemia_ferropenica, terms = c("P037", "educacion", "etnia"), margin = "empirical")

# Plot
a1_rcs_anemia_ferropenica <- plot(fitted_rcs_1)
a2_rcs_anemia_ferropenica <- plot(fitted_rcs_2)

# View
ggarrange(
  a1_rcs_anemia_ferropenica, a2_rcs_anemia_ferropenica, ncol = 1, nrow = 2, 
  common.legend = FALSE, legend = "right")
```

### GAM (Cubic Regression Splines and REML)

#### Anemia

```{r}
#| fig-height: 8
#| fig-width: 8
# Model
gam_anemia <- gam(
  anemia ~ 
    s(ferr_adj, k = -1, bs = "cr") + etnia + wealth_3 + sexo + educacion + DEP, 
  data = data, family = binomial(link = "logit"), method = "REML", select = TRUE)

# Model summary
summary(gam_anemia)
tidy(gam_anemia, exponentiate = TRUE, conf.int = TRUE)

# Predicted values
fitted_gam_1 <- predict_response(
  gam_anemia, terms = c("ferr_adj", "wealth_3", "etnia"), margin = "empirical")

fitted_gam_2 <- predict_response(
  gam_anemia, terms = c("ferr_adj", "educacion", "etnia"), margin = "empirical")

# Plot
a1_gam_anemia <- plot(fitted_gam_1)
a2_gam_anemia <- plot(fitted_gam_2)

# View
ggarrange(
  a1_gam_anemia, a2_gam_anemia, ncol = 1, nrow = 2, 
  common.legend = FALSE, legend = "right")
```

#### Ferropenia

```{r}
#| fig-height: 8
#| fig-width: 8
# Model
gam_ferropenia <- gam(
  ferropenia ~ 
    s(P037, k = -1, bs = "cr") + etnia + wealth_3 + sexo + educacion + DEP, 
  data = data, family = binomial(link = "logit"), method = "REML", select = TRUE)

# Model summary
summary(gam_ferropenia)
tidy(gam_ferropenia, exponentiate = TRUE, conf.int = TRUE)

# Predicted values
fitted_gam_1 <- predict_response(
  gam_ferropenia, terms = c("P037", "wealth_3", "etnia"), margin = "empirical")

fitted_gam_2 <- predict_response(
  gam_ferropenia, terms = c("P037", "educacion", "etnia"), margin = "empirical")

# Plot
a1_gam_ferropenia <- plot(fitted_gam_1)
a2_gam_ferropenia <- plot(fitted_gam_2)

# View
ggarrange(
  a1_gam_ferropenia, a1_gam_ferropenia, ncol = 1, nrow = 2, 
  common.legend = FALSE, legend = "right")
```

#### Non-iron deficiency anemia

```{r}
#| fig-height: 8
#| fig-width: 8
# Model
gam_anemia_no_ferropenica <- data |>
  mutate(
    anemia_no_ferropenica = case_when(anemia == 1 & ferropenia == 0 ~ "Si", TRUE ~ "No"),
    anemia_no_ferropenica = factor(anemia_no_ferropenica, levels = c("No", "Si"))
  ) |>
  gam(
    anemia_no_ferropenica ~ 
      s(ferr_adj, k = -1, bs = "cr") + etnia + wealth_3 + sexo + educacion + DEP,
    family = binomial(link = "logit"),
    data = _,
    method = "REML",
    select = TRUE
  )

# Model summary
summary(gam_anemia_no_ferropenica)
tidy(gam_anemia_no_ferropenica, exponentiate = TRUE, conf.int = TRUE)

# Predicted values
fitted_gam_1 <- predict_response(
  gam_anemia_no_ferropenica, terms = c("ferr_adj", "wealth_3", "etnia"), margin = "empirical")

fitted_gam_2 <- predict_response(
  gam_anemia_no_ferropenica, terms = c("ferr_adj", "educacion", "etnia"), margin = "empirical")

# Plot
a1_gam_no_ferropenica <- plot(fitted_gam_1)
a2_gam_no_ferropenica <- plot(fitted_gam_2)

# View
ggarrange(
  a1_gam_no_ferropenica, a2_gam_no_ferropenica, ncol = 1, nrow = 2, 
  common.legend = FALSE, legend = "right")
```

#### Iron deficiency anemia

```{r}
#| fig-height: 8
#| fig-width: 8
# Model
mode_anemia_ferropenica <- data |>
  mutate(
    anemia_ferropenica = case_when(anemia == 1 & ferropenia == 1 ~ "Si", TRUE ~ "No"),
    anemia_ferropenica = factor(anemia_ferropenica, levels = c("No", "Si"))
  ) |>
  gam(
    anemia_ferropenica ~
      s(P037, k = -1, bs = "cr") + etnia + wealth_3 + sexo + educacion + DEP,
    family = binomial(link = "logit"),
    data = _,
    method = "REML",
    select = TRUE
  )
# Model summary
summary(mode_anemia_ferropenica)
tidy(mode_anemia_ferropenica, exponentiate = TRUE, conf.int = TRUE)

# Predicted values
fitted_gam_1 <- predict_response(
  mode_anemia_ferropenica, terms = c("P037", "wealth_3", "etnia"), margin = "empirical")

fitted_gam_2 <- predict_response(
  mode_anemia_ferropenica, terms = c("P037", "educacion", "etnia"), margin = "empirical")

# Plot
a1_gam_anemia_ferropenica <- plot(fitted_gam_1)
a2_gam_anemia_ferropenica <- plot(fitted_gam_2)

# View
ggarrange(
  a1_gam_anemia_ferropenica, a2_gam_anemia_ferropenica, ncol = 1, nrow = 2, 
  common.legend = FALSE, legend = "right")
```

# Save outputs

## Tables

```{r}
# Tables
save_as_docx(
  table_1,
  align = "center",
  path = here("outputs", "Table_1.docx"))

save_as_docx(
  table_2,
  align = "center",
  path = here("outputs", "Table_2.docx"))

save_as_docx(
  table_3,
  align = "center",
  path = here("outputs", "Table_3.docx"),
  pr_section = sect_properties)

# Supplementary tables
save_as_docx(
  table_S1,
  align = "center",
  path = here("outputs", "Table_S1.docx"))

save_as_docx(
  table_S2,
  align = "center",
  path = here("outputs", "Table_S2.docx"))

save_as_docx(
  table_S3,
  align = "center",
  path = here("outputs", "Table_S3.docx"))

save_as_docx(
  table_S4,
  align = "center",
  path = here("outputs", "Table_S4.docx"))

```

## Figures

```{r}

```

