---
title: "Ferritina"
author: "Carlos Ballón-Salcedo"
date: "`r Sys.Date()`"
format:
  html:
    theme: 
     light: lux
     dark: darkly
    toc: true
    toc-depth: 3
    code-overflow: wrap
    include-after-body: zoom_in_out.js
    highlight-style: github
    number-sections: true
    code-fold: true
    code-tools: 
      source: "https://github.com/Carlos-Ballon/ferritin-anemia_diagnosis.git"
    embed-resources: true
editor: source
execute:
  message: false
  warning: false
bibliography: grateful-refs.bib
csl: vancouver.csl
lang: en
---

# Load packages

```{r}
# Packages
pacman::p_load(
  tidyverse,
  rio,
  here,
  epiDisplay,
  Hmisc,
  ggplot2,
  psych,
  factoextra,
  ggpubr,
  rms,
  broom,
  ggeffects,
  rfextras,
  grateful,
  flextable,
  janitor,
  performance,
  gtsummary,
  finalfit,
  mgcv,
  officer,
  ggtext,
  Gifi,
  eulerr,
  ggsci,
  psych,
  ggrepel,
  ggplotify)
```

```{r}
#| eval: false
# Citations
grateful::cite_packages(
  output = "file",
  out.format = "docx",
  out.dir = ".",
  citation.style = "vancouver")
```

```{r}
# Set gtsummary theme
theme_gtsummary_journal(journal = "jama")

# Set gtsummary language
theme_gtsummary_language(language = "en")
```

# Import data

```{r}
#| eval: true
#| echo: true
#| results: false
# Data
data <- import(here("data", "base_de_curvas.dta")) |>
  tibble::rownames_to_column(var = "ID1")

# Scripts
# rfextras::load_scripts()
source(here("scripts", "wealth index_catpca.R"))
source(here("scripts", "models.R"))
source(here("scripts", "marginal effects.R"))
```

# Process data

```{r}
# Select categorical variables (to factor)
vars <- c(
  "P001", "P002", "P004", "P005", "P006", "P007", "P008", "P009", "P010", "P011",
  "P012", "P013", "P014", "P015", "P018", "P019", "P020", "P021", "P022", "P023",
  "P024", "P025", "P028", "P029")

data <- data |>
  dplyr::filter(P015 %in% c(1, 2, 6)) |>
  mutate(
    across(all_of(vars), ~ replace(.x, .x >= 99, NA)),
    
    anemia = if_else(P037 < 10.5, 1L, 0L, missing = NA_integer_),
    
    ferropenia = if_else(ferr_adj < 12, 1L, 0L, missing = NA_integer_),
    
    anemia_no_ferropenica = if_else(
      anemia == 1L & ferropenia == 0L, 1L, 0L, missing = NA_integer_),
    
    anemia_ferropenica = if_else(
      anemia == 1L & ferropenia == 1L, 1L, 0L, missing = NA_integer_),
    
    hematological_states = case_when(
      anemia == 1 & ferropenia == 1 ~ "Iron-deficiency anemia", 
      anemia == 1 & ferropenia == 0 ~ "Non-iron-deficiency anemia", 
      anemia == 0 & ferropenia == 1 ~ "Iron Deficiency",
      anemia == 0 & ferropenia == 0 ~ "No deficiencies", 
      TRUE ~ "Another"
    ) |> 
      fct_relevel(
        "No deficiencies", "Iron Deficiency", 
        "Non-iron-deficiency anemia", "Iron-deficiency anemia") |>
      ff_label("Hematological status"),
    
    sexo = factor(P001) |> 
      fct_recode("Male" = "1", "Female" = "2") |> 
      fct_relevel("Male", "Female") |> 
      ff_label("Sex of children"),
    
    etnia = case_match(as.character(P015),
      c("1", "2") ~ "Quechua/Aymara",
      "6" ~ "Mestizo",
      .default = NA_character_
    ) |> 
      fct_relevel("Mestizo", "Quechua/Aymara") |> 
      ff_label("Ethnic group"),
    
    seguro_infante = case_match(as.character(P002),
      c("1", "2", "3") ~ "Publics (SIS, EsSalud, FFAA)",
      c("4", "5") ~ "Private",
      c("6", "7", "99") ~ "None or no answer",
      .default = NA_character_
    ) |>
      fct_relevel("Publics (SIS, EsSalud, FFAA)", "Private", "None or no answer") |>
      ff_label("Child Health Insurance"), 
    
    educacion = case_match(as.character(P007), 
      c("0", "1", "2") ~ "None or primary", "3" ~ "Secondary", 
      c("4", "5") ~ "Higher",
      .default = NA_character_) |>
      fct_relevel("None or primary", "Secondary", "Higher") |>
      ff_label("Level of education"),
    
    DEP = factor(DEP) |>
      fct_relevel("Arequipa", "Lima", "Cusco", "Puno") |>
      ff_label("Department"),
    
    altura_cat = case_when(
      P017 < 1500  ~ "< 1500",
      P017 >= 1500 & P017 < 3000 ~ "1500 - 2999",
      P017 >= 3000 & P017 < 3500 ~ "3000 - 3499",
      P017 >= 3500 ~ ">= 3500",
      TRUE ~ NA_character_
    ) |>
      fct_relevel("< 1500", "1500 - 2999", "3000 - 3499", ">= 3500") |>
      ff_label("Elevation (m a.s.l.)"), 
    
    anemia_oms2024 = if_else(anemia == 1, "Si", "No") |> 
      fct_relevel("No", "Si") |> 
      ff_label("Anemia (WHO 2024, adjusted)"),
    
    ferropenia_brinda = if_else(ferropenia == 1, "Si", "No") |>
      fct_relevel("No", "Si") |>
      ff_label("Iron Deficiency (BRINDA Method)"),
    
    vitamina_A = if_else(
      P033 < 0.70, "Deficiencia de Vitamina A", "Suficiente") |>
      fct_relevel("Suficiente", "Deficiencia de Vitamina A") |>
      ff_label("Deficiencia de Vitamina A"),
    
    suplemento = case_match(as.character(P029), 
      "1" ~ "Si", 
      "2" ~ "No", 
      .default = NA_character_) |>
      fct_relevel("No", "Si") |>
      ff_label("Suplementación con de hierro"),
    
    across(all_of(setdiff(vars, c("P015", "P007", "P002", "P001", "P029"))), as_factor),
    
    edad_madre = ff_label(P003, "Mother's age"),
    
    wealth_5 = ff_label(wealth_5, "Wealth index"),
    
    wealth_3 = ff_label(wealth_3, "Wealth index"),
    
    sTfR_cat = ff_label(P032, "Soluble transferrin receptor"),
   
    AGP = ff_label(P034, "Alpha-1-acid glycoprotein (g/L)"),
    
    PCR = ff_label(P035, "C-reactive protein (g/L) (mg/L)"),
    
    reserva_hierro = ff_label(P036, "Estado del hierro corporal total")
  ) |>
  dplyr::select(ID1, DEP, P037:PCR)
```

# Data dictionary

```{r}
#| eval: false
# Generate a dictionary
labelled::generate_dictionary(data)

# Inspect variable labels and data.frame structure
Hmisc::contents(data)      # data.frame of variable types and missing values
dplyr::glimpse(data)       # compact structure
str(data)                  # detailed structure

# Inspect labels of specific variables
attributes(data$P001)
haven::var_labels(data$P001)
```

# Exploratory Data Analysis

::: {style="text-align: justify"}
Several R packages provide functions with identical names, such as `describe()` in the `Hmisc` package and `describe()` in the `psych` package. The first function performs descriptive analysis by providing robust estimators and shape metrics, such as the interquartile range (IQR), trimmed mean, median absolute deviation (MAD), skewness, and kurtosis. In contrast, the second function provides a distribution profile using percentiles, Gini's mean difference (Gdm), and the pseudomedian (pMedian), while also facilitating data screening with diagnostics for unique and missing values. The `epiDisplay` package also provides functions inspired by **Stata**, such as `summ()`. Additional valuable resources include the `janitor` package for data cleaning, as well as initiatives like the R Epidemics Consortium (RECON), Epiverse-TRACE, and the R4EPI project, which provide specialized tools for epidemiological research and analysis.
:::

## Categorical data

```{r}
#| eval: false
# Select categorical variables (factors)
categorical_vars <- data |>
  dplyr::select(where(\(x) is.character(x) | is.factor(x)))
```

### Stucture of categorical variables

```{r}
#| eval: false
# Statistical description (display labels)
Hmisc::describe(categorical_vars, exclude.missing = FALSE)
```

### Missing values and complete cases

```{r}
#| eval: false
# Count of missing values by column (vector)
colSums(is.na(categorical_vars))

# List of complete values by column
lapply(categorical_vars, function(x)
  sum(complete.cases(x)))

# Columns without missing values (vector)
colnames(categorical_vars)[sapply(categorical_vars, function(x)
  all(!is.na(x)))]
```

### Duplicate elements

::: {style="text-align: justify"}
The `duplicated()` function identifies duplicate elements, `unique()` extracts unique elements, and `distinct()` from dplyr package removes duplicate rows from a data frame.
:::

### Descriptive analysis: Measures of frequency and proportions

```{r}
#| eval: false
# Absolute frequency for categorical variables
lapply(categorical_vars, function(x)
  addmargins(table(x, useNA = "ifany")))

# Relative frequency for categorical variables
lapply(categorical_vars, function(x)
  round(addmargins(prop.table(table(x)) * 100), 1))
  
# Absolute frequency for categorical variables by anemia
lapply(categorical_vars, function(x)
  addmargins(table(x, categorical_vars$anemia)))

# Janitor with flextable
categorical_vars |>
  tabyl(anemia, ferropenia) |>
  adorn_totals(where = "both") |>
  adorn_percentages(denominator = "col") |>
  adorn_pct_formatting() |>
  adorn_ns(position = "front") |>
  flextable() |>
  autofit()
```

## Numerical data

```{r}
#| eval: false
# Selection of variables
numerical_vars <- data |>
  dplyr::select(where(\(x) is.numeric(x)), anemia, ferropenia)
```

#### Descriptive statistics: Summary statistics

```{r}
#| eval: false
# Compact
numerical_vars |> epiDisplay::summ(digits = 2, na.rm = FALSE)

# Detailed
numerical_vars |> psych::describe(na.rm = FALSE, IQR = TRUE, quant = c(.25,.75))

# Percentiles
numerical_vars |> Hmisc::describe()
quantile(data$P037, probs = seq(0, 1, by = 0.1), na.rm = TRUE)
quantile(data$P037, probs = c(0.25, 0.5, 0.75), na.rm = TRUE)
```

#### Descriptive statistics: Grouped summary statistics

```{r}
#| eval: false
# Anemia
numerical_vars |>
  dplyr::group_split(anemia) |>
  lapply(function(data)
    summ(numerical_vars, digits = 2, na.rm = TRUE))

# Ferropenia
numerical_vars |>
  dplyr::group_split(ferropenia) |>
  lapply(function(data)
    summ(numerical_vars, digits = 2, na.rm = TRUE))
```

# Produce outputs

Anemia no relacionada con ferropenia

Objetivo: Evaluar las brechas entre grupos etnicos relacionadas con la anemia no ferropenica según el SES

Evaluar si la etica se asocia a la ferropenia

Evaluar si la asociación entre el Wealth index del hogar y la prevalencia de anemia y ferropenia infantil difiere según la pertenencia étnica (mestizos, quechuas y aymaras)

Evaluar si la etnicidad se asocia (o influye) a la prevalencia de anemia o ferropenia infantil

Evaluar si la etnicidad se asocia a la prevalencia de ferropenia infantil

Anemia, anemia ferropenica, anemia no ferropenica, ferropenia. El mensaje seria "En el gradiente, tener un mejor SES reduce los niveles de anemia, pero la brecha por etnicidad es más grande en ferropenia que en anemia no ferropenica y probablemente que en anemia".

Posible resultado: La brecha es mas grande en ferropenia que en anemia no ferropenica

El muestreo nace en el establecimento de salud, basado en el CRED

## Table 1. 

```{r}
table_1 <- data |> 
  tbl_summary(
    include = c(edad_madre, sexo, wealth_3, educacion, DEP, etnia, AGP, PCR),
    by = hematological_states,
    percent = "column",
    statistic = list(
      all_continuous() ~ "{median} ({p25}, {p75})", 
      all_categorical() ~ "{n} ({p}%)"),
    digits = list(
      all_categorical() ~ c(0, 1)),
    missing_text = "no"
  ) |>
  add_overall() |>
  add_p(
    test = list(
      all_continuous() ~ "kruskal.test",
      all_categorical() ~ "chisq.test",
      c(wealth_3, educacion) ~ "kruskal.test"
    )
  ) |> 
  # add_q(method = "BH") |>
  bold_p(t = 0.05) |>
  # Simple star for Kruskal-Wallis rank sum test
  modify_fmt_fun(
    p.value ~ function(x) ifelse(is.na(x), "",paste0(style_pvalue(x, digits = 3), "*")),
    rows = variable %in% c("wealth_3", "educacion") | var_type == "continuous"
  ) |>
  # Double star for Chi-square test
  modify_fmt_fun( 
    p.value ~ function(x) ifelse(is.na(x), "",paste0(style_pvalue(x, digits = 3), "**")),
    rows = var_type %in% c("categorical", "dichotomous") & 
      !(variable %in% c("wealth_3", "educacion"))
  ) |>
  modify_header(
    label = "**Characteristics**",
    stat_0 = "**Total** \nN = {n}",
    stat_1 = "**No deficiencies**  \nN = {n} ({style_percent(p, digits = 1)}%)",
    stat_2 = "**Iron Deficiency**  \nN = {n} ({style_percent(p, digits = 0)}%)",
    stat_3 = "**Non-iron-deficiency anemia**  \nN = {n} ({style_percent(p, digits = 1)}%)",
    stat_4 = "**Iron-deficiency anemia**  \nN = {n} ({style_percent(p, digits = 1)}%)") |>
  modify_footnote(
    starts_with("p.value") ~ 
    "Kruskal-Wallis test (*); Chi-square test (**)."
  ) |>
  as_flex_table() |>
  theme_booktabs() |>
  fontsize(size = 9, part = "all") |>
  align(align = "center", part = "all") |>
  align(align = "left", part = "footer") |>
  align(j = 1, align = "left", part = "body") |>
  padding(padding.top = 0.5, padding.bottom = 0.5, part = "all") |>
  set_table_properties(layout = "autofit")

# View
table_1
```

## Table S1. 

```{r}
table_S1 <- data |> 
  tbl_summary(
    include = c(
      edad_madre, educacion, sexo, seguro_infante, wealth_3, altura_cat, DEP, 
      anemia_oms2024, ferropenia_brinda, hematological_states, AGP, PCR),
    by = etnia,
    percent = "row",
    statistic = list(
      all_continuous() ~ "{median} ({p25}, {p75})", 
      all_categorical() ~ "{n} ({p}%)"),
    digits = list(all_categorical() ~ c(0, 1)),
    missing_text = "no"
  ) |>
  add_p(
    test = list(
      all_continuous() ~ "wilcox.test",
      all_categorical() ~ "chisq.test",
      seguro_infante ~ "fisher.test"
    ),
    pvalue_fun = ~ style_pvalue(.x, digits = 3)
  ) |>
  bold_p(t = 0.05) |>
  # Simple star for Mann-Whitney U test
  modify_fmt_fun(
    p.value ~ function(x) ifelse(is.na(x), "", paste0(style_pvalue(x, digits = 3), "*")),
    rows = var_type == "continuous"
  ) |>
  # Double star for Chi-square test
  modify_fmt_fun( 
    p.value ~ function(x) ifelse(is.na(x), "", paste0(style_pvalue(x, digits = 3), "**")),
    rows = var_type %in% c("categorical", "dichotomous") & variable != "seguro_infante"
  ) |>
  # Cross for Fisher test for seguro_infante
  modify_fmt_fun(
    p.value ~ function(x) ifelse(is.na(x), "",paste0(style_pvalue(x, digits = 3), "†")),
    rows = variable == "seguro_infante"
  ) |>
  modify_header(
    label = "**Characteristics**", 
    stat_1 = "**Mestizo**  \nN = {n} ({style_percent(p, digits = 1)}%)",
    stat_2 = "**Quechua/Aymara**  \nN = {n} ({style_percent(p, digits = 1)}%)"
  ) |>
  modify_abbreviation(
    "WHO, World Health Organization; SIS, Comprehensive Health Insurance") |>
  modify_footnote(
    starts_with("p.value") ~ 
    "Mann-Whitney U test (*); Chi-square test (**); Fisher's exact test (†)"
  ) |>
  as_flex_table() |>
  theme_booktabs() |>
  fontsize(size = 9, part = "all") |>
  align(align = "center", part = "header") |>
  align(j = 1, align = "left", part = "body") |>
  align(j = 2:4, align = "center", part = "body") |>
  padding(padding.top = 0.5, padding.bottom = 0.5, part = "all") |>
  width(j = c(1:4), width = c(2, 1, 1, 0.7)) |>
  set_table_properties(layout = "fixed")

# View
table_S1
```

## Table S2. Simple regression analysis (univariable)

```{r}
# Anemia
table_S2a <- data |> 
  tbl_crude(
    x_vars = c("etnia", "wealth_3", "sexo", "educacion"), 
    outcome = "anemia")

# Iron Deficiency
table_S2b <- data |> 
  tbl_crude(
    x_vars = c("etnia", "wealth_3", "sexo", "educacion"), 
    outcome = "ferropenia")

# Non-iron-deficiency anemia
table_S2c <- data |> 
  tbl_crude(
    x_vars = c("etnia", "wealth_3", "sexo", "educacion"), 
    outcome = "anemia_no_ferropenica")

# Iron-deficiency anemia
table_S2d <- data |> 
  tbl_crude(
    x_vars = c("etnia", "wealth_3", "sexo", "educacion"),
    outcome = "anemia_ferropenica")

# Merge tables
table_S2 <- tbl_merge(
  tbls = list(table_S2a, table_S2b, table_S2c, table_S2d),
  tab_spanner = c(
    "**Anemia**", "**Iron Deficiency**", 
    "**Non-iron-deficiency anemia**", "**Iron-deficiency anemia**")) |>
  modify_header(
    label = "**Characteristics**",
    starts_with("estimate") ~ "**RPc (IC 95%)**") |>
  remove_abbreviation() |>
  modify_abbreviation(
    "PR: Crude Prevalence Ratio; 95% CI: 95% Confidence Interval") |>
  as_flex_table() |>
  theme_booktabs() |>
  fontsize(size = 9, part = "all") |>
  align(align = "center", part = "all") |>
  align(align = "left", part = "footer") |>
  align(j = 1, align = "left", part = "body") |>
  padding(padding.top = 0.5, padding.bottom = 0.5, part = "all") |>
  set_table_properties(layout = "autofit")

# View
table_S2
```

## Table 2. Multiple regression analysis (multivariable)

::: {style="text-align: justify"}
Incluir el Department como una variable predictora (efecto fijo) es la opción más robusta debido a que, dado el número reducido de unidades de nivel Higher ($K=4$ clusters), un modelo de efectos mixtos no permitiría estimar de forma fiable la varianza inter-departamental ($\tau^2$). Asimismo, los estimadores de varianza robustos (clúster-robustos) como `vcovCL`, basados en la matriz de varianza-covarianza `sandwich` asintótica, requieren generalmente entre 30 y 50 clústeres para evitar el sesgo hacia abajo de los errores estándar y la consecuente inflación del error tipo I. Incluso métodos diseñados para muestras pequeñas como `vcovCR` (ajuste tipo `CR2`), que suelen ser válidos a partir de 10 o 15 clústeres, resultan inestables con tan solo 4 unidades debido a la insuficiencia de Grados de Libertad Efectivos (EDF). Al incorporar el Department como efecto fijo, el modelo controla explícitamente la heterogeneidad geográfica de base, permitiendo comparaciones ajustadas e inferencias válidas sobre la prevalencia de anemia y ferropenia. Sin embargo, se obserrvó alta correlación entre los Departments con el indice de riqueza y la hemoglobina ajustada por la altura.
::: 

```{r}
# Anemia
table_2a <- data |>
  fit_logbinomial_safe(anemia ~ etnia + wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif()

# Iron Deficiency
table_2b <- data |>
  fit_logbinomial_safe(ferropenia ~ etnia + wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif()

# Non-iron-deficiency anemia
table_2c <- data |>
  fit_logbinomial_safe(anemia_no_ferropenica ~ etnia + wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif()

# Iron-deficiency anemia
table_2d <- data |>
 fit_logbinomial_safe(anemia_ferropenica ~ etnia + wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif()

# Merge tables
table_2 <- tbl_merge(
  tbls = list(table_2a, table_2b, table_2c, table_2d),
  tab_spanner = c(
    "**Anemia**", "**Iron Deficiency**",
    "**Non-iron-deficiency anemia**", "**Iron-deficiency anemia**")) |>
  modify_header(
    label = "**Characteristics**",
    starts_with("estimate") ~ "**RPa (IC 95%)**") |>
  remove_abbreviation() |>
  modify_abbreviation(
    "RPa: Adjusted Prevalence Ratio; 95% CI: 95% Confidence Interval. The models were adjusted for the Ethnic group, household wealth index, sex of children, and level of education.") |>
  as_flex_table() |>
  theme_booktabs() |>
  fontsize(size = 9, part = "all") |>
  align(align = "center", part = "all") |>
  align(align = "left", part = "footer") |>
  align(j = 1, align = "left", part = "body") |>
  padding(padding.top = 0.5, padding.bottom = 0.5, part = "all") |>
  set_table_properties(layout = "autofit")

# View
table_2
```

### Diagnosis of assumptions

::: {style="text-align: justify"}
Check the model assumptions for each outcome (anemia, ferropenia, anemia_no_ferropenica, and  anemia_ferropenica) only when an independent variable is numerical.
:::

```{r}
#| eval: false
# Anemia 
# Modelo 1: SIN Department 
m1 <- glm(
  anemia ~ etnia + wealth_3 + sexo + educacion,
  family = binomial(link = "log"),
  data = data
)

# Modelo 2: CON Department
m2 <- glm(
  anemia ~ etnia + wealth_3 + sexo + educacion + DEP,
  family = binomial(link = "log"),
  data = data
)

# Likelihood-Ratio-Test (LRT)
test_likelihoodratio(m1, m2)

# Model Performance Indices
model_performance(m1)
model_performance(m2)

# Comparison of Model Performance Indices
compare_performance(m1, m2, rank = TRUE, verbose = FALSE)

# Visualization of indices of models’ performance
plot(compare_performance(m1, m2, rank = TRUE, verbose = FALSE))

# Multicollinearity of model terms
check_collinearity(m2)
check_collinearity(m1)
```

## Table S3. Mestizo

```{r}
# Anemia
table_S3a <- data |>
  dplyr::filter(etnia == "Mestizo") |> 
  fit_logbinomial_safe(anemia ~ wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif() |>
  # modify_spanning_header(all_stat_cols() ~ "**Mestizo**")

# Iron Deficiency
table_S3b <- data |>
  dplyr::filter(etnia == "Mestizo") |> 
  fit_logbinomial_safe(ferropenia ~ wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif()

# Non-iron-deficiency anemia
table_S3c <- data |>
  dplyr::filter(etnia == "Mestizo") |>
  fit_logbinomial_safe(anemia_no_ferropenica ~ wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif()

# Iron-deficiency anemia
table_S3d <- data |>
  dplyr::filter(etnia == "Mestizo") |>
  fit_logbinomial_safe(anemia_ferropenica ~ wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif()

# Merge tables
table_S3 <- tbl_merge(
  tbls = list(table_S3a, table_S3b, table_S3c, table_S3d),
  tab_spanner = c(
    "**Anemia**", "**Iron Deficiency**", 
    "**Non-iron-deficiency anemia**", "**Iron-deficiency anemia**")) |>
  modify_header(
    label = "**Characteristics**",
    starts_with("estimate") ~ "**RPa (IC 95%)**") |>
  remove_abbreviation() |>
  modify_abbreviation(
    "RPa: Adjusted Prevalence Ratio; 95% CI: 95% Confidence Interval") |>
  as_flex_table() |>
  theme_booktabs() |>
  fontsize(size = 9, part = "all") |>
  align(align = "center", part = "all") |>
  align(align = "left", part = "footer") |>
  align(j = 1, align = "left", part = "body") |>
  padding(padding.top = 0.5, padding.bottom = 0.5, part = "all") |>
  set_table_properties(layout = "autofit")

# View
table_S3
```

### Diagnosis of assumptions

```{r}
#| eval: false
# Modelo 1: SIN Department
m1 <- data |>
  filter(etnia == "Mestizo") |> 
  glm(
    anemia ~ wealth_3 + sexo + educacion, 
    family = binomial(link = "log"),
    data = _
  )

# Modelo 2: CON Department
m2 <- data |>
  filter(etnia == "Mestizo") |>
  glm(
    anemia ~ wealth_3 + sexo + educacion + DEP,
    family = binomial(link = "log"),
    data = _
  )

# Likelihood-Ratio-Test (LRT)
test_likelihoodratio(m1, m2)

# Model Performance Indices
model_performance(m1)
model_performance(m2)

# Comparison of Model Performance Indices
compare_performance(m1, m2, rank = TRUE, verbose = FALSE)

# Visualization of indices of models’ performance
plot(compare_performance(m1, m2, rank = TRUE, verbose = FALSE))

# Multicollinearity of model terms
check_collinearity(m2)
check_collinearity(m1)
```

## Table S4. Quechua/Aymara	

```{r}
# Anemia
table_S4a <- data |>
  dplyr::filter(etnia == "Quechua/Aymara") |> 
  fit_logbinomial_safe(anemia ~ wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif()

# Iron Deficiency
table_S4b <- data |>
  dplyr::filter(etnia == "Quechua/Aymara") |> 
  fit_logbinomial_safe(ferropenia ~ wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif()

# Non-iron-deficiency anemia
table_S4c <- data |>
  dplyr::filter(etnia == "Quechua/Aymara") |> 
  fit_logbinomial_safe(anemia_no_ferropenica ~ wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif()

# Iron-deficiency anemia
table_S4d <- data |>
  dplyr::filter(etnia == "Quechua/Aymara") |> 
  fit_logbinomial_safe(anemia_ferropenica ~ wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif()

# Merge tables
table_S4 <- tbl_merge(
  tbls = list(table_S4a, table_S4b, table_S4c, table_S4d),
  tab_spanner = c(
    "**Anemia**", "**Iron Deficiency**", "**Non-iron-deficiency anemia**", "**Iron-deficiency anemia**")) |>
  modify_header(
    label = "**Characteristics**",
    starts_with("estimate") ~ "**RPa (IC 95%)**") |>
  remove_abbreviation() |>
  modify_abbreviation(
    "RPa: Adjusted Prevalence Ratio; 95% CI: 95% Confidence Interval") |>
  as_flex_table() |>
  theme_booktabs() |>
  fontsize(size = 9, part = "all") |>
  align(align = "center", part = "all") |>
  align(align = "left", part = "footer") |>
  align(j = 1, align = "left", part = "body") |>
  padding(padding.top = 0.5, padding.bottom = 0.5, part = "all") |>
  set_table_properties(layout = "autofit")

# View
table_S4
```

### Diagnosis of assumptions

```{r}
#| eval: false
# Modelo 1: SIN Department
m1 <- data |>
  filter(etnia == "Quechua/Aymara") |> 
  glm(
    anemia ~ wealth_3 + sexo + educacion, 
    family = binomial(link = "log"),
    data = _
  )

# Modelo 2: CON Department
m2 <- data |>
  filter(etnia == "Quechua/Aymara") |> 
  glm(
    anemia ~ wealth_3 + sexo + educacion + DEP,
    family = binomial(link = "log"),
    data = _
  )

# Likelihood-Ratio-Test (LRT)
test_likelihoodratio(m1, m2)

# Model Performance Indices
model_performance(m1)
model_performance(m2)

# Comparison of Model Performance Indices
compare_performance(m1, m2, rank = TRUE, verbose = FALSE)

# Visualization of indices of models’ performance
plot(compare_performance(m1, m2, rank = TRUE, verbose = FALSE))

# Multicollinearity of model terms
check_collinearity(m1)
check_collinearity(m2)
```

## Table for figure 1

```{r}
# Merge columns, essential for the triple header
theme_gtsummary_journal(journal = "jama")

# Anemia
table_a <- tbl_merge(tbls = list(table_S3a, table_S4a)) |> remove_abbreviation()
# Ferropenia
table_b <- tbl_merge(tbls = list(table_S3b, table_S4b)) |> remove_abbreviation()
# Non-iron-deficiency anemia
table_c <- tbl_merge(tbls = list(table_S3c, table_S4c)) |> remove_abbreviation()
# Iron-deficiency anemia
table_d <- tbl_merge(tbls = list(table_S3d, table_S4d)) |> remove_abbreviation()

# Stack tables
table_F1 <- tbl_merge(tbls = list(table_a, table_b, table_c, table_d))

# Triple header
table_F1 <- table_F1 |>
  as_flex_table() |>
  delete_part(part = "header") |>
  
  # Level 1: Estimates and 95% CI
  add_header_row(
    values = c("Determinantes Sociales", rep(c("RPa (IC 95%)", "Valor p"), 8))
  ) |>
  
  # Level 2: Ethnic group (Mestizo y Quechua/Aymara)
  add_header_row(values = c("", rep(
    c("Mestizo", "Mestizo", "Quechua/Aymara", "Quechua/Aymara"), 4))
  ) |> 
  
  # Level 3: Hematological status
  add_header_row(
    values = c(
      "",
      rep("Anemia", 4),
      rep("Iron Deficiency", 4),
      rep("Non-iron-deficiency anemia", 4),
      rep("Iron-deficiency anemia", 4)
    )
  ) |>
  
  add_footer_row(
    values = "RPa: Adjusted Prevalence Ratio; 95% CI: 95% Confidence Interval",
    colwidths = 17) |>
  
  # Fusionar horizontalmente (donde hay textos repetidos como "Anemia" o "Mestizo")
  merge_h(part = "header") |>
  # Fusionar verticalmente (para que "Determinantes Sociales" ocupe las 3 filas)
  merge_v(part = "header") |>
  
  # Theme
  theme_booktabs() |>
  align(align = "center", part = "all") |>
  align(align = "left", part = "footer") |>
  align(j = 1, align = "left", part = "body") |>
  fontsize(size = 9, part = "all") |>
  padding(padding.top = 0.5, padding.bottom = 0.5, part = "all") |>
  set_table_properties(layout = "autofit")

# View
table_F1
``` 

## Figure 1

```{r}
#| fig-height: 8
#| fig-width: 8
# Combine all results
plot_data <- bind_rows(
  extract_forest_data(table_S3a, "Anemia", "Mestizo"),
  extract_forest_data(table_S3b, "Iron Deficiency", "Mestizo"),
  extract_forest_data(table_S3c, "Non-iron-deficiency anemia", "Mestizo"),
  extract_forest_data(table_S3d, "Iron-deficiency anemia", "Mestizo"),
  extract_forest_data(table_S4a, "Anemia", "Quechua/Aymara"),
  extract_forest_data(table_S4b, "Iron Deficiency", "Quechua/Aymara"),
  extract_forest_data(table_S4c, "Non-iron-deficiency anemia", "Quechua/Aymara"),
  extract_forest_data(table_S4d, "Iron-deficiency anemia", "Quechua/Aymara")
)

# Order of independent variables (Without references)
orden_labels <- c(
  "**Wealth index**", # Wealth index (ref. Poor)
  "  Middle", "  Rich",
  "**Sexo del Infante**", # Sexo (ref. Masculino)
  "  Female",
  "**Level of education**", # Nivel educativo (ref. None or primary)
  "  Secondary", "  Higher"
  # "**Department**", # Department (ref. Arequipa)
  # "  Lima", "  Cusco", "  Puno"
)

# Ordered data
plot_data_ordered <- plot_data |>
  mutate(label = paste0("  ", label)) |>
  bind_rows(expand_grid(
    label = c(
      "**Wealth index**",
      "**Sex of children**",
      "**Level of education**"
      # "**Department**"
    ),
    Outcome = unique(plot_data$Outcome),
    Etnia = unique(plot_data$Etnia)
  )) |>
  # Formatear outcomes (Panel A, B, C, D)
  mutate(
    Outcome = case_match(
      Outcome,
      "Anemia" ~ "A. Anemia",
      "Iron Deficiency" ~ "B. Iron-deficiency",
      "Non-iron-deficiency anemia" ~ "C. Non-iron-deficiency anemia",
      "Iron-deficiency anemia" ~ "D. Iron-deficiency anemia"
    ),
    Outcome = factor(
      Outcome,
      levels = c(
        "A. Anemia",
        "B. Iron-deficiency",
        "C. Non-iron-deficiency anemia",
        "D. Iron-deficiency anemia"
      )
    ),
    label = factor(label, levels = orden_labels)
  )

# Plot
F1 <- ggplot(plot_data_ordered, aes(x = estimate, y = fct_rev(label), color = Etnia)) +
  # No effect line (RP = 1)
  geom_vline(xintercept = 1, linetype = "solid", color = "grey40", linewidth = 1) +
  # Points and confidence intervals
  geom_pointrange(
    aes(xmin = conf.low, xmax = conf.high), 
    position = position_dodge(width = 0.6), size = 0.6, fatten = 4) +
  # Panels by outcome
  facet_wrap(~ Outcome, scales = "free_x", ncol = 2) +
  # Log scale
  scale_x_log10(breaks = c(0.25, 0.5, 1, 2, 4), limits = c(0.1, 10)) +
  # Colors
  scale_color_manual(values = c("Mestizo" = "dodgerblue", "Quechua/Aymara" = "red2")) +
  # Labels
  labs(
    x = "adjusted Prevalence Ratio with 95% CI",
    color = "Ethnic group"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "bottom",
    legend.title = element_text(size = 12, face = "bold"),
    legend.margin = margin(t = -5, unit = "pt"),
    axis.title.y = element_blank(),
    axis.title.x = element_text(colour = "black", margin = margin(t = 20, unit = "pt")),
    axis.text.y = element_markdown(size = 10, colour = "black"), 
    axis.text.x = element_text(colour = "black"),
    strip.text = element_text(face = "bold", size = 12, hjust = 0),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.major.x = element_line(linetype = 2, color = "grey70", linewidth = 1),
    panel.spacing = unit(1, "lines"),
    axis.line = element_line(colour = "black", linewidth = 1),
    axis.ticks = element_line(colour = "black", linewidth = 1)
  )

# View
F1
```

## Figure 2. Marginal effects for education level

```{r}
#| fig-height: 8
#| fig-width: 10
pA_edu <- plot_margins_logbin(
  df = data,
  outcome = "anemia",
  letter = "A",
  x_var = "educacion",
  covars = c("sexo", "wealth_3")
)

pB_edu <- plot_margins_logbin(
  df = data,
  outcome = "ferropenia",
  letter = "B",
  x_var = "educacion",
  covars = c("sexo", "wealth_3")
)

pC_edu <- plot_margins_logbin(
  df = data,
  outcome = "anemia_no_ferropenica",
  letter = "C",
  x_var = "educacion",
  covars = c("sexo", "wealth_3")
)

pD_edu <- plot_margins_logbin(
  df = data,
  outcome = "anemia_ferropenica",
  letter = "D",
  x_var = "educacion",
  covars = c("sexo", "wealth_3")
)

# Merge plots
Fig_Edu_ABCD <- ggarrange(
  pA_edu, pB_edu, pC_edu, pD_edu, 
  ncol = 2, nrow = 2, 
  common.legend = TRUE, 
  legend = "top")

# Common axes
Fig_Edu_ABCD <- annotate_figure(
  Fig_Edu_ABCD,
  left = text_grob(
    "Predicted prevalence of outcome", rot = 90, face = "bold", size = 14),
  bottom = text_grob("Level of education", face = "bold", size = 14) 
)

# View
Fig_Edu_ABCD
```

## Figure 3. Marginal effects for wealth index

```{r}
#| fig-height: 8
#| fig-width: 10
pA_w <- plot_margins_logbin(
  df = data,
  outcome = "anemia",
  letter = "A",
  x_var = "wealth_3",
  covars = c("sexo", "educacion")
)

pB_w <- plot_margins_logbin(
  df = data,
  outcome = "ferropenia",
  letter = "B",
  x_var = "wealth_3",
  covars = c("sexo", "educacion")
)

pC_w <- plot_margins_logbin(
  df = data,
  outcome = "anemia_no_ferropenica",
  letter = "C",
  x_var = "wealth_3",
  covars = c("sexo", "educacion")
)

pD_w <- plot_margins_logbin(
  df = data,
  outcome = "anemia_ferropenica",
  letter = "D",
  x_var = "wealth_3",
  covars = c("sexo", "educacion")
)

# Merge plots
Fig_Wealth_ABCD <- ggarrange(
  pA_w, pB_w, pC_w, pD_w, 
  ncol = 2, nrow = 2, 
  common.legend = TRUE, 
  legend = "top"
)

# Common axes
Fig_Wealth_ABCD <- annotate_figure(
  Fig_Wealth_ABCD,
  left = text_grob(
    "Predicted prevalence of outcome", rot = 90, face = "bold", size = 14),
  bottom = text_grob("Wealth index", face = "bold", size = 14) 
)

# View
Fig_Wealth_ABCD
```

## Linear Model (Naive model)

```{r}
#| eval: false
#| fig-height: 4
#| fig-width: 8
# Model
mod_anemia <- glm(
  anemia ~ etnia * educacion + sexo + wealth_3 + DEP, 
  data = data, family = binomial(link = "log"))

# Model summary
summary(mod_anemia)
tidy(mod_anemia, exponentiate = TRUE, conf.int = TRUE)

# Predicted values
fitted_glm_1 <- predict_response(
  mod_anemia, terms = c("wealth_3", "Ethnic group"), margin = "empirical")

fitted_glm_2 <- predict_response(
  mod_anemia, terms = c("educacion", "Ethnic group"), margin = "empirical")

# Plot
a1_mod_anemia <- plot(fitted_glm_1)
a2_mod_anemia <- plot(fitted_glm_2)

# View
ggarrange(
  a1_mod_anemia, a2_mod_anemia, ncol = 2, nrow = 1, 
  common.legend = TRUE, legend = "bottom")
```

## Restricted cubic spline (natural spline).

```{r}
#| eval: false
#| fig-height: 8
#| fig-width: 8
# Model
rcs_anemia <- glm(
  anemia ~ rcs(ferr_adj, 3) + wealth_3 + sexo + etnia + educacion + DEP, 
  data = data, family = binomial(link = "logit"))

# Model summary
summary(rcs_anemia)
tidy(rcs_anemia, exponentiate = TRUE, conf.int = TRUE)

# Predicted values
fitted_rcs_1 <- predict_response(
  rcs_anemia, terms = c("ferr_adj", "wealth_3", "Ethnic group"))

fitted_rcs_2 <- predict_response(
  rcs_anemia, terms = c("ferr_adj", "educacion", "Ethnic group"))

# Plot
a1_rcs_anemia <- plot(fitted_rcs_1)
a2_rcs_anemia <- plot(fitted_rcs_2)

# View
ggarrange(
  a1_rcs_anemia, a2_rcs_anemia, ncol = 1, nrow = 2, 
  common.legend = FALSE, legend = "right")
```

## GAM (Cubic regression splines and REML)

```{r}
#| eval: false
#| fig-height: 8
#| fig-width: 8
# Model
gam_anemia <- gam(
  anemia ~ 
    s(ferr_adj, k = -1, bs = "cr") + etnia + wealth_3 + sexo + educacion + DEP, 
  data = data, family = binomial(link = "logit"), method = "REML", select = TRUE)

# Model summary
summary(gam_anemia)
tidy(gam_anemia, exponentiate = TRUE, conf.int = TRUE)

# Predicted values
fitted_gam_1 <- predict_response(
  gam_anemia, terms = c("ferr_adj", "wealth_3", "Ethnic group"))

fitted_gam_2 <- predict_response(
  gam_anemia, terms = c("ferr_adj", "educacion", "Ethnic group"))

# Plot
a1_gam_anemia <- plot(fitted_gam_1)
a2_gam_anemia <- plot(fitted_gam_2)

# View
ggarrange(
  a1_gam_anemia, a2_gam_anemia, ncol = 1, nrow = 2, 
  common.legend = FALSE, legend = "right")
```

## Venn diagram

```{r}
#| fig-height: 5
#| fig-width: 7
lista_venn <- list(
  Ferropenia = which(data$ferropenia == 1),
  Anemia = which(data$anemia == 1)
)

test_1 <- ggVennDiagram(
  lista_venn,
  category.names = c("A. Ferropenia", "B. Anemia"),
  set_color = "black",
  label_color = "black",
  label = "both",
  label_alpha = 0,
  edge_size = 1
) +
  coord_flip() +
  scale_fill_gradient(low = "#1E90FF66", high = "#EE000066") +
  theme(
    legend.position = "none",
    panel.background = element_blank()
  )

# View
test_1
```

```{r}
summary_hematological_states <- data |>
  # Usamos la columna que creamos antes
  count(hematological_states) |>
  mutate(
    porcentaje = (n / sum(n)) * 100,
    label = paste0(round(porcentaje, 1), "%")
  ) |>
  # Ordenamos para que la gráfica sea legible
  arrange(desc(porcentaje))
```

## Euler diagram

```{r}
#| fig-height: 5
#| fig-width: 7

# Calculate the totals and the intersection
n_ferropenia <- sum(data$ferropenia == 1 & data$anemia == 0, na.rm = TRUE)
n_anemia <- sum(data$anemia == 1 & data$ferropenia == 0, na.rm = TRUE)
n_ambos <- sum(data$anemia == 1 & data$ferropenia == 1, na.rm = TRUE)
n_total <- nrow(data)

# Adjust the model
fit <- euler(c(
  "Ferropenia" = n_ferropenia,
  "Anemia" = n_anemia,
  "Ferropenia&Anemia" = n_ambos
))

# Prepare the numeric texts
txt_f <- paste0("'", n_ferropenia, " (", round(n_ferropenia / n_total * 100, 1), "%)'")
txt_a <- paste0("'", n_anemia, " (", round(n_anemia / n_total * 100, 1), "%)'")
txt_ambos <- paste0("'", n_ambos, " (", round(n_ambos / n_total * 100, 1), "%)'")

# Use parse() and atop() to create expressions: Up (bold) and Down (normal)
labs_internas <- parse(text = c(
  paste0("atop(bold('Ferropenia'), ", txt_f, ")"),
  paste0("atop(bold('Anemia no ferropénica'), ", txt_a, ")"),
  paste0("atop(bold('Anemia ferropénica'), ", txt_ambos, ")")
))

# Plot
euler_plot <- plot(fit,
  # Turn off the top labels of the circles
  labels = FALSE,
  
  # Legend
  legend = list(
    col = "black",
    fontsize = 12,
    fontface = "bold",
    side = "bottom",
    nrow = 1,
    ncol = 2
  ),
  # Internal labels 
  quantities = list(
    labels = labs_internas,
    fontsize = 10,
    fontface = "plain"
  ),
  
  # Theme
  fill = c("skyblue", "tomato"), 
  alpha = 0.5,
  edges = list(col = "black", lwd = 2)
)

# View
euler_plot
```

# Save outputs

## Section properties

```{r}
# Definir las propiedades de la sección (Horizontal)
sect_properties_h <- prop_section(
  page_size = page_size(orient = "landscape"),
  page_margins = page_mar(bottom = 0.5, top = 0.5, right = 0.5, left = 0.5),
  type = "continuous"
)

# Definir las propiedades de la sección (Vertical)
sect_properties_v <- prop_section(
  page_size = page_size(orient = "portrait"),
  page_margins = page_mar(bottom = 0.5, top = 0.5, right = 0.5, left = 0.5),
  type = "continuous"
)
```

## Tables

```{r}
# Tables
save_as_docx(
  table_1,
  align = "center",
  path = here("outputs", "Table_1_by disease.docx"),
  pr_section = sect_properties_v)

save_as_docx(
  table_2,
  align = "center",
  path = here("outputs", "Table_2_multivariable.docx"),
  pr_section = sect_properties_h)

# Supplementary tables
save_as_docx(
  table_S1,
  align = "center",
  path = here("outputs", "Table_S1_by ethnicity.docx"),
  pr_section = sect_properties_v)

save_as_docx(
  table_S2,
  align = "center",
  path = here("outputs", "Table_S2_univariable.docx"),
  pr_section = sect_properties_h)

save_as_docx(
  table_S3,
  align = "center",
  path = here("outputs", "Table_S3_mestizo.docx"),
  pr_section = sect_properties_h)

save_as_docx(
  table_S4,
  align = "center",
  path = here("outputs", "Table_S4_quechua.docx"),
  pr_section = sect_properties_h)

save_as_docx(
  table_S5,
  align = "center",
  path = here("outputs", "Table_S5_reliability.docx"),
  pr_section = sect_properties_v)

save_as_docx(
  table_S6,
  align = "center",
  path = here("outputs", "Table_S6_item statistics.docx"),
  pr_section = sect_properties_v)

save_as_docx(
  table_S7,
  align = "center",
  path = here("outputs", "Table_S7_loadings.docx"),
  pr_section = sect_properties_v)

save_as_docx(
  table_F1,
  align = "center",
  path = here("outputs", "Table for figure 1.docx"),
  pr_section = sect_properties_h)
```

## Figures

```{r}
# Figure 1
ggsave(
  here::here("outputs", "Figure_1.png"),
  F1,
  width = 8,
  height = 8,
  dpi = 600
)

ggsave(
  here::here("outputs", "Figure_1.jpeg"),
  F1,
  width = 8,
  height = 8,
  dpi = 600
)

# Figure 2
ggsave(
  here::here("outputs", "Figure_2_Education.png"),
  Fig_Edu_ABCD,
  width = 10,
  height = 8,
  dpi = 600
)

# Figure 3
ggsave(
  here::here("outputs", "Figure_3_Wealth.png"),
  Fig_Wealth_ABCD,
  width = 12,
  height = 8,
  dpi = 600
)

# Supplementary figure 1
ggsave(
  here::here("outputs", "Figure_S1_loading plot.png"),
  FS1,
  height = 8,
  dpi = 600
)

# Supplementary figure 2
ggsave(
  here::here("outputs", "Figure_S2_quantification plot.png"),
  FS2,
  width = 8,
  height = 6,
  dpi = 600
)

# Venn
ggsave(
  here::here("outputs", "Venn_plot.jpeg"),
  test_1,
  width = 7,
  height = 5,
  dpi = 600
)

# Euler
ggsave(
  here::here("outputs", "Euler_plot.png"),
  euler_plot,
  width = 7,
  height = 5,
  dpi = 600
)
```

