---
title: "Ferritina"
author: "Carlos Ballon-Salcedo"
date: "`r Sys.Date()`"
format:
  html:
    theme: 
     light: lux
     dark: darkly
    toc: true
    toc-depth: 3
    code-overflow: wrap
    lightbox: true
    highlight-style: github
    number-sections: true
    code-fold: true
    code-tools: 
      source: "https://github.com/Carlos-Ballon/ferritin-anemia_diagnosis.git"
    embed-resources: true
editor: source
execute:
  message: false
  warning: false
bibliography: grateful-refs.bib
csl: vancouver.csl
lang: en
---

# Load packages

```{r}
# Packages
pacman::p_load(
  tidyverse,
  rio,
  here,
  Hmisc,
  psych,
  factoextra,
  ggpubr,
  broom,
  ggeffects,
  grateful,
  flextable,
  janitor,
  performance,
  gtsummary,
  finalfit,
  rms,
  mgcv,
  officer,
  Gifi,
  eulerr,
  ggsci,
  coin,
  FSA,
  rcompanion,
  ggtext)
```

```{r}
#| eval: false
# Citations
grateful::cite_packages(
  output = "file",
  out.format = "docx",
  out.dir = ".",
  citation.style = "vancouver")
```

```{r}
# Set gtsummary theme
theme_gtsummary_journal(journal = "jama")

# Set gtsummary language
theme_gtsummary_language(language = "en")
```

# Import data

```{r}
#| eval: true
#| echo: true
#| results: false
# Data
data <- import(here("data", "base_de_curvas.dta")) |>
  tibble::rownames_to_column(var = "ID1")

# Scripts
# rfextras::load_scripts()
source(here("scripts", "wealth index_catpca.R"))
source(here("scripts", "models.R"))
source(here("scripts", "marginal effects.R"))
```

# Process data

```{r}
# Select categorical variables (to factor)
vars <- c(
  "P001", "P002", "P004", "P005", "P006", "P007", "P008", "P009", "P010", "P011",
  "P012", "P013", "P014", "P015", "P018", "P019", "P020", "P021", "P022", "P023",
  "P024", "P025", "P028", "P029")

data <- data |>
  dplyr::filter(P015 %in% c(1, 2, 6)) |>
  mutate(
    across(all_of(vars), ~ replace(.x, .x >= 99, NA)),
    
    anemia = if_else(P037 < 10.5, 1L, 0L, missing = NA_integer_),
    
    ferropenia = if_else(ferr_adj < 12, 1L, 0L, missing = NA_integer_),
    
    anemia_no_ferropenica = if_else(
      anemia == 1L & ferropenia == 0L, 1L, 0L, missing = NA_integer_),
    
    anemia_ferropenica = if_else(
      anemia == 1L & ferropenia == 1L, 1L, 0L, missing = NA_integer_),
    
    hematological_states = case_when(
      anemia == 1 & ferropenia == 1 ~ "Iron-deficiency anemia", 
      anemia == 1 & ferropenia == 0 ~ "Non-iron-deficiency anemia", 
      anemia == 0 & ferropenia == 1 ~ "Iron Deficiency",
      anemia == 0 & ferropenia == 0 ~ "No deficiencies", 
      TRUE ~ "Another"
    ) |> 
      fct_relevel(
        "No deficiencies", "Iron Deficiency", 
        "Non-iron-deficiency anemia", "Iron-deficiency anemia") |>
      ff_label("Hematological status"),
    
    sexo = factor(P001) |> 
      fct_recode("Male" = "1", "Female" = "2") |> 
      fct_relevel("Male", "Female") |> 
      ff_label("Sex of children"),
    
    etnia = case_match(as.character(P015),
      c("1", "2") ~ "Quechua/Aymara",
      "6" ~ "Mestizo",
      .default = NA_character_
    ) |> 
      fct_relevel("Mestizo", "Quechua/Aymara") |> 
      ff_label("Ethnic group"),
    
    seguro_infante = case_match(as.character(P002),
      c("1", "2", "3") ~ "Publics (SIS, EsSalud, FFAA)",
      c("4", "5") ~ "Private",
      c("6", "7", "99") ~ "None or no answer",
      .default = NA_character_
    ) |>
      fct_relevel("Publics (SIS, EsSalud, FFAA)", "Private", "None or no answer") |>
      ff_label("Child Health Insurance"), 
    
    educacion = case_match(as.character(P007), 
      c("0", "1", "2") ~ "None or primary", 
      "3" ~ "Secondary", 
      c("4", "5") ~ "Higher",
      .default = NA_character_) |>
      fct_relevel("None or primary", "Secondary", "Higher") |>
      ff_label("Level of education"),
    
    DEP = factor(DEP) |>
      fct_relevel("Arequipa", "Lima", "Cusco", "Puno") |>
      ff_label("Department"),
    
    altura_cat = case_when(
      P017 < 1500  ~ "< 1500",
      P017 >= 1500 & P017 < 3000 ~ "1500 - 2999",
      P017 >= 3000 & P017 < 3500 ~ "3000 - 3499",
      P017 >= 3500 ~ ">= 3500",
      TRUE ~ NA_character_
    ) |>
      fct_relevel("< 1500", "1500 - 2999", "3000 - 3499", ">= 3500") |>
      ff_label("Elevation (m a.s.l.)"), 
    
    anemia_oms2024 = if_else(anemia == 1, "Si", "No") |> 
      fct_relevel("No", "Si") |> 
      ff_label("Anemia (WHO 2024, adjusted)"),
    
    ferropenia_brinda = if_else(ferropenia == 1, "Si", "No") |>
      fct_relevel("No", "Si") |>
      ff_label("Iron Deficiency (BRINDA Method)"),
    
    vitamina_A = if_else(
      P033 < 0.70, "Deficiencia de Vitamina A", "Suficiente") |>
      fct_relevel("Suficiente", "Deficiencia de Vitamina A") |>
      ff_label("Deficiencia de Vitamina A"),
    
    suplemento = case_match(as.character(P029), 
      "1" ~ "Si", 
      "2" ~ "No", 
      .default = NA_character_) |>
      fct_relevel("No", "Si") |>
      ff_label("Suplementación con de hierro"),
    
    across(all_of(setdiff(vars, c("P015", "P007", "P002", "P001", "P029"))), as_factor),
    
    edad_madre = ff_label(P003, "Mother's age"),
    
    wealth_5 = ff_label(wealth_5, "Wealth index"),
    
    wealth_3 = ff_label(wealth_3, "Wealth index"),
    
    sTfR_cat = ff_label(P032, "Soluble transferrin receptor"),
   
    AGP = ff_label(P034, "Alpha-1-acid glycoprotein (g/L)"),
    
    PCR = ff_label(P035, "C-reactive protein (g/L) (mg/L)"),
    
    reserva_hierro = ff_label(P036, "Estado del hierro corporal total")
  ) |>
  dplyr::select(ID1, DEP, P037:PCR)
```

# Dictionary

```{r}
#| eval: false
# Generate a dictionary
labelled::generate_dictionary(data)

# Inspect variable labels and data.frame structure
Hmisc::contents(data)   # data.frame with the variable types and missing values
dplyr::glimpse(data)    # compact structure
str(data)               # detailed structure

# Inspect labels of specific variables
attributes(data$P001)
haven::var_labels(data$P001)
```

# Produce outputs

## Table 1

Characteristics of study participants according to maternal ethnic group among Peruvian infants.

```{r}
table_1 <- data |>
  mutate(
    educacion = factor(educacion, ordered = TRUE), 
    wealth_3 = factor(wealth_3, ordered = TRUE)) |>
  tbl_summary(
    include = c(
      edad_madre, educacion, sexo, seguro_infante, wealth_3, altura_cat, DEP, 
      anemia_oms2024, ferropenia_brinda, hematological_states, AGP, PCR),
    by = etnia,
    percent = "row",
    statistic = list(
      all_continuous() ~ "{median} ({p25}, {p75})", 
      all_categorical() ~ "{n} ({p}%)"),
    digits = list(all_categorical() ~ c(0, 1)),
    missing_text = "no"
  ) |>
  add_p(
    test = list(
      all_continuous() ~ "wilcox.test",
      all_categorical() ~ "chisq.test",
      wealth_3 ~ test_tendencia_ordinal,
      educacion ~ test_tendencia_ordinal,
      seguro_infante ~ "fisher.test"
    ),
    pvalue_fun = ~ style_pvalue(.x, digits = 3)
  ) |>
  bold_p(t = 0.05) |>
  # Simple star for Mann-Whitney U test
  modify_fmt_fun(
    p.value ~ function(x) ifelse(is.na(x), "", paste0(style_pvalue(x, digits = 3), "*")),
    rows = var_type == "continuous"
  ) |>
  # Double star for Chi-square test
  modify_fmt_fun( 
    p.value ~ function(x) ifelse(is.na(x), "", paste0(style_pvalue(x, digits = 3), "**")),
    rows = var_type %in% c("categorical", "dichotomous") & variable != "seguro_infante"
  ) |>
  # Cross for Fisher test for seguro_infante
  modify_fmt_fun(
    p.value ~ function(x) ifelse(is.na(x), "",paste0(style_pvalue(x, digits = 3), "†")),
    rows = variable == "seguro_infante"
  ) |>
  # Double cross for Cochran-Armitage test (Cochran-Mantel-Haenszel)
  modify_fmt_fun(
    p.value ~ function(x) ifelse(is.na(x), "",paste0(style_pvalue(x, digits = 3), "††")),
    rows = variable %in% c("wealth_3", "educacion")
  ) |>
  modify_header(
    label = "**Characteristics**", 
    stat_1 = "**Mestizo**  \nN = {n} ({style_percent(p, digits = 1)}%)",
    stat_2 = "**Quechua/Aymara**  \nN = {n} ({style_percent(p, digits = 1)}%)"
  ) |>
  modify_caption(caption = "Table 1. Characteristics of study participants according to maternal ethnic group among Peruvian infants") |>
  modify_abbreviation(
    "SIS, Seguro Integral de Salud; EsSalud, Seguro Social de Salud; FF. AA., Fuerzas Armadas") |>
  modify_footnote(
    starts_with("p.value") ~ 
    "(*) Mann-Whitney test; (**) Chi-square test (**); (†) Fisher's exact test; (††) Cochran-Mantel-Haenszel test"
  ) |>
  as_flex_table() |>
  theme_booktabs() |>
  fontsize(size = 9, part = "all") |>
  align(align = "center", part = "header") |>
  align(j = 1, align = "left", part = "body") |>
  align(j = 2:4, align = "center", part = "body") |>
  padding(padding.top = 0.5, padding.bottom = 0.5, part = "all") |>
  width(j = c(1:4), width = c(2, 1, 1, 0.7)) |>
  set_table_properties(layout = "fixed")

# View
table_1
```

## Table 2 

Characteristics of study participants according to hematological status among Peruvian infants.

```{r}
table_2 <- data |> 
  mutate(
    educacion = factor(educacion, ordered = TRUE), 
    wealth_3 = factor(wealth_3, ordered = TRUE)) |>
  tbl_summary(
    include = c(edad_madre, sexo, wealth_3, educacion, DEP, etnia, AGP, PCR),
    by = hematological_states,
    percent = "column",
    statistic = list(
      all_continuous() ~ "{median} ({p25}, {p75})", 
      all_categorical() ~ "{n} ({p}%)"),
    digits = list(
      all_categorical() ~ c(0, 1)),
    missing_text = "no"
  ) |>
  add_overall() |>
  add_p(
    test = list(
      all_continuous() ~ "kruskal.test",
      all_categorical() ~ "chisq.test",
      wealth_3 ~ test_tendencia_ordinal,
      educacion ~ test_tendencia_ordinal
    )
  ) |>
  bold_p(t = 0.05) |>
  # Simple star for Kruskal-Wallis rank sum test
  modify_fmt_fun(
    p.value ~ function(x) ifelse(is.na(x), "",paste0(style_pvalue(x, digits = 3), "*")),
    rows = var_type == "continuous"
  ) |>
  # Double star for Chi-square test
  modify_fmt_fun( 
    p.value ~ function(x) ifelse(is.na(x), "",paste0(style_pvalue(x, digits = 3), "**")),
    rows = var_type %in% c("categorical", "dichotomous") & 
      !(variable %in% c("wealth_3", "educacion"))
  ) |>
  # Cross for Cochran-Mantel-Haenszel test
  modify_fmt_fun(
    p.value ~ function(x) ifelse(is.na(x), "",paste0(style_pvalue(x, digits = 3), "†")),
    rows = variable %in% c("wealth_3", "educacion")
  ) |>
  modify_header(
    label = "**Characteristics**",
    stat_0 = "**Total** \nN = {n}",
    stat_1 = "**No deficiencies**  \nN = {n} ({style_percent(p, digits = 1)}%)",
    stat_2 = "**Iron Deficiency**  \nN = {n} ({style_percent(p, digits = 0)}%)",
    stat_3 = "**Non-iron-deficiency anemia**  \nN = {n} ({style_percent(p, digits = 1)}%)",
    stat_4 = "**Iron-deficiency anemia**  \nN = {n} ({style_percent(p, digits = 1)}%)") |>
  modify_caption(caption = "Table 2. Characteristics of study participants according to hematological status among Peruvian infants") |>
  modify_footnote(
    starts_with("p.value") ~ 
    "(*) Kruskal-Wallis test; (**) Chi-square test; (†) Cochran-Mantel-Haenszel test"
  ) |>
  modify_abbreviation(
    "RPa: Adjusted Prevalence Ratio; 95% CI: 95% Confidence Interval") |>
  as_flex_table() |>
  theme_booktabs() |>
  fontsize(size = 9, part = "all") |>
  align(align = "center", part = "all") |>
  align(align = "left", part = "footer") |>
  align(j = 1, align = "left", part = "body") |>
  padding(padding.top = 0.5, padding.bottom = 0.5, part = "all") |>
  set_table_properties(layout = "autofit")

# View
table_2
```

### Post Hoc tests

```{r}
#| eval: false
# Chi-Squared Test
chisq.test(data$etnia, data$educacion)
chisq_test(table(data$educacion, data$etnia))

# Pairwise tests of independence for nominal data (Chi-squared)
tabla_test <- table(data$hematological_states, data$etnia)
pairwiseNominalIndependence(
  x = tabla_test,
  method = "holm",
  gtest = FALSE,
  fisher = FALSE,
  chisq = TRUE
)

# Pairwise tests of independence for nominal data (Fisher)
tabla_test <- table(data$seguro_infante, data$etnia)
pairwiseNominalIndependence(
  x = tabla_test,
  method = "holm",
  gtest = FALSE,
  fisher = TRUE,
  chisq = FALSE
)

# Cochran-Mantel-Haenszel Test
cmh_test(hematological_states ~ factor(educacion, ordered = TRUE), data = data)
cmh_test(etnia ~ factor(educacion, ordered = TRUE), data = data)

# Kruskal-Wallis Rank Sum Test
kruskal.test(data$educacion, data$hematological_states)

# Dunn's Kruskal-Wallis Multiple Comparisons
dunnTest(
  PCR ~ hematological_states,
  data = data,
  method = "holm" # Método de ajuste
)
```

## Table S4. Simple regression analysis (univariable)

Crude associations between sociodemographic factors and hematological outcomes among Peruvian infants.

```{r}
# Anemia
table_S4a <- data |> 
  tbl_crude(
    x_vars = c("etnia", "wealth_3", "sexo", "educacion"), 
    outcome = "anemia")

# Iron Deficiency
table_S4b <- data |> 
  tbl_crude(
    x_vars = c("etnia", "wealth_3", "sexo", "educacion"), 
    outcome = "ferropenia")

# Non-iron-deficiency anemia
table_S4c <- data |> 
  tbl_crude(
    x_vars = c("etnia", "wealth_3", "sexo", "educacion"), 
    outcome = "anemia_no_ferropenica")

# Iron-deficiency anemia
table_S4d <- data |> 
  tbl_crude(
    x_vars = c("etnia", "wealth_3", "sexo", "educacion"),
    outcome = "anemia_ferropenica")

# Merge tables
table_S4 <- tbl_merge(
  tbls = list(table_S4a, table_S4b, table_S4c, table_S4d),
  tab_spanner = c(
    "**Anemia**", "**Iron Deficiency**", 
    "**Non-iron-deficiency anemia**", "**Iron-deficiency anemia**")) |>
  modify_header(
    label = "**Characteristics**",
    starts_with("estimate") ~ "**RPc (IC 95%)**") |>
  modify_caption(caption = "Supplementary Table S4. Crude associations between sociodemographic factors and hematological outcomes among Peruvian infants") |>
  remove_abbreviation() |>
  modify_abbreviation(
    "PR: Crude Prevalence Ratio; 95% CI: 95% Confidence Interval") |>
  as_flex_table() |>
  theme_booktabs() |>
  fontsize(size = 9, part = "all") |>
  align(align = "center", part = "all") |>
  align(align = "left", part = "footer") |>
  align(j = 1, align = "left", part = "body") |>
  padding(padding.top = 0.5, padding.bottom = 0.5, part = "all") |>
  set_table_properties(layout = "autofit")

# View
table_S4
```

## Table 3. Multiple regression analysis (multivariable)

Adjusted associations between sociodemographic factors and hematological outcomes among Peruvian infants aged 6–8 months.

::: {style="text-align: justify"}
Incluir el Department como una variable predictora (efecto fijo) es la opción más robusta debido a que, dado el número reducido de unidades de nivel Higher ($K=4$ clusters), un modelo de efectos mixtos no permitiría estimar de forma fiable la varianza inter-departamental ($\tau^2$). Asimismo, los estimadores de varianza robustos (clúster-robustos) como `vcovCL`, basados en la matriz de varianza-covarianza `sandwich` asintótica, requieren generalmente entre 30 y 50 clústeres para evitar el sesgo hacia abajo de los errores estándar y la consecuente inflación del error tipo I. Incluso métodos diseñados para muestras pequeñas como `vcovCR` (ajuste tipo `CR2`), que suelen ser válidos a partir de 10 o 15 clústeres, resultan inestables con tan solo 4 unidades debido a la insuficiencia de Grados de Libertad Efectivos (EDF). Al incorporar el Department como efecto fijo, el modelo controla explícitamente la heterogeneidad geográfica de base, permitiendo comparaciones ajustadas e inferencias válidas sobre la prevalencia de anemia y ferropenia. Sin embargo, se obserrvó alta correlación entre los Departments con el indice de riqueza y la hemoglobina ajustada por la altura.
::: 

```{r}
# Anemia
table_3a <- data |>
  fit_logbinomial_safe(anemia ~ etnia + wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif()

# Iron Deficiency
table_3b <- data |>
  fit_logbinomial_safe(ferropenia ~ etnia + wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif()

# Non-iron-deficiency anemia
table_3c <- data |>
  fit_logbinomial_safe(anemia_no_ferropenica ~ etnia + wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif()

# Iron-deficiency anemia
table_3d <- data |>
 fit_logbinomial_safe(anemia_ferropenica ~ etnia + wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif()

# Merge tables
table_3 <- tbl_merge(
  tbls = list(table_3a, table_3b, table_3c, table_3d),
  tab_spanner = c(
    "**Anemia**", "**Iron Deficiency**",
    "**Non-iron-deficiency anemia**", "**Iron-deficiency anemia**")) |>
  modify_header(
    label = "**Characteristics**",
    starts_with("estimate") ~ "**RPa (IC 95%)**") |>
  modify_caption(caption = "Table 3. Adjusted associations between sociodemographic factors and hematological outcomes among Peruvian infants aged 6–8 months") |>
  remove_abbreviation() |>
  modify_abbreviation(
    "RPa: Adjusted Prevalence Ratio; 95% CI: 95% Confidence Interval. The models were adjusted for the ethnic group, household wealth index, sex of children, and level of education.") |>
  as_flex_table() |>
  theme_booktabs() |>
  fontsize(size = 9, part = "all") |>
  align(align = "center", part = "all") |>
  align(align = "left", part = "footer") |>
  align(j = 1, align = "left", part = "body") |>
  padding(padding.top = 0.5, padding.bottom = 0.5, part = "all") |>
  set_table_properties(layout = "autofit")

# View
table_3
```

### Diagnosis of assumptions

::: {style="text-align: justify"}
Check the model assumptions for each outcome (anemia, ferropenia, anemia_no_ferropenica, and  anemia_ferropenica) only when an independent variable is numerical.
:::

```{r}
#| eval: false
# Anemia 
# Modelo 1: SIN Department 
m1 <- glm(
  anemia ~ etnia + wealth_3 + sexo + educacion,
  family = binomial(link = "log"),
  data = data
)

# Modelo 2: CON Department
m2 <- glm(
  anemia ~ etnia + wealth_3 + sexo + educacion + DEP,
  family = binomial(link = "log"),
  data = data
)

# Likelihood-Ratio-Test (LRT)
test_likelihoodratio(m1, m2)

# Model Performance Indices
model_performance(m1)
model_performance(m2)

# Comparison of Model Performance Indices
compare_performance(m1, m2, rank = TRUE, verbose = FALSE)

# Visualization of indices of models’ performance
plot(compare_performance(m1, m2, rank = TRUE, verbose = FALSE))

# Multicollinearity of model terms
check_collinearity(m2)
check_collinearity(m1)
```

## Table S5. Mestizo

Adjusted associations between sociodemographic factors and hematological outcomes among Mestizo infants.

```{r}
# Anemia
table_S5a <- data |>
  dplyr::filter(etnia == "Mestizo") |> 
  fit_logbinomial_safe(anemia ~ wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif() |>
  # modify_spanning_header(all_stat_cols() ~ "**Mestizo**")

# Iron Deficiency
table_S5b <- data |>
  dplyr::filter(etnia == "Mestizo") |> 
  fit_logbinomial_safe(ferropenia ~ wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif()

# Non-iron-deficiency anemia
table_S5c <- data |>
  dplyr::filter(etnia == "Mestizo") |>
  fit_logbinomial_safe(anemia_no_ferropenica ~ wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif()

# Iron-deficiency anemia
table_S5d <- data |>
  dplyr::filter(etnia == "Mestizo") |>
  fit_logbinomial_safe(anemia_ferropenica ~ wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif()

# Merge tables
table_S5 <- tbl_merge(
  tbls = list(table_S5a, table_S5b, table_S5c, table_S5d),
  tab_spanner = c(
    "**Anemia**", "**Iron Deficiency**", 
    "**Non-iron-deficiency anemia**", "**Iron-deficiency anemia**")) |>
  modify_header(
    label = "**Characteristics**",
    starts_with("estimate") ~ "**RPa (IC 95%)**") |>
  modify_caption(caption = "Supplementary Table S5. Adjusted associations between sociodemographic factors and hematological outcomes among Mestizo infants") |>
  remove_abbreviation() |>
  modify_abbreviation(
    "RPa: Adjusted Prevalence Ratio; 95% CI: 95% Confidence Interval") |>
  as_flex_table() |>
  theme_booktabs() |>
  fontsize(size = 9, part = "all") |>
  align(align = "center", part = "all") |>
  align(align = "left", part = "footer") |>
  align(j = 1, align = "left", part = "body") |>
  padding(padding.top = 0.5, padding.bottom = 0.5, part = "all") |>
  set_table_properties(layout = "autofit")

# View
table_S5
```

### Diagnosis of assumptions

```{r}
#| eval: false
# Modelo 1: SIN Department
m1 <- data |>
  filter(etnia == "Mestizo") |> 
  glm(
    anemia ~ wealth_3 + sexo + educacion, 
    family = binomial(link = "log"),
    data = _
  )

# Modelo 2: CON Department
m2 <- data |>
  filter(etnia == "Mestizo") |>
  glm(
    anemia ~ wealth_3 + sexo + educacion + DEP,
    family = binomial(link = "log"),
    data = _
  )

# Likelihood-Ratio-Test (LRT)
test_likelihoodratio(m1, m2)

# Model Performance Indices
model_performance(m1)
model_performance(m2)

# Comparison of Model Performance Indices
compare_performance(m1, m2, rank = TRUE, verbose = FALSE)

# Visualization of indices of models’ performance
plot(compare_performance(m1, m2, rank = TRUE, verbose = FALSE))

# Multicollinearity of model terms
check_collinearity(m2)
check_collinearity(m1)
```

## Table S6. Quechua/Aymara	

Adjusted associations between sociodemographic factors and hematological outcomes among Quechua/Aymara infants.

```{r}
# Anemia
table_S6a <- data |>
  dplyr::filter(etnia == "Quechua/Aymara") |> 
  fit_logbinomial_safe(anemia ~ wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif()

# Iron Deficiency
table_S6b <- data |>
  dplyr::filter(etnia == "Quechua/Aymara") |> 
  fit_logbinomial_safe(ferropenia ~ wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif()

# Non-iron-deficiency anemia
table_S6c <- data |>
  dplyr::filter(etnia == "Quechua/Aymara") |> 
  fit_logbinomial_safe(anemia_no_ferropenica ~ wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif()

# Iron-deficiency anemia
table_S6d <- data |>
  dplyr::filter(etnia == "Quechua/Aymara") |> 
  fit_logbinomial_safe(anemia_ferropenica ~ wealth_3 + sexo + educacion) |>
  tbl_robust()
  # add_vif()

# Merge tables
table_S6 <- tbl_merge(
  tbls = list(table_S6a, table_S6b, table_S6c, table_S6d),
  tab_spanner = c(
    "**Anemia**", "**Iron Deficiency**", "**Non-iron-deficiency anemia**", "**Iron-deficiency anemia**")) |>
  modify_header(
    label = "**Characteristics**",
    starts_with("estimate") ~ "**RPa (IC 95%)**") |>
  modify_caption(caption = "Supplementary Table S6. Adjusted associations between sociodemographic factors and hematological outcomes among Quechua/Aymara infants") |>
  remove_abbreviation() |>
  modify_abbreviation(
    "RPa: Adjusted Prevalence Ratio; 95% CI: 95% Confidence Interval") |>
  as_flex_table() |>
  theme_booktabs() |>
  fontsize(size = 9, part = "all") |>
  align(align = "center", part = "all") |>
  align(align = "left", part = "footer") |>
  align(j = 1, align = "left", part = "body") |>
  padding(padding.top = 0.5, padding.bottom = 0.5, part = "all") |>
  set_table_properties(layout = "autofit")

# View
table_S6
```

### Diagnosis of assumptions

```{r}
#| eval: false
# Modelo 1: SIN Department
m1 <- data |>
  filter(etnia == "Quechua/Aymara") |> 
  glm(
    anemia ~ wealth_3 + sexo + educacion, 
    family = binomial(link = "log"),
    data = _
  )

# Modelo 2: CON Department
m2 <- data |>
  filter(etnia == "Quechua/Aymara") |> 
  glm(
    anemia ~ wealth_3 + sexo + educacion + DEP,
    family = binomial(link = "log"),
    data = _
  )

# Likelihood-Ratio-Test (LRT)
test_likelihoodratio(m1, m2)

# Model Performance Indices
model_performance(m1)
model_performance(m2)

# Comparison of Model Performance Indices
compare_performance(m1, m2, rank = TRUE, verbose = FALSE)

# Visualization of indices of models’ performance
plot(compare_performance(m1, m2, rank = TRUE, verbose = FALSE))

# Multicollinearity of model terms
check_collinearity(m1)
check_collinearity(m2)
```

## Table for figure 1

```{r}
# Merge columns, essential for the triple header
theme_gtsummary_journal(journal = "jama")

# Anemia
table_a <- tbl_merge(tbls = list(table_S5a, table_S6a)) |> remove_abbreviation()
# Ferropenia
table_b <- tbl_merge(tbls = list(table_S5b, table_S6b)) |> remove_abbreviation()
# Non-iron-deficiency anemia
table_c <- tbl_merge(tbls = list(table_S5c, table_S6c)) |> remove_abbreviation()
# Iron-deficiency anemia
table_d <- tbl_merge(tbls = list(table_S5d, table_S6d)) |> remove_abbreviation()

# Stack tables
table_F1 <- tbl_merge(tbls = list(table_a, table_b, table_c, table_d))

# Triple header
table_F1 <- table_F1 |>
  as_flex_table() |>
  delete_part(part = "header") |>
  
  # Level 1: Estimates and 95% CI
  add_header_row(
    values = c("Determinantes Sociales", rep(c("RPa (IC 95%)", "Valor p"), 8))
  ) |>
  
  # Level 2: Ethnic group (Mestizo y Quechua/Aymara)
  add_header_row(values = c("", rep(
    c("Mestizo", "Mestizo", "Quechua/Aymara", "Quechua/Aymara"), 4))
  ) |> 
  
  # Level 3: Hematological status
  add_header_row(
    values = c(
      "",
      rep("Anemia", 4),
      rep("Iron Deficiency", 4),
      rep("Non-iron-deficiency anemia", 4),
      rep("Iron-deficiency anemia", 4)
    )
  ) |>
  
  add_footer_row(
    values = "RPa: Adjusted Prevalence Ratio; 95% CI: 95% Confidence Interval",
    colwidths = 17) |>
  
  # Fusionar horizontalmente (donde hay textos repetidos como "Anemia" o "Mestizo")
  merge_h(part = "header") |>
  # Fusionar verticalmente (para que "Determinantes Sociales" ocupe las 3 filas)
  merge_v(part = "header") |>
  
  # Theme
  theme_booktabs() |>
  align(align = "center", part = "all") |>
  align(align = "left", part = "footer") |>
  align(j = 1, align = "left", part = "body") |>
  fontsize(size = 9, part = "all") |>
  padding(padding.top = 0.5, padding.bottom = 0.5, part = "all") |>
  set_table_properties(layout = "autofit")

# View
table_F1
``` 

## Figure 1

Adjusted prevalence ratios for hematological outcomes according to sociodemographic factors, stratified by maternal ethnic group.

```{r}
#| fig-height: 9
#| fig-width: 8
# Combine all results
plot_data <- bind_rows(
  extract_forest_data(table_S5a, "Anemia", "Mestizo"),
  extract_forest_data(table_S5b, "Iron Deficiency", "Mestizo"),
  extract_forest_data(table_S5c, "Non-iron-deficiency anemia", "Mestizo"),
  extract_forest_data(table_S5d, "Iron-deficiency anemia", "Mestizo"),
  extract_forest_data(table_S6a, "Anemia", "Quechua/Aymara"),
  extract_forest_data(table_S6b, "Iron Deficiency", "Quechua/Aymara"),
  extract_forest_data(table_S6c, "Non-iron-deficiency anemia", "Quechua/Aymara"),
  extract_forest_data(table_S6d, "Iron-deficiency anemia", "Quechua/Aymara")
)

# Order of independent variables (Without references)
orden_labels <- c(
  "**Wealth index**", # Wealth index (ref. Poor)
  "  Middle", "  Rich",
  "**Sex of children**", # Sexo (ref. Masculino)
  "  Female",
  "**Level of education**", # Nivel educativo (ref. None or primary)
  "  Secondary", "  Higher"
  # "**Department**", # Department (ref. Arequipa)
  # "  Lima", "  Cusco", "  Puno"
)

# Ordered data
plot_data_ordered <- plot_data |>
  mutate(label = paste0("  ", label)) |>
  bind_rows(expand_grid(
    label = c(
      "**Wealth index**",
      "**Sex of children**",
      "**Level of education**"
      # "**Department**"
    ),
    Outcome = unique(plot_data$Outcome),
    Etnia = unique(plot_data$Etnia)
  )) |>
  # Formatear outcomes (Panel A, B, C, D)
  mutate(
    Outcome = case_match(
      Outcome,
      "Anemia" ~ "A. Anemia",
      "Iron Deficiency" ~ "B. Iron-deficiency",
      "Non-iron-deficiency anemia" ~ "C. Non-iron-deficiency anemia",
      "Iron-deficiency anemia" ~ "D. Iron-deficiency anemia"
    ),
    Outcome = factor(
      Outcome,
      levels = c(
        "A. Anemia",
        "B. Iron-deficiency",
        "C. Non-iron-deficiency anemia",
        "D. Iron-deficiency anemia"
      )
    ),
    label = factor(label, levels = orden_labels)
  )

# Plot
F1 <- ggplot(plot_data_ordered, aes(x = estimate, y = fct_rev(label), color = Etnia)) +
  # No effect line (RP = 1)
  geom_vline(xintercept = 1, linetype = "solid", color = "grey40", linewidth = 1) +
  # Points and confidence intervals
  geom_pointrange(
    aes(xmin = conf.low, xmax = conf.high), 
    position = position_dodge(width = 0.6), size = 0.6, fatten = 4) +
  # Panels by outcome
  facet_wrap(~ Outcome, scales = "free_x", ncol = 2) +
  # Log scale
  scale_x_log10(breaks = c(0.25, 0.5, 1, 2, 4), limits = c(0.1, 10)) +
  # Colors
  scale_color_manual(values = c("Mestizo" = "dodgerblue", "Quechua/Aymara" = "red2")) +
  # Labels
  labs(
    x = "adjusted Prevalence Ratio with 95% CI",
    color = "Ethnic group"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "bottom",
    legend.title = element_text(size = 12, face = "bold"),
    legend.margin = margin(t = -5, unit = "pt"),
    axis.title.y = element_blank(),
    axis.title.x = element_text(colour = "black", margin = margin(t = 20, unit = "pt")),
    axis.text.y = ggtext::element_markdown(size = 10, colour = "black"), 
    axis.text.x = element_text(colour = "black"),
    strip.text = element_text(face = "bold", size = 12, hjust = 0),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.major.x = element_line(linetype = 2, color = "grey70", linewidth = 1),
    panel.spacing = unit(1, "lines"),
    axis.line = element_line(colour = "black", linewidth = 1),
    axis.ticks = element_line(colour = "black", linewidth = 1)
  )

# View
F1
```

## Figure 2. Marginal effects for education level

Adjusted prevalence of hematological outcomes according to maternal educational level and ethnic group.

```{r}
df_anemia <- get_margins_table(
  df = data,
  outcome = "anemia",
  x_var = "educacion",
  group_var = "etnia",
  covars = c("sexo", "wealth_3")
) |>
  mutate(across(where(is.numeric), \(x) round(x, digits = 3))) |>
  mutate(Outcome = "Anemia", .before = 1)

df_ferropenia <- get_margins_table(
  df = data,
  outcome = "ferropenia",
  x_var = "educacion",
  group_var = "etnia",
  covars = c("sexo", "wealth_3")
) |>
  mutate(across(where(is.numeric), \(x) round(x, digits = 3))) |>
  mutate(Outcome = "Iron Deficiency", .before = 1)

df_anemia_nofe <- get_margins_table(
  df = data,
  outcome = "anemia_no_ferropenica",
  x_var = "educacion",
  group_var = "etnia",
  covars = c("sexo", "wealth_3")
) |>
  mutate(across(where(is.numeric), \(x) round(x, digits = 3))) |>
  mutate(Outcome = "Non-Iron-Deficiency Anemia", .before = 1)

df_anemia_fe <- get_margins_table(
  df = data,
  outcome = "anemia_ferropenica",
  x_var = "educacion",
  group_var = "etnia",
  covars = c("sexo", "wealth_3")
) |>
  mutate(across(where(is.numeric), \(x) round(x, digits = 3))) |>
  mutate(Outcome = "Iron-Deficiency Anemia", .before = 1)

tabla_margins_edu <- bind_rows(df_anemia, df_ferropenia, df_anemia_nofe, df_anemia_fe) |>
  rename(
    `Resultado` = Outcome,
    `Nivel Educativo` = educacion,
    `Grupo Étnico` = etnia
  ) |> 
  flextable() |>
  theme_booktabs() |>
  merge_v(j = 1) |> 
  fix_border_issues() |>
  autofit() |>
  align(j = 4:6, align = "center", part = "all") |>
  bold(part = "header")
```

```{r}
#| fig-height: 8
#| fig-width: 10
pA_edu <- plot_margins_logbin(
  df = data,
  outcome = "anemia",
  letter = "A",
  x_var = "educacion",
  covars = c("sexo", "wealth_3")
)

pB_edu <- plot_margins_logbin(
  df = data,
  outcome = "ferropenia",
  letter = "B",
  x_var = "educacion",
  covars = c("sexo", "wealth_3")
)

pC_edu <- plot_margins_logbin(
  df = data,
  outcome = "anemia_no_ferropenica",
  letter = "C",
  x_var = "educacion",
  covars = c("sexo", "wealth_3")
)

pD_edu <- plot_margins_logbin(
  df = data,
  outcome = "anemia_ferropenica",
  letter = "D",
  x_var = "educacion",
  covars = c("sexo", "wealth_3")
)

# Merge plots
Fig_Edu_ABCD <- ggarrange(
  pA_edu, pB_edu, pC_edu, pD_edu, 
  ncol = 2, nrow = 2, 
  common.legend = TRUE, 
  legend = "top")

# Common axes
Fig_Edu_ABCD <- annotate_figure(
  Fig_Edu_ABCD,
  left = text_grob(
    "Predicted prevalence of outcome", rot = 90, face = "bold", size = 14),
  bottom = text_grob("Level of education", face = "bold", size = 14) 
)

# View
Fig_Edu_ABCD
```

## Figure 3. Marginal effects for wealth index

Adjusted prevalence of hematological outcomes according to household wealth index and ethnic group.

```{r}
df_anemia <- get_margins_table(
  df = data,
  outcome = "anemia",
  x_var = "wealth_3",
  group_var = "etnia",
  covars = c("sexo", "educacion")
) |>
  mutate(across(where(is.numeric), \(x) round(x, digits = 3))) |>
  mutate(Outcome = "Anemia", .before = 1)

df_ferropenia <- get_margins_table(
  df = data,
  outcome = "ferropenia",
  x_var = "wealth_3",
  group_var = "etnia",
  covars = c("sexo", "educacion")
) |>
  mutate(across(where(is.numeric), \(x) round(x, digits = 3))) |>
  mutate(Outcome = "Iron Deficiency", .before = 1)

df_anemia_nofe <- get_margins_table(
  df = data,
  outcome = "anemia_no_ferropenica",
  x_var = "wealth_3",
  group_var = "etnia",
  covars = c("sexo", "educacion")
) |>
  mutate(across(where(is.numeric), \(x) round(x, digits = 3))) |>
  mutate(Outcome = "Non-Iron-Deficiency Anemia", .before = 1)

df_anemia_fe <- get_margins_table(
  df = data,
  outcome = "anemia_ferropenica",
  x_var = "wealth_3",
  group_var = "etnia",
  covars = c("sexo", "educacion")
) |>
  mutate(across(where(is.numeric), \(x) round(x, digits = 3))) |>
  mutate(Outcome = "Iron-Deficiency Anemia", .before = 1)

tabla_margins_wealth <- bind_rows(df_anemia, df_ferropenia, df_anemia_nofe, df_anemia_fe) |>
  rename(
    `Resultado` = Outcome,
    `Wealth index` = wealth_3,
    `Grupo Étnico` = etnia
  ) |> 
  flextable() |>
  theme_booktabs() |>
  merge_v(j = 1) |> 
  fix_border_issues() |>
  autofit() |>
  align(j = 4:6, align = "center", part = "all") |>
  bold(part = "header")
```


```{r}
#| fig-height: 8
#| fig-width: 10
pA_w <- plot_margins_logbin(
  df = data,
  outcome = "anemia",
  letter = "A",
  x_var = "wealth_3",
  covars = c("sexo", "educacion")
)

pB_w <- plot_margins_logbin(
  df = data,
  outcome = "ferropenia",
  letter = "B",
  x_var = "wealth_3",
  covars = c("sexo", "educacion")
)

pC_w <- plot_margins_logbin(
  df = data,
  outcome = "anemia_no_ferropenica",
  letter = "C",
  x_var = "wealth_3",
  covars = c("sexo", "educacion")
)

pD_w <- plot_margins_logbin(
  df = data,
  outcome = "anemia_ferropenica",
  letter = "D",
  x_var = "wealth_3",
  covars = c("sexo", "educacion")
)

# Merge plots
Fig_Wealth_ABCD <- ggarrange(
  pA_w, pB_w, pC_w, pD_w, 
  ncol = 2, nrow = 2, 
  common.legend = TRUE, 
  legend = "top"
)

# Common axes
Fig_Wealth_ABCD <- annotate_figure(
  Fig_Wealth_ABCD,
  left = text_grob(
    "Predicted prevalence of outcome", rot = 90, face = "bold", size = 14),
  bottom = text_grob("Wealth index", face = "bold", size = 14) 
)

# View
Fig_Wealth_ABCD
```

## Linear Model (Naive model)

```{r}
#| eval: false
#| fig-height: 4
#| fig-width: 8
# Model
mod_anemia <- glm(
  anemia ~ etnia * educacion + sexo + wealth_3 + DEP, 
  data = data, family = binomial(link = "log"))

# Model summary
summary(mod_anemia)
tidy(mod_anemia, exponentiate = TRUE, conf.int = TRUE)

# Predicted values
fitted_glm_1 <- predict_response(
  mod_anemia, terms = c("wealth_3", "Ethnic group"), margin = "empirical")

fitted_glm_2 <- predict_response(
  mod_anemia, terms = c("educacion", "Ethnic group"), margin = "empirical")

# Plot
a1_mod_anemia <- plot(fitted_glm_1)
a2_mod_anemia <- plot(fitted_glm_2)

# View
ggarrange(
  a1_mod_anemia, a2_mod_anemia, ncol = 2, nrow = 1, 
  common.legend = TRUE, legend = "bottom")
```

## Restricted cubic spline (natural spline).

```{r}
#| eval: false
#| fig-height: 8
#| fig-width: 8
# Model
rcs_anemia <- glm(
  anemia ~ rcs(ferr_adj, 3) + wealth_3 + sexo + etnia + educacion + DEP, 
  data = data, family = binomial(link = "logit"))

# Model summary
summary(rcs_anemia)
tidy(rcs_anemia, exponentiate = TRUE, conf.int = TRUE)

# Predicted values
fitted_rcs_1 <- predict_response(
  rcs_anemia, terms = c("ferr_adj", "wealth_3", "Ethnic group"))

fitted_rcs_2 <- predict_response(
  rcs_anemia, terms = c("ferr_adj", "educacion", "Ethnic group"))

# Plot
a1_rcs_anemia <- plot(fitted_rcs_1)
a2_rcs_anemia <- plot(fitted_rcs_2)

# View
ggarrange(
  a1_rcs_anemia, a2_rcs_anemia, ncol = 1, nrow = 2, 
  common.legend = FALSE, legend = "right")
```

## GAM (Cubic regression splines and REML)

```{r}
#| eval: false
#| fig-height: 8
#| fig-width: 8
# Model
gam_anemia <- gam(
  anemia ~ 
    s(ferr_adj, k = -1, bs = "cr") + etnia + wealth_3 + sexo + educacion + DEP, 
  data = data, family = binomial(link = "logit"), method = "REML", select = TRUE)

# Model summary
summary(gam_anemia)
tidy(gam_anemia, exponentiate = TRUE, conf.int = TRUE)

# Predicted values
fitted_gam_1 <- predict_response(
  gam_anemia, terms = c("ferr_adj", "wealth_3", "Ethnic group"))

fitted_gam_2 <- predict_response(
  gam_anemia, terms = c("ferr_adj", "educacion", "Ethnic group"))

# Plot
a1_gam_anemia <- plot(fitted_gam_1)
a2_gam_anemia <- plot(fitted_gam_2)

# View
ggarrange(
  a1_gam_anemia, a2_gam_anemia, ncol = 1, nrow = 2, 
  common.legend = FALSE, legend = "right")
```

## Venn plot

```{r}
#| eval: false
#| fig-height: 5
#| fig-width: 7
lista_venn <- list(
  Ferropenia = which(data$ferropenia == 1),
  Anemia = which(data$anemia == 1)
)

test_1 <- ggVennDiagram(
  lista_venn,
  category.names = c("A. Ferropenia", "B. Anemia"),
  set_color = "black",
  label_color = "black",
  label = "both",
  label_alpha = 0,
  edge_size = 1
) +
  coord_flip() +
  scale_fill_gradient(low = "#1E90FF66", high = "#EE000066") +
  theme(
    legend.position = "none",
    panel.background = element_blank()
  )

# View
test_1
```

```{r}
#| eval: false
#| include: false
summary_hematological_states <- data |>
  count(hematological_states) |>
  mutate(
    porcentaje = (n / sum(n)) * 100,
    label = paste0(round(porcentaje, 1), "%")
  ) |>
  arrange(desc(porcentaje))
```

## Euler plot

```{r}
#| fig-height: 5
#| fig-width: 7

# Calculate the totals and the intersection
n_ferropenia <- sum(data$ferropenia == 1 & data$anemia == 0, na.rm = TRUE)
n_anemia <- sum(data$anemia == 1 & data$ferropenia == 0, na.rm = TRUE)
n_ambos <- sum(data$anemia == 1 & data$ferropenia == 1, na.rm = TRUE)
n_total <- nrow(data)

# Adjust the model
fit <- euler(c(
  "Ferropenia" = n_ferropenia,
  "Anemia" = n_anemia,
  "Ferropenia&Anemia" = n_ambos
))

# Prepare the numeric texts
txt_f <- paste0("'", n_ferropenia, " (", round(n_ferropenia / n_total * 100, 1), "%)'")
txt_a <- paste0("'", n_anemia, " (", round(n_anemia / n_total * 100, 1), "%)'")
txt_ambos <- paste0("'", n_ambos, " (", round(n_ambos / n_total * 100, 1), "%)'")

# Use parse() and atop() to create expressions: Up (bold) and Down (normal)
labs_internas <- parse(text = c(
  paste0("atop(bold('Ferropenia'), ", txt_f, ")"),
  paste0("atop(bold('Anemia no ferropénica'), ", txt_a, ")"),
  paste0("atop(bold('Anemia ferropénica'), ", txt_ambos, ")")
))

# Plot
euler_plot <- plot(fit,
  # Turn off the top labels of the circles
  labels = FALSE,
  
  # Legend
  legend = list(
    col = "black",
    fontsize = 12,
    fontface = "bold",
    side = "bottom",
    nrow = 1,
    ncol = 2
  ),
  # Internal labels 
  quantities = list(
    labels = labs_internas,
    fontsize = 10,
    fontface = "plain"
  ),
  
  # Theme
  fill = c("skyblue", "tomato"), 
  alpha = 0.5,
  edges = list(col = "black", lwd = 2)
)

# View
euler_plot
```

# Save outputs

## Section properties

```{r}
# Definir las propiedades de la sección (Horizontal)
sect_properties_h <- prop_section(
  page_size = page_size(orient = "landscape"),
  page_margins = page_mar(bottom = 0.5, top = 0.5, right = 0.5, left = 0.5),
  type = "continuous"
)

# Definir las propiedades de la sección (Vertical)
sect_properties_v <- prop_section(
  page_size = page_size(orient = "portrait"),
  page_margins = page_mar(bottom = 0.5, top = 0.5, right = 0.5, left = 0.5),
  type = "continuous"
)
```

## Tables

```{r}
# Tables
save_as_docx(
  table_1,
  align = "center",
  path = here("outputs", "Table 1_by ethnicity.docx"),
  pr_section = sect_properties_v)

save_as_docx(
  table_2,
  align = "center",
  path = here("outputs", "Table 2_by disease.docx"),
  pr_section = sect_properties_h)

save_as_docx(
  table_3,
  align = "center",
  path = here("outputs", "Table 3_multivariable.docx"),
  pr_section = sect_properties_h)

# Supplementary tables
save_as_docx(
  table_S1,
  align = "center",
  path = here("outputs", "Table S1_reliability.docx"),
  pr_section = sect_properties_v)

save_as_docx(
  table_S2,
  align = "center",
  path = here("outputs", "Table S2_item statistics.docx"),
  pr_section = sect_properties_v)

save_as_docx(
  table_S3,
  align = "center",
  path = here("outputs", "Table S3_loadings.docx"),
  pr_section = sect_properties_v)

save_as_docx(
  table_S4,
  align = "center",
  path = here("outputs", "Table S4_univariable.docx"),
  pr_section = sect_properties_h)

save_as_docx(
  table_S5,
  align = "center",
  path = here("outputs", "Table S5_mestizo.docx"),
  pr_section = sect_properties_h)

save_as_docx(
  table_S6,
  align = "center",
  path = here("outputs", "Table S6_quechua.docx"),
  pr_section = sect_properties_h)

save_as_docx(
  table_F1,
  align = "center",
  path = here("outputs", "Table for figure 1.docx"),
  pr_section = sect_properties_h)

save_as_docx(
  tabla_margins_edu,
  align = "center",
  path = here("outputs", "Table for figure 2.docx")
)

save_as_docx(
  tabla_margins_wealth,
  align = "center",
  path = here("outputs", "Table for figure 3.docx"))
```

## Figures

```{r}
# Figure 1
ggsave(
  here::here("outputs", "Figure_1.png"),
  F1,
  width = 8,
  height = 8,
  dpi = 600
)

ggsave(
  here::here("outputs", "Figure_1.jpeg"),
  F1,
  width = 8,
  height = 8,
  dpi = 600
)

# Figure 2
ggsave(
  here::here("outputs", "Figure_2_Education.png"),
  Fig_Edu_ABCD,
  width = 10,
  height = 8,
  dpi = 600
)

# Figure 3
ggsave(
  here::here("outputs", "Figure_3_Wealth.png"),
  Fig_Wealth_ABCD,
  width = 12,
  height = 8,
  dpi = 600
)

# Supplementary figure 1
ggsave(
  here::here("outputs", "Figure_S1_loading plot.png"),
  FS1,
  height = 8,
  dpi = 600
)

# Supplementary figure 2
ggsave(
  here::here("outputs", "Figure_S2_quantification plot.png"),
  FS2,
  width = 8,
  height = 6,
  dpi = 600
)

# Euler plot
ggsave(
  here::here("outputs", "Euler_plot.png"),
  euler_plot,
  width = 7,
  height = 5,
  dpi = 600
)
```

