---
title: "Ferritina"
author: "Carlos Ballón-Salcedo"
date: "`r Sys.Date()`"
format:
  html:
    theme: 
     light: lux
     dark: darkly
    toc: true        # índice automático
    toc-depth: 3     # niveles de encabezado en el índice
    code-overflow: wrap
    highlight-style: github
    number-sections: true
    code-fold: true  # plegar código
    code-tools: 
      source: "https://github.com/Carlos-Ballon/ferritin-anemia_diagnosis.git"
editor: source
execute:
  message: false
  warning: false
bibliography: grateful-refs.bib
csl: vancouver.csl
lang: en             # idioma del documento
---

# Load packages

```{r}
pacman::p_load(
  tidyverse,
  rio,
  here,
  circlize,
  epiDisplay,
  Hmisc,
  labelled,
  networkD3,
  ggalluvial,
  ggplot2,
  ggsankey,
  psych,
  factoextra,
  ggpubr,
  rms,
  mgcv,
  broom,
  ggeffects,
  rfextras,
  grateful)

# Citations
grateful::cite_packages(
  output = "file",
  out.format = "docx",
  out.dir = ".",
  citation.style = "vancouver")
```

# Import data

```{r}
data <- import(here("data", "base_de_curvas.dta"))
load_scripts()
```

# Process data

```{r}
data <- data |>
  mutate(
    anemia = if_else(P037 >= 10.5, 0L, 1L),
    ferropenia = if_else(ferr_adj >= 12, 0L, 1L)
  )
```

```{r}
#| eval: false
contents(data)
glimpse(data)
```

# Produce outputs

## Ferritin

### Linear Model (Naive model)

```{r}
# Model
mod_ferritin <- glm(
  anemia ~ ferr_adj, data = data, family = binomial(link = "logit"))

summary(mod_ferritin)

# Predicted values
fitted_lin <- predict_response(
  mod_ferritin, terms = "ferr_adj", margin = "mean_reference")

# View
a1 <- plot(fitted_lin)
plot(fitted_lin)
```

### Restricted cubic spline (natural spline)

```{r}
# Restricted cubic spline (natural spline)
mod_rcs_ferritin <- glm(
  anemia ~ rcs(ferr_adj, 3), data = data, family = binomial(link = "logit"))

summary(mod_rcs_ferritin)

# Predicted values
fitted_rcs <- predict_response(
  mod_rcs_ferritin, terms = "ferr_adj", margin = "mean_reference")

# View
b1 <- plot(fitted_rcs)
plot(fitted_rcs)
```

### GAM

```{r}
# Cubic regression splines with REML
mod_gam_ferritin  <- gam(
  anemia ~ s(ferr_adj, k = 4, bs = "cr"),
  data = data,
  family = binomial(link = "logit"),
  method = "REML",
  select = TRUE
)

summary(mod_gam_ferritin)

# Predicted values
fitted_gam <- predict_response(mod_gam_ferritin, terms = "ferr_adj")

# View
c1 <- plot(fitted_gam)
plot(fitted_gam)
```

## Transferrin

### Linear Model (Naive model)

```{r}
# Model
mod_transferrin <- glm(
  anemia ~ P032, data = data, family = binomial(link = "logit"))

summary(mod_transferrin)

# Predicted values
fitted_lin <- predict_response(
  mod_transferrin, terms = "P032", margin = "mean_reference")

# View
a2 <- plot(fitted_lin)
plot(fitted_lin)
```

### Restricted cubic spline (natural spline)

```{r}
# Restricted cubic spline (natural spline)
mod_rcs_transferrin <- glm(
  anemia ~ rcs(P032, 3), data = data, family = binomial(link = "logit"))

summary(mod_rcs_transferrin)

# Predicted values
fitted_rcs <- predict_response(
  mod_rcs_transferrin, terms = "P032", margin = "mean_reference")

# View
b2 <- plot(fitted_rcs)
plot(fitted_rcs)
```

### GAM

```{r}
# Cubic regression splines with REML
mod_gam_transferrin  <- gam(
  anemia ~ s(P032, k = 4, bs = "cr"),
  data = data,
  family = binomial(link = "logit"),
  method = "REML",
  select = TRUE
)

summary(mod_gam_transferrin)

# Predicted values
fitted_gam <- predict_response(mod_gam_transferrin, terms = "P032")

# View
c2 <- plot(fitted_gam)
plot(fitted_gam)
```

## Altitude

### Linear Model (Naive model)

```{r}
# Model
mod_altitude <- glm(
  anemia ~ P017, data = data, family = binomial(link = "logit"))

summary(mod_altitude)

# Predicted values
fitted_lin <- predict_response(
  mod_altitude, terms = "P017", margin = "mean_reference")

# View
a3 <- plot(fitted_lin)
plot(fitted_lin)
```

### Restricted cubic spline (natural spline)

```{r}
# Restricted cubic spline (natural spline)
mod_rcs_altitude <- glm(
  anemia ~ rcs(P017, 3), data = data, family = binomial(link = "logit"))

summary(mod_rcs_altitude)

# Predicted values
fitted_rcs <- predict_response(
  mod_rcs_altitude, terms = "P017", margin = "mean_reference")

# View
b3 <- plot(fitted_rcs)
plot(fitted_rcs)
```

### GAM

```{r}
# Cubic regression splines with REML
mod_gam_altitude  <- gam(
  anemia ~ s(P017, k = 4, bs = "cr"),
  data = data,
  family = binomial(link = "logit"),
  method = "REML",
  select = TRUE
)

summary(mod_gam_altitude)

# Predicted values
fitted_gam <- predict_response(mod_gam_altitude, terms = "P017")

# View
c3 <- plot(fitted_gam)
plot(fitted_gam)
```
## Ferritin + Altitude

### Linear Model (Naive model)

```{r}
# Model
mod_ferritin_altitude <- glm(
  anemia ~ ferr_adj + P017, data = data, family = binomial(link = "logit"))

summary(mod_ferritin_altitude)

# Predicted values
fitted_lin <- predict_response(
  mod_ferritin_altitude, terms = c("ferr_adj", "P017"), margin = "mean_reference")

# View
a4 <- plot(fitted_lin)
plot(fitted_lin)
```

### Restricted cubic spline (natural spline)

```{r}
# Restricted cubic spline (natural spline)
mod_rcs_ferritin_altitude <- glm(
  anemia ~ rcs(ferr_adj, 3) + rcs(P017, 3), data = data, family = binomial(link = "logit"))

summary(mod_rcs_ferritin_altitude)

# Predicted values
fitted_rcs <- predict_response(
  mod_rcs_ferritin_altitude, terms = c("ferr_adj", "P017"), margin = "mean_reference")

# View
b4 <- plot(fitted_rcs)
plot(fitted_rcs)
```

### GAM

```{r}
# Cubic regression splines with REML
mod_gam_ferritin_altitude  <- gam(
  anemia ~ s(ferr_adj, k = 4, bs = "cr") + s(P017, k = 4, bs = "cr"),
  data = data,
  family = binomial(link = "logit"),
  method = "REML",
  select = TRUE
)

summary(mod_gam_ferritin_altitude)

# Predicted values
fitted_gam <- predict_response(mod_gam_ferritin_altitude, terms = c("ferr_adj", "P017"))

# View
c4 <- plot(fitted_gam)
plot(fitted_gam)
```

## Ferritin + Wealth index

### Linear Model (Naive model)

```{r}
# Model
mod_ferritin_wealth <- glm(
  anemia ~ ferr_adj + wealth_5, data = data, family = binomial(link = "logit"))

summary(mod_ferritin_wealth)

# Predicted values
fitted_lin <- predict_response(
  mod_ferritin_wealth, terms = c("ferr_adj", "wealth_5"), margin = "mean_reference")

# View
a5 <- plot(fitted_lin)
plot(fitted_lin)
```

### Restricted cubic spline (natural spline)

```{r}
data$wealth_5 <- as.numeric(data$wealth_5)

# Restricted cubic spline (natural spline)
mod_rcs_ferritin_wealth <- glm(
  anemia ~ rcs(ferr_adj, 3) + wealth_5, data = data, family = binomial(link = "logit"))

summary(mod_rcs_ferritin_wealth)

# Predicted values
fitted_rcs <- predict_response(
  mod_rcs_ferritin_wealth, terms = c("ferr_adj", "wealth_5"), margin = "mean_reference")

# View
b5 <- plot(fitted_rcs)
plot(fitted_rcs)
```

### GAM

```{r}
# Cubic regression splines with REML
mod_gam_ferritin_wealth  <- gam(
  anemia ~ s(ferr_adj, k = 6, bs = "cr") + wealth_5,
  data = data,
  family = binomial(link = "logit"),
  method = "REML",
  select = TRUE
)

summary(mod_gam_ferritin_wealth)

# Predicted values
fitted_gam <- predict_response(mod_gam_ferritin_wealth, terms = c("ferr_adj", "wealth_5"))

# View
c5 <- plot(fitted_gam)
plot(fitted_gam)
```

## Ferritin + Transferrin

### Linear Model (Naive model)

```{r}
# Model
mod_ferritin_transferrin <- glm(
  anemia ~ ferr_adj + P032, data = data, family = binomial(link = "logit"))

summary(mod_ferritin_transferrin)

# Predicted values
fitted_lin <- predict_response(
  mod_ferritin_transferrin, terms = c("ferr_adj", "P032"), margin = "mean_reference")

# View
a6 <- plot(fitted_lin)
plot(fitted_lin)
```

### Restricted cubic spline (natural spline)

```{r}
# Restricted cubic spline (natural spline)
mod_rcs_ferritin_transferrin <- glm(
  anemia ~ rcs(ferr_adj, 3) + rcs(P032, 3), data = data, family = binomial(link = "logit"))

summary(mod_rcs_ferritin_transferrin)

# Predicted values
fitted_rcs <- predict_response(
  mod_rcs_ferritin_transferrin, terms = c("ferr_adj", "P032"), margin = "mean_reference")

# View
b6 <- plot(fitted_rcs)
plot(fitted_rcs)
```

### GAM

```{r}
# Cubic regression splines with REML
mod_gam_ferritin_transferrin  <- gam(
  anemia ~ s(ferr_adj, k = 4, bs = "cr") + s(P032, k = 4, bs = "cr"),
  data = data,
  family = binomial(link = "logit"),
  method = "REML",
  select = TRUE
)

summary(mod_gam_ferritin_transferrin)

# Predicted values
fitted_gam <- predict_response(mod_gam_ferritin_transferrin, terms = c("ferr_adj", "P032"))

# View
c6 <- plot(fitted_gam)
plot(fitted_gam)
```

# Plots

```{r}
#| fig-height: 18
#| fig-width: 25
ggarrange(a1, b1, a1, a2, b2, c2, a3, b3, c3, a4, b4, c4, a5, b5, c5, a6, b6, c6, 
          ncol = 3, nrow = 4)


```

# Save outputs

```{r}

```

