---
title: "Ferritina"
author: "Carlos Ballón-Salcedo"
date: "`r Sys.Date()`"
format:
  html:
    theme: 
     light: lux
     dark: darkly
    toc: true        # índice automático
    toc-depth: 3     # niveles de encabezado en el índice
    code-overflow: wrap
    include-after-body: zoom_in_out.js
    highlight-style: github
    number-sections: true
    code-fold: true  # plegar código
    code-tools: 
      source: "https://github.com/Carlos-Ballon/ferritin-anemia_diagnosis.git"
editor: source
execute:
  message: false
  warning: false
bibliography: grateful-refs.bib
csl: vancouver.csl
lang: en             # idioma del documento
---

# Load packages

```{r}
# Packages
pacman::p_load(
  tidyverse,
  rio,
  here,
  epiDisplay,
  Hmisc,
  sjlabelled,
  ggalluvial,
  ggplot2,
  ggsankey,
  psych,
  factoextra,
  ggpubr,
  rms,
  mgcv,
  broom,
  ggeffects,
  rfextras,
  grateful,
  flextable,
  janitor,
  performance,
  gtsummary,
  finalfit)
```

```{r}
#| eval: false
# Citations
grateful::cite_packages(
  output = "file",
  out.format = "docx",
  out.dir = ".",
  citation.style = "vancouver")
```

# Import data

```{r}
# Data
data <- import(here("data", "base_de_curvas.dta"))

# Scripts
rfextras::load_scripts()
```

# Process data

```{r}
# Select categorical variables (to factor)
vars <- c(
  "P001", "P002", "P004", "P005", "P006", "P007", "P008", "P009", "P010", "P011",
  "P012", "P013", "P014", "P015", "P018", "P019", "P020", "P021", "P022", "P023",
  "P024", "P025", "P028", "P029", "anemia", "ferropenia")

data <- data |>
  dplyr::select(-wealth_pc1_raw, -wealth_pc1) |>
  mutate(
    anemia = if_else(P037 < 10.5, 1L, 0L),
    ferropenia = if_else(ferr_adj < 12, 1L, 0L),
    patologia = case_when(
      anemia == 1 & ferropenia == 1 ~ "Anemia ferropénica",
      anemia == 1 & ferropenia == 0 ~ "Anemia no ferropénica",
      anemia == 0 & ferropenia == 1 ~ "Ferropenia sin anemia",
      anemia == 0 & ferropenia == 0 ~ "Sano/Normal",
      TRUE ~ "Otro"
    )
  ) |>
  mutate(across(all_of(vars), ~ replace(.x, .x >= 99, NA))) |>
  mutate(across(all_of(vars), as_factor)) |>
  filter(P015 %in% c(1, 2, 6)) |>
  mutate(
    etnia = case_match(
      P015,
      "1" ~ "Quechua/Aymara",
      "2" ~ "Quechua/Aymara",
      "6" ~ "Mestizo",
      .default = NA_character_
    ) |>
      fct_relevel("Mestizo", "Quechua/Aymara"),
    educacion = case_match(
      P007, c("0", "1", "2") ~ "Primaria o ninguno", "3" ~ "Secundaria", c("4", "5") ~ "Superior") |>
      fct_relevel("Bajo", "Medio", "Alto")
  )
```

# Data dictionary / structure

```{r}
#| eval: false
# Generate a data dictionary
labelled::generate_dictionary(data)

# Inspect variable labels and data.frame structure
labelled::var_label(data)  # list of variable labels (if available)
Hmisc::contents(data)      # data.frame of variable types and missing values
dplyr::glimpse(data)       # compact structure
str(data)                  # detailed structure

# Inspect labels of specific variables
attributes(data$P001)   
```

# Exploratory Data Analysis

::: {style="text-align: justify"}
There are R packages that provide functions with the same name, such as `describe()` from the `Hmisc` package and `describe()` from the `psych` package. The former is more suitable for categorical data, while the latter is designed for numerical data. The `epiDisplay` package also offers powerful functions inspired by **Stata**, such as `summ()`. Other important options include the `janitor` package for data cleaning, as well as projects from the R Epidemics Consortium (RECON), Epiverse-TRACE, and R4EPI, which provide tools for epidemiological analysis.
:::

## Categorical data

```{r}
#| eval: false
# Select categorical variables (factors)
categorical_vars <- data |>
  dplyr::select(where(\(x) is.character(x) | is.factor(x)))
```

### Stucture of categorical variables

```{r}
#| eval: false
# Concise statistical description (display labels)
Hmisc::describe(categorical_vars, exclude.missing = FALSE)
```

### Missing values and complete cases

```{r}
#| eval: false
# Count of missing values by column (vector)
colSums(is.na(categorical_vars))

# List of complete values by column
lapply(categorical_vars, function(x)
  sum(complete.cases(x)))

# Columns without missing values (vector)
colnames(categorical_vars)[sapply(categorical_vars, function(x)
  all(!is.na(x)))]
```

### Duplicate elements

::: {style="text-align: justify"}
The `duplicated()` function identifies duplicate elements, `unique()` extracts unique elements, and `distinct()` from dplyr package removes duplicate rows from a data frame.
:::

### Descriptive analysis: Measures of frequency and proportions

```{r}
#| eval: false
# Absolute frequency for categorical variables
lapply(categorical_vars, function(x)
  addmargins(table(x, useNA = "ifany")))

# Relative frequency for categorical variables
lapply(categorical_vars, function(x)
  round(addmargins(prop.table(table(x)) * 100), 1))
  
# Absolute frequency for categorical variables by anemia
lapply(categorical_vars, function(x)
  addmargins(table(x, categorical_vars$anemia)))

# Flextable
categorical_vars |>
  tabyl(anemia, ferropenia) |>
  adorn_totals(where = "both") |>
  adorn_percentages(denominator = "col") |>
  adorn_pct_formatting() |>
  adorn_ns(position = "front") |>
  flextable() |>
  autofit()
```

## Numerical data

```{r}
#| eval: false
# Selection of variables
numerical_vars <- data |>
  dplyr::select(where(\(x) is.numeric(x)), anemia, ferropenia)
```

#### Descriptive statistics: Summary statistics

```{r}
#| eval: false
# Compact
numerical_vars |> epiDisplay::summ(digits = 2, na.rm = FALSE)

# Detailed
numerical_vars |> psych::describe(na.rm = FALSE)
```

#### Descriptive statistics: Grouped summary statistics

```{r}
#| eval: false
# Anemia
numerical_vars |>
  dplyr::group_split(anemia) |>
  lapply(function(data)
    summ(numerical_vars, digits = 2, na.rm = TRUE))

# Ferropenia
numerical_vars |>
  dplyr::group_split(ferropenia) |>
  lapply(function(data)
    summ(numerical_vars, digits = 2, na.rm = TRUE))
```

# Produce outputs

```{r}
data_test <- data |>
  dplyr::filter(ferropenia == "1") |> # Sin ferropenia
  rename(anemia_no_ferropenia = anemia)
```

Anemia no relacionada con ferropenia

Objetivo: Evaluar las brechas entre grupos etnicos relacionadas con la anemia no ferropenica según el SES

Evaluar si la etica se asocia a la ferropenia

Evaluar si la asociación entre el índice de riqueza del hogar y la prevalencia de anemia y ferropenia infantil difiere según la pertenencia étnica (mestizos, quechuas y aymaras)

Evaluar si la etnicidad se asocia (o influye) a la prevalencia de anemia o ferropenia infantil

Evaluar si la etnicidad se asocia a la prevalencia de ferropenia infantil

Anemia, anemia ferropenica, anemia no ferropenica, ferropenia. El mensaje seria "En el gradiente, tener un mejor SES reduce los niveles de anemia, pero la brecha por etnicidad es más grande en ferropenia que en anemia no ferropenica y probablemente que en anemia".

Posible resultado: La brecha es mas grande en ferropenia que en anemia no ferropenica

El muestreo nace en el establecimento de salud, basado en el CRED

8 graficos

Tabla 1. Descritiva
Tabla 2. Bivariada de grupos etnicos
Tabla 3. Anemia ferropenica, anemia no ferropenica, ferropenia (solo si ferropenia), anemia total
Tabla 4. Modelos
Figura 1. 4 cosas = SES + etnica
Figura 2. 4 cosas = Educación + etnica



## Table 1. 

```{r}
test <- data |> 
  dplyr::select(
    P001, P002, P003, educacion, etnia, 
    P017, wealth_5, patologia, P029, P030, P031, ferr_adj, P032, P033, 
    P034, P035, P036, P037
  ) |>
  mutate(
    sexo = factor(P001) |>
      fct_recode("Masculino" = "1", "Femenino" = "2") |>
      fct_relevel("Masculino", "Femenino") |>
      ff_label("Sexo del infante"),
    
    seguro_infante = case_match(
      as.character(P002), 
      c("1", "2", "3") ~ "Públicos (SIS, EsSalud, FFAA)", 
      c("4", "5") ~ "Privado", 
      c("6", "7", "99") ~ "No sabe o no responde",
      .default = NA_character_
    ) |> 
      fct_relevel("Públicos (SIS, EsSalud, FFAA)", "Privado", "No sabe o no responde") |>
      ff_label("Seguro de salud del infante"),
    
    edad_madre = ff_label(P003, "Edad de la madre")
  ) |>
  tbl_summary(
    missing_text = "(Valores perdidos)"
  )
```




## Linear Model (Naive model)

```{r}
#| fig-height: 7
#| fig-width: 9
# Anemia model
mod_anemia_1 <- glm(
  anemia_no_ferropenia ~ etnia + educacion + P001, data = data_test, family = binomial(link = "log"))

mod_anemia_1_id <- glm(
  anemia_no_ferropenia ~ etnia + educacion + P001, data = data_test, family = binomial(link = "identity"))

mod_anemia_2 <- glm(
  anemia_no_ferropenia ~ etnia + wealth_3 + P001, data = data_test, family = binomial(link = "log"))

mod_anemia_2_id <- glm(
  anemia_no_ferropenia ~ etnia + wealth_3 + P001, data = data_test, family = binomial(link = "identity"))

# Model summary
summary(mod_anemia_1)
tidy(mod_anemia_1, exponentiate = TRUE, conf.int = TRUE)

# Model summary with LRT
epiDisplay::logistic.display(mod_anemia, simplified = FALSE, crude = FALSE)

# Visual check of model assumptions
check_model(mod_anemia)

# Model performance
broom::glance(mod_anemia)

# Indices of model performance
model_performance(mod_anemia)

# Predicted values
fitted_lin_1 <- predict_response(
  mod_anemia_1, terms = c("educacion", "etnia"), margin = "mean_reference")

fitted_lin_2 <- predict_response(
  mod_anemia_2, terms = c("wealth_3", "etnia"), margin = "mean_reference")

# Plot
a1 <- plot(fitted_lin_1)
a2 <- plot(fitted_lin_2)

ggarrange(a1, a1, ncol = 2, nrow = 1)
```

```{r}
mod_ferropenia <- glm(
  ferropenia ~ etnia + P017 + educacion + P001, data = data, family = binomial(link = "log"))

summary(mod_ferropenia)

# Predicted values
fitted_lin <- predict_response(
  mod_ferropenia , terms = c("educacion", "etnia"), margin = "mean_reference")

# Plot
plot(fitted_lin)

# Altura (Ivan)
mod_ferropenia <- glm(
  ferropenia ~ etnia + P017 + educacion + P001 + P017, data = data, family = binomial(link = "log"))

summary(mod_ferropenia)

# Predicted values
fitted_lin <- predict_response(
  mod_ferropenia , terms = c("educacion", "etnia"), margin = "mean_reference")

# Plot
plot(fitted_lin)
```


```{r}
# Anemia model
mod_ferropenia <- glm(
  anemia ~ P032, data = data, family = binomial(link = "logit"))

summary(mod_ferropenia)

# Predicted values
fitted_lin <- predict_response(
  mod_ferropenia, terms = "P032", margin = "mean_reference")

# Plot
a2 <- plot(fitted_lin)
```

```{r}
# Ferropenia model
mod_ferropenia <- glm(
  ferropenia ~ P037, data = data, family = binomial(link = "logit"))

summary(mod_ferropenia)

# Predicted values
fitted_lin <- predict_response(
  mod_ferropenia, terms = "P037", margin = "mean_reference")

# Plot
a3 <- plot(fitted_lin)
```

```{r}
# Anemia model
mod_ferropenia <- glm(
  ferropenia ~ P037, data = data, family = binomial(link = "logit"))

summary(mod_ferropenia)

# Predicted values
fitted_lin <- predict_response(
  mod_ferropenia, terms = "P037", margin = "mean_reference")

# Plot
a3 <- plot(fitted_lin)
```

```{r}
# Anemia model
mod_ferropenia <- glm(
  ferropenia ~ P032, data = data, family = binomial(link = "logit"))

summary(mod_ferropenia)

# Predicted values
fitted_lin <- predict_response(
  mod_ferropenia, terms = "P032", margin = "mean_reference")

# Plot
a4 <- plot(fitted_lin)
```

```{r}
#| fig-height: 8
#| fig-width: 10
F1 <- ggarrange(
  a1, a2, a3, a4, 
  ncol = 2, nrow = 2, common.legend = TRUE, widths = c(1, 1), labels = c("A", "B", "C", "D"))

# View
F1
```

### Restricted cubic spline (natural spline)

```{r}
# Restricted cubic spline (natural spline)
mod_rcs_ferritin <- glm(
  anemia ~ rcs(ferr_adj, 3), data = data, family = binomial(link = "logit"))

summary(mod_rcs_ferritin)

# Predicted values
fitted_rcs <- predict_response(
  mod_rcs_ferritin, terms = "ferr_adj", margin = "mean_reference")

# View
b1 <- plot(fitted_rcs)
plot(fitted_rcs)
```

### GAM

```{r}
# Cubic regression splines with REML
mod_gam_ferritin  <- gam(
  anemia ~ s(ferr_adj, k = 4, bs = "cr"),
  data = data,
  family = binomial(link = "logit"),
  method = "REML",
  select = TRUE
)

summary(mod_gam_ferritin)

# Predicted values
fitted_gam <- predict_response(mod_gam_ferritin, terms = "ferr_adj")

# View
c1 <- plot(fitted_gam)
plot(fitted_gam)
```

## Transferrin

### Linear Model (Naive model)

```{r}
# Model
mod_transferrin <- glm(
  anemia ~ P032, data = data, family = binomial(link = "logit"))

summary(mod_transferrin)

# Predicted values
fitted_lin <- predict_response(
  mod_transferrin, terms = "P032", margin = "mean_reference")

# View
a2 <- plot(fitted_lin)
plot(fitted_lin)
```

### Restricted cubic spline (natural spline)

```{r}
# Restricted cubic spline (natural spline)
mod_rcs_transferrin <- glm(
  anemia ~ rcs(P032, 3), data = data, family = binomial(link = "logit"))

summary(mod_rcs_transferrin)

# Predicted values
fitted_rcs <- predict_response(
  mod_rcs_transferrin, terms = "P032", margin = "mean_reference")

# View
b2 <- plot(fitted_rcs)
plot(fitted_rcs)
```

### GAM

```{r}
# Cubic regression splines with REML
mod_gam_transferrin  <- gam(
  anemia ~ s(P032, k = 4, bs = "cr"),
  data = data,
  family = binomial(link = "logit"),
  method = "REML",
  select = TRUE
)

summary(mod_gam_transferrin)

# Predicted values
fitted_gam <- predict_response(mod_gam_transferrin, terms = "P032")

# View
c2 <- plot(fitted_gam)
plot(fitted_gam)
```

## Altitude

### Linear Model (Naive model)

```{r}
# Model
mod_altitude <- glm(
  anemia ~ P017, data = data, family = binomial(link = "logit"))

summary(mod_altitude)

# Predicted values
fitted_lin <- predict_response(
  mod_altitude, terms = "P017", margin = "mean_reference")

# View
a3 <- plot(fitted_lin)
plot(fitted_lin)
```

### Restricted cubic spline (natural spline)

```{r}
# Restricted cubic spline (natural spline)
mod_rcs_altitude <- glm(
  anemia ~ rcs(P017, 3), data = data, family = binomial(link = "logit"))

summary(mod_rcs_altitude)

# Predicted values
fitted_rcs <- predict_response(
  mod_rcs_altitude, terms = "P017", margin = "mean_reference")

# View
b3 <- plot(fitted_rcs)
plot(fitted_rcs)
```

### GAM

```{r}
# Cubic regression splines with REML
mod_gam_altitude  <- gam(
  anemia ~ s(P017, k = 4, bs = "cr"),
  data = data,
  family = binomial(link = "logit"),
  method = "REML",
  select = TRUE
)

summary(mod_gam_altitude)

# Predicted values
fitted_gam <- predict_response(mod_gam_altitude, terms = "P017")

# View
c3 <- plot(fitted_gam)
plot(fitted_gam)
```
## Ferritin + Altitude

### Linear Model (Naive model)

```{r}
# Model
mod_ferritin_altitude <- glm(
  anemia ~ ferr_adj + P017, data = data, family = binomial(link = "logit"))

summary(mod_ferritin_altitude)

# Predicted values
fitted_lin <- predict_response(
  mod_ferritin_altitude, terms = c("ferr_adj", "P017"), margin = "mean_reference")

# View
a4 <- plot(fitted_lin)
plot(fitted_lin)
```

### Restricted cubic spline (natural spline)

```{r}
# Restricted cubic spline (natural spline)
mod_rcs_ferritin_altitude <- glm(
  anemia ~ rcs(ferr_adj, 3) + rcs(P017, 3), data = data, family = binomial(link = "logit"))

summary(mod_rcs_ferritin_altitude)

# Predicted values
fitted_rcs <- predict_response(
  mod_rcs_ferritin_altitude, terms = c("ferr_adj", "P017"), margin = "mean_reference")

# View
b4 <- plot(fitted_rcs)
plot(fitted_rcs)
```

### GAM

```{r}
# Cubic regression splines with REML
mod_gam_ferritin_altitude  <- gam(
  anemia ~ s(ferr_adj, k = 4, bs = "cr") + s(P017, k = 4, bs = "cr"),
  data = data,
  family = binomial(link = "logit"),
  method = "REML",
  select = TRUE
)

summary(mod_gam_ferritin_altitude)

# Predicted values
fitted_gam <- predict_response(mod_gam_ferritin_altitude, terms = c("ferr_adj", "P017"))

# View
c4 <- plot(fitted_gam)
plot(fitted_gam)
```

## Ferritin + Wealth index

### Linear Model (Naive model)

```{r}
# Model
mod_ferritin_wealth <- glm(
  anemia ~ ferr_adj + wealth_5, data = data, family = binomial(link = "logit"))

summary(mod_ferritin_wealth)

# Predicted values
fitted_lin <- predict_response(
  mod_ferritin_wealth, terms = c("ferr_adj", "wealth_5"), margin = "mean_reference")

# View
a5 <- plot(fitted_lin)
plot(fitted_lin)
```

### Restricted cubic spline (natural spline)

```{r}
data$wealth_5 <- as.numeric(data$wealth_5)

# Restricted cubic spline (natural spline)
mod_rcs_ferritin_wealth <- glm(
  anemia ~ rcs(ferr_adj, 3) + wealth_5, data = data, family = binomial(link = "logit"))

summary(mod_rcs_ferritin_wealth)

# Predicted values
fitted_rcs <- predict_response(
  mod_rcs_ferritin_wealth, terms = c("ferr_adj", "wealth_5"), margin = "mean_reference")

# View
b5 <- plot(fitted_rcs)
plot(fitted_rcs)
```

### GAM

```{r}
# Cubic regression splines with REML
mod_gam_ferritin_wealth  <- gam(
  anemia ~ s(ferr_adj, k = 6, bs = "cr") + wealth_5,
  data = data,
  family = binomial(link = "logit"),
  method = "REML",
  select = TRUE
)

summary(mod_gam_ferritin_wealth)

# Predicted values
fitted_gam <- predict_response(mod_gam_ferritin_wealth, terms = c("ferr_adj", "wealth_5"))

# View
c5 <- plot(fitted_gam)
plot(fitted_gam)
```

## Ferritin + Transferrin

### Linear Model (Naive model)

```{r}
# Model
mod_ferritin_transferrin <- glm(
  anemia ~ ferr_adj + P032, data = data, family = binomial(link = "logit"))

summary(mod_ferritin_transferrin)

# Predicted values
fitted_lin <- predict_response(
  mod_ferritin_transferrin, terms = c("ferr_adj", "P032"), margin = "mean_reference")

# View
a6 <- plot(fitted_lin)
plot(fitted_lin)
```

### Restricted cubic spline (natural spline)

```{r}
# Restricted cubic spline (natural spline)
mod_rcs_ferritin_transferrin <- glm(
  anemia ~ rcs(ferr_adj, 3) + rcs(P032, 3), data = data, family = binomial(link = "logit"))

summary(mod_rcs_ferritin_transferrin)

# Predicted values
fitted_rcs <- predict_response(
  mod_rcs_ferritin_transferrin, terms = c("ferr_adj", "P032"), margin = "mean_reference")

# View
b6 <- plot(fitted_rcs)
plot(fitted_rcs)
```

### GAM

```{r}
# Cubic regression splines with REML
mod_gam_ferritin_transferrin  <- gam(
  anemia ~ s(ferr_adj, k = 4, bs = "cr") + s(P032, k = 4, bs = "cr"),
  data = data,
  family = binomial(link = "logit"),
  method = "REML",
  select = TRUE
)

summary(mod_gam_ferritin_transferrin)

# Predicted values
fitted_gam <- predict_response(mod_gam_ferritin_transferrin, terms = c("ferr_adj", "P032"))

# View
c6 <- plot(fitted_gam)
plot(fitted_gam)
```

# Plots

```{r}
#| fig-height: 18
#| fig-width: 25
ggarrange(a1, b1, a1, a2, b2, c2, a3, b3, c3, a4, b4, c4, a5, b5, c5, a6, b6, c6, 
          ncol = 3, nrow = 4)


```

# Save outputs

```{r}

```

