---
title: "Ferritina"
author: "Carlos Ballón-Salcedo"
date: "`r Sys.Date()`"
format:
  html:
    theme: 
     light: lux
     dark: darkly
    toc: true        # índice automático
    toc-depth: 3     # niveles de encabezado en el índice
    code-overflow: wrap
    include-after-body: zoom_in_out.js
    highlight-style: github
    number-sections: true
    code-fold: true  # plegar código
    code-tools: 
      source: "https://github.com/Carlos-Ballon/ferritin-anemia_diagnosis.git"
editor: source
execute:
  message: false
  warning: false
bibliography: grateful-refs.bib
csl: vancouver.csl
lang: en             # idioma del documento
---

# Load packages

```{r}
# Packages
pacman::p_load(
  tidyverse,
  rio,
  here,
  epiDisplay,
  Hmisc,
  sjlabelled,
  ggalluvial,
  ggplot2,
  ggsankey,
  psych,
  factoextra,
  ggpubr,
  rms,
  mgcv,
  broom,
  ggeffects,
  rfextras,
  grateful,
  flextable,
  janitor,
  performance)
```

```{r}
#| eval: false
# Citations
grateful::cite_packages(
  output = "file",
  out.format = "docx",
  out.dir = ".",
  citation.style = "vancouver")
```

# Import data

```{r}
# Data
data <- import(here("data", "base_de_curvas.dta"))

# Scripts
rfextras::load_scripts()
```

# Process data

```{r}
# Select categorical variables (to factor)
vars <- c(
  "P001", "P002", "P004", "P005", "P006", "P007", "P008", "P009", "P010", "P011",
  "P012", "P013", "P014", "P015", "P018", "P019", "P020", "P021", "P022", "P023",
  "P024", "P025", "P028", "P029", "anemia", "ferropenia")

data <- data |>
  dplyr::select(-wealth_pc1_raw, -wealth_pc1) |>
  mutate(
    anemia = if_else(P037 >= 10.5, 0L, 1L),
    ferropenia = if_else(ferr_adj >= 12, 0L, 1L)
  ) |>
  mutate(across(all_of(vars), ~ replace(.x, .x >= 99, NA))) |>
  mutate(across(all_of(vars), as_factor)) 
```

# Data dictionary / structure

```{r}
#| eval: false
# Generate a data dictionary
labelled::generate_dictionary(data)

# Inspect variable labels and data.frame structure
labelled::var_label(data)  # list of variable labels (if available)
Hmisc::contents(data)      # data.frame of variable types and missing values
dplyr::glimpse(data)       # compact structure
str(data)                  # detailed structure

# Inspect labels of specific variables
attributes(data$P001)   
```

# Exploratory Data Analysis

::: {style="text-align: justify"}
There are R packages that provide functions with the same name, such as `describe()` from the `Hmisc` package and `describe()` from the `psych` package. The former is more suitable for categorical data, while the latter is designed for numerical data. The `epiDisplay` package also offers powerful functions inspired by **Stata**, such as `summ()`. Other important options include the `janitor` package for data cleaning, as well as projects from the R Epidemics Consortium (RECON), Epiverse-TRACE, and R4EPI, which provide tools for epidemiological analysis.
:::

## Categorical data

```{r}
# Select categorical variables (factors)
categorical_vars <- data |>
  dplyr::select(where(\(x) is.character(x) | is.factor(x)))
```

### Stucture of categorical variables

```{r}
#| eval: false
# Concise statistical description (display labels)
Hmisc::describe(categorical_vars, exclude.missing = FALSE)
```

### Missing values and complete cases

```{r}
#| eval: false
# Count of missing values by column (vector)
colSums(is.na(categorical_vars))

# List of complete values by column
lapply(categorical_vars, function(x)
  sum(complete.cases(x)))

# Columns without missing values (vector)
colnames(categorical_vars)[sapply(categorical_vars, function(x)
  all(!is.na(x)))]
```

### Duplicate elements

::: {style="text-align: justify"}
The `duplicated()` function identifies duplicate elements, `unique()` extracts unique elements, and `distinct()` from dplyr package removes duplicate rows from a data frame.
:::

### Descriptive analysis: Measures of frequency and proportions

```{r}
#| eval: false
# Absolute frequency for categorical variables
lapply(categorical_vars, function(x)
  addmargins(table(x, useNA = "ifany")))

# Relative frequency for categorical variables
lapply(categorical_vars, function(x)
  round(addmargins(prop.table(table(x)) * 100), 1))
  
# Absolute frequency for categorical variables by anemia
lapply(categorical_vars, function(x)
  addmargins(table(x, categorical_vars$anemia)))

# Flextable
categorical_vars |>
  tabyl(anemia, ferropenia) |>
  adorn_totals(where = "both") |>
  adorn_percentages(denominator = "col") |>
  adorn_pct_formatting() |>
  adorn_ns(position = "front") |>
  flextable() |>
  autofit()
```

## Numerical data

```{r}
# Selection of variables
numerical_vars <- data |>
  dplyr::select(where(\(x) is.numeric(x)), anemia, ferropenia)
```

#### Descriptive statistics: Summary statistics

```{r}
#| eval: false
# Compact
numerical_vars |> epiDisplay::summ(digits = 2, na.rm = FALSE)

# Detailed
numerical_vars |> psych::describe(na.rm = FALSE)
```

#### Descriptive statistics: Grouped summary statistics

```{r}
#| eval: false
# Anemia
numerical_vars |>
  dplyr::group_split(anemia) |>
  lapply(function(data)
    summ(numerical_vars, digits = 2, na.rm = TRUE))

# Ferropenia
numerical_vars |>
  dplyr::group_split(ferropenia) |>
  lapply(function(data)
    summ(numerical_vars, digits = 2, na.rm = TRUE))
```

# Produce outputs

## Linear Model (Naive model)

```{r}
#| fig-height: 7
#| fig-width: 9
# Anemia model
mod_anemia <- glm(
  anemia ~ ferr_adj, data = data, family = binomial(link = "logit"))

# Model summary
summary(mod_anemia)

# Model summary with LRT
epiDisplay::logistic.display(mod_anemia, simplified = FALSE, crude = FALSE)

# Visual check of model assumptions
check_model(mod_anemia)

# Model performance
broom::glance(mod_anemia)

# Indices of model performance
model_performance(mod_anemia)

# Predicted values
fitted_lin <- predict_response(
  mod_anemia, terms = "ferr_adj", margin = "mean_reference")

# Plot
a1 <- plot(fitted_lin)
```

```{r}
# Anemia model
mod_ferropenia <- glm(
  anemia ~ P032, data = data, family = binomial(link = "logit"))

summary(mod_ferropenia)

# Predicted values
fitted_lin <- predict_response(
  mod_ferropenia, terms = "P032", margin = "mean_reference")

# Plot
a2 <- plot(fitted_lin)
```

```{r}
# Ferropenia model
mod_ferropenia <- glm(
  ferropenia ~ P037, data = data, family = binomial(link = "logit"))

summary(mod_ferropenia)

# Predicted values
fitted_lin <- predict_response(
  mod_ferropenia, terms = "P037", margin = "mean_reference")

# Plot
a3 <- plot(fitted_lin)
```

```{r}
# Anemia model
mod_ferropenia <- glm(
  ferropenia ~ P037, data = data, family = binomial(link = "logit"))

summary(mod_ferropenia)

# Predicted values
fitted_lin <- predict_response(
  mod_ferropenia, terms = "P037", margin = "mean_reference")

# Plot
a3 <- plot(fitted_lin)
```

```{r}
# Anemia model
mod_ferropenia <- glm(
  ferropenia ~ P032, data = data, family = binomial(link = "logit"))

summary(mod_ferropenia)

# Predicted values
fitted_lin <- predict_response(
  mod_ferropenia, terms = "P032", margin = "mean_reference")

# Plot
a4 <- plot(fitted_lin)
```

```{r}
#| fig-height: 8
#| fig-width: 10
F1 <- ggarrange(
  a1, a2, a3, a4, 
  ncol = 2, nrow = 2, common.legend = TRUE, widths = c(1, 1), labels = c("A", "B", "C", "D"))

# View
F1
```

### Restricted cubic spline (natural spline)

```{r}
# Restricted cubic spline (natural spline)
mod_rcs_ferritin <- glm(
  anemia ~ rcs(ferr_adj, 3), data = data, family = binomial(link = "logit"))

summary(mod_rcs_ferritin)

# Predicted values
fitted_rcs <- predict_response(
  mod_rcs_ferritin, terms = "ferr_adj", margin = "mean_reference")

# View
b1 <- plot(fitted_rcs)
plot(fitted_rcs)
```

### GAM

```{r}
# Cubic regression splines with REML
mod_gam_ferritin  <- gam(
  anemia ~ s(ferr_adj, k = 4, bs = "cr"),
  data = data,
  family = binomial(link = "logit"),
  method = "REML",
  select = TRUE
)

summary(mod_gam_ferritin)

# Predicted values
fitted_gam <- predict_response(mod_gam_ferritin, terms = "ferr_adj")

# View
c1 <- plot(fitted_gam)
plot(fitted_gam)
```

## Transferrin

### Linear Model (Naive model)

```{r}
# Model
mod_transferrin <- glm(
  anemia ~ P032, data = data, family = binomial(link = "logit"))

summary(mod_transferrin)

# Predicted values
fitted_lin <- predict_response(
  mod_transferrin, terms = "P032", margin = "mean_reference")

# View
a2 <- plot(fitted_lin)
plot(fitted_lin)
```

### Restricted cubic spline (natural spline)

```{r}
# Restricted cubic spline (natural spline)
mod_rcs_transferrin <- glm(
  anemia ~ rcs(P032, 3), data = data, family = binomial(link = "logit"))

summary(mod_rcs_transferrin)

# Predicted values
fitted_rcs <- predict_response(
  mod_rcs_transferrin, terms = "P032", margin = "mean_reference")

# View
b2 <- plot(fitted_rcs)
plot(fitted_rcs)
```

### GAM

```{r}
# Cubic regression splines with REML
mod_gam_transferrin  <- gam(
  anemia ~ s(P032, k = 4, bs = "cr"),
  data = data,
  family = binomial(link = "logit"),
  method = "REML",
  select = TRUE
)

summary(mod_gam_transferrin)

# Predicted values
fitted_gam <- predict_response(mod_gam_transferrin, terms = "P032")

# View
c2 <- plot(fitted_gam)
plot(fitted_gam)
```

## Altitude

### Linear Model (Naive model)

```{r}
# Model
mod_altitude <- glm(
  anemia ~ P017, data = data, family = binomial(link = "logit"))

summary(mod_altitude)

# Predicted values
fitted_lin <- predict_response(
  mod_altitude, terms = "P017", margin = "mean_reference")

# View
a3 <- plot(fitted_lin)
plot(fitted_lin)
```

### Restricted cubic spline (natural spline)

```{r}
# Restricted cubic spline (natural spline)
mod_rcs_altitude <- glm(
  anemia ~ rcs(P017, 3), data = data, family = binomial(link = "logit"))

summary(mod_rcs_altitude)

# Predicted values
fitted_rcs <- predict_response(
  mod_rcs_altitude, terms = "P017", margin = "mean_reference")

# View
b3 <- plot(fitted_rcs)
plot(fitted_rcs)
```

### GAM

```{r}
# Cubic regression splines with REML
mod_gam_altitude  <- gam(
  anemia ~ s(P017, k = 4, bs = "cr"),
  data = data,
  family = binomial(link = "logit"),
  method = "REML",
  select = TRUE
)

summary(mod_gam_altitude)

# Predicted values
fitted_gam <- predict_response(mod_gam_altitude, terms = "P017")

# View
c3 <- plot(fitted_gam)
plot(fitted_gam)
```
## Ferritin + Altitude

### Linear Model (Naive model)

```{r}
# Model
mod_ferritin_altitude <- glm(
  anemia ~ ferr_adj + P017, data = data, family = binomial(link = "logit"))

summary(mod_ferritin_altitude)

# Predicted values
fitted_lin <- predict_response(
  mod_ferritin_altitude, terms = c("ferr_adj", "P017"), margin = "mean_reference")

# View
a4 <- plot(fitted_lin)
plot(fitted_lin)
```

### Restricted cubic spline (natural spline)

```{r}
# Restricted cubic spline (natural spline)
mod_rcs_ferritin_altitude <- glm(
  anemia ~ rcs(ferr_adj, 3) + rcs(P017, 3), data = data, family = binomial(link = "logit"))

summary(mod_rcs_ferritin_altitude)

# Predicted values
fitted_rcs <- predict_response(
  mod_rcs_ferritin_altitude, terms = c("ferr_adj", "P017"), margin = "mean_reference")

# View
b4 <- plot(fitted_rcs)
plot(fitted_rcs)
```

### GAM

```{r}
# Cubic regression splines with REML
mod_gam_ferritin_altitude  <- gam(
  anemia ~ s(ferr_adj, k = 4, bs = "cr") + s(P017, k = 4, bs = "cr"),
  data = data,
  family = binomial(link = "logit"),
  method = "REML",
  select = TRUE
)

summary(mod_gam_ferritin_altitude)

# Predicted values
fitted_gam <- predict_response(mod_gam_ferritin_altitude, terms = c("ferr_adj", "P017"))

# View
c4 <- plot(fitted_gam)
plot(fitted_gam)
```

## Ferritin + Wealth index

### Linear Model (Naive model)

```{r}
# Model
mod_ferritin_wealth <- glm(
  anemia ~ ferr_adj + wealth_5, data = data, family = binomial(link = "logit"))

summary(mod_ferritin_wealth)

# Predicted values
fitted_lin <- predict_response(
  mod_ferritin_wealth, terms = c("ferr_adj", "wealth_5"), margin = "mean_reference")

# View
a5 <- plot(fitted_lin)
plot(fitted_lin)
```

### Restricted cubic spline (natural spline)

```{r}
data$wealth_5 <- as.numeric(data$wealth_5)

# Restricted cubic spline (natural spline)
mod_rcs_ferritin_wealth <- glm(
  anemia ~ rcs(ferr_adj, 3) + wealth_5, data = data, family = binomial(link = "logit"))

summary(mod_rcs_ferritin_wealth)

# Predicted values
fitted_rcs <- predict_response(
  mod_rcs_ferritin_wealth, terms = c("ferr_adj", "wealth_5"), margin = "mean_reference")

# View
b5 <- plot(fitted_rcs)
plot(fitted_rcs)
```

### GAM

```{r}
# Cubic regression splines with REML
mod_gam_ferritin_wealth  <- gam(
  anemia ~ s(ferr_adj, k = 6, bs = "cr") + wealth_5,
  data = data,
  family = binomial(link = "logit"),
  method = "REML",
  select = TRUE
)

summary(mod_gam_ferritin_wealth)

# Predicted values
fitted_gam <- predict_response(mod_gam_ferritin_wealth, terms = c("ferr_adj", "wealth_5"))

# View
c5 <- plot(fitted_gam)
plot(fitted_gam)
```

## Ferritin + Transferrin

### Linear Model (Naive model)

```{r}
# Model
mod_ferritin_transferrin <- glm(
  anemia ~ ferr_adj + P032, data = data, family = binomial(link = "logit"))

summary(mod_ferritin_transferrin)

# Predicted values
fitted_lin <- predict_response(
  mod_ferritin_transferrin, terms = c("ferr_adj", "P032"), margin = "mean_reference")

# View
a6 <- plot(fitted_lin)
plot(fitted_lin)
```

### Restricted cubic spline (natural spline)

```{r}
# Restricted cubic spline (natural spline)
mod_rcs_ferritin_transferrin <- glm(
  anemia ~ rcs(ferr_adj, 3) + rcs(P032, 3), data = data, family = binomial(link = "logit"))

summary(mod_rcs_ferritin_transferrin)

# Predicted values
fitted_rcs <- predict_response(
  mod_rcs_ferritin_transferrin, terms = c("ferr_adj", "P032"), margin = "mean_reference")

# View
b6 <- plot(fitted_rcs)
plot(fitted_rcs)
```

### GAM

```{r}
# Cubic regression splines with REML
mod_gam_ferritin_transferrin  <- gam(
  anemia ~ s(ferr_adj, k = 4, bs = "cr") + s(P032, k = 4, bs = "cr"),
  data = data,
  family = binomial(link = "logit"),
  method = "REML",
  select = TRUE
)

summary(mod_gam_ferritin_transferrin)

# Predicted values
fitted_gam <- predict_response(mod_gam_ferritin_transferrin, terms = c("ferr_adj", "P032"))

# View
c6 <- plot(fitted_gam)
plot(fitted_gam)
```

# Plots

```{r}
#| fig-height: 18
#| fig-width: 25
ggarrange(a1, b1, a1, a2, b2, c2, a3, b3, c3, a4, b4, c4, a5, b5, c5, a6, b6, c6, 
          ncol = 3, nrow = 4)


```

# Save outputs

```{r}

```

